# Court Document Analysis Pipeline

# 

# All document types processed by Claude:

# VERDICT forms (handwritten): Claude reads PDFs directly

# JUDGEMENT and MINUTE documents (typed PDFs): Claude reads PDFs directly

# 

# Output: one merged CSV plus per-type CSVs

## ── SETUP ────────────────────────────────────────────────────────────────────

# Before running:

# 1. Install packages if needed:

# install.packages(c("tidyverse","httr","jsonlite","purrr","base64enc"))

# 2. Create a config.R file in the same directory as this script (see template below)

# 3. Add config.R to your .gitignore — NEVER commit it to version control

# 

# config.R should define these variables:

# anthropic_key \<- "sk-ant-..."

# cases_root \<- "\~/path/to/your/cases"

```{r setup}
library(tidyverse)
library(httr)
library(jsonlite)
library(dplyr)
library(purrr)
library(base64enc)
library(pdftools)      # for docket text extraction — install.packages("pdftools")

# Load API key and config (DO NOT SHARE THIS FILE)
source("config.R")
```

## ── HELPERS ──────────────────────────────────────────────────────────────────

```{r helpers}
`%||%` <- function(x, y) {
  if (is.null(x) || length(x) == 0) y else x
}

# Encode a local PDF to base64 string
encode_pdf <- function(filepath) {
  base64encode(readBin(filepath, "raw", file.info(filepath)$size))
}

# Detect document type from filename.
# More-specific minute types are checked first so they take priority over the
# general "minute" fallback.
#   minute_day1         — filename contains "minute" and "day1"
#   minute_final        — filename contains "minute" and "final"
#   minute_deliberation — all other minute files (contain "minute" but not day1 or final)
detect_doc_type <- function(filename) {
  fname <- tolower(basename(filename))
  if (str_detect(fname, "verdict"))                                return("verdict")
  if (str_detect(fname, "judgement"))                              return("judgement")
  if (str_detect(fname, "docket"))                                 return("docket")
  if (str_detect(fname, "minute") && str_detect(fname, "day1"))   return("minute_day1")
  if (str_detect(fname, "minute") && str_detect(fname, "final"))  return("minute_final")
  if (str_detect(fname, "minute"))                                 return("minute_deliberation")
  return("unknown")
}

# Safely extract a named field from a parsed JSON list
safe_field <- function(json_list, field, default = NA_character_) {
  val <- json_list[[field]]
  if (is.null(val) || length(val) == 0) default else as.character(val)
}

# Extract only the header and docket entries from a PACER docket PDF,
# skipping the plaintiff/defendant party block which can be very long.
# Dockets are digitally generated PDFs so pdftools extracts clean text.
#
# Strategy:
#   - Header ends when the party block begins (first line starting with
#     "Plaintiff", "Petitioner", "Defendant", or "In Re")
#   - Docket entries begin at the first line matching a date + entry number
#     pattern (MM/DD/YYYY followed by a docket number)
#   - We keep the header + everything from the first docket entry onward,
#     discarding the party/attorney block in between
extract_docket_text <- function(filepath) {
  raw_pages <- pdftools::pdf_text(filepath)
  full_text <- paste(raw_pages, collapse = "\n")
  lines     <- str_split(full_text, "\n")[[1]]

  # Party block starts at a line that is just whitespace + "Plaintiff" and nothing else
  party_start <- which(str_detect(lines, "^\\s*Plaintiff\\s*$"))
  party_start <- if (length(party_start) > 0) party_start[1] else length(lines)

  # Docket entries begin at the header line "   Date Filed   #   Docket Text"
  entry_start <- which(str_detect(lines, "^\\s*Date Filed\\s+#\\s+Docket Text\\s*$"))
  entry_start <- if (length(entry_start) > 0) entry_start[1] else (party_start + 1)

  # Keep: header (lines before party block) + docket column header + entries
  header_lines <- lines[seq_len(party_start - 1)]
  entry_lines  <- lines[entry_start:length(lines)]

  paste(c(header_lines, "", entry_lines),
        collapse = "\n") %>%
    str_trim()
}


sleep_if_needed <- function(results, j, limit = 30000) {

  # look back ~60 seconds worth of recent calls (approx via last N docs)
  window <- max(1, j - 10):j

  recent_tokens <- sum(results$total_tokens[window], na.rm = TRUE)

  if (recent_tokens > limit) {
    message("Rate limit protection triggered: sleeping 10s...")
    Sys.sleep(10)
  }
}
```

## ── BUILD CASE INVENTORY ─────────────────────────────────────────────────────

```{r inventory}
case_folders <- list.dirs(cases_root, recursive = FALSE)

doc_inventory <- map_dfr(case_folders, function(folder) {
  case_id <- basename(folder)
  pdfs    <- list.files(folder, pattern = "\\.pdf$", full.names = TRUE, ignore.case = TRUE)
  tibble(
    case_id  = case_id,
    filepath = pdfs,
    doc_type = map_chr(pdfs, detect_doc_type)
  )
}) %>%
  filter(doc_type != "unknown") %>%
  arrange(case_id, doc_type)

#doc_inventory <- doc_inventory %>% filter(case_id == "1000309")

cat(sprintf("Found %d documents across %d cases:\n",
            nrow(doc_inventory), n_distinct(doc_inventory$case_id)))
print(count(doc_inventory, doc_type))
```

## Rerun on failed cases (Temporary)
```{r}
#retry_files <- c(
#  "/Users/jasonliang/Desktop/plab-parser/kate_files/1077/Judgement_1.pdf",
#  "/Users/jasonliang/Desktop/plab-parser/kate_files/1077/Judgement_2.pdf",
#  "/Users/jasonliang/Desktop/plab-parser/kate_files/1077/Judgement_3.pdf",
#  "/Users/jasonliang/Desktop/plab-parser/kate_files/1077/Judgement.pdf",
#  "/Users/jasonliang/Desktop/plab-parser/kate_files/1400778/Verdict_A.pdf",
#  "/Users/jasonliang/Desktop/plab-parser/kate_files/1400778/Verdict_B.pdf",
#  "/Users/jasonliang/Desktop/plab-parser/kate_files/1400778/Verdict_C.pdf"
#)

#doc_inventory <- tibble(filepath = retry_files) %>%
#  mutate(
#    case_id  = basename(dirname(filepath)),
#    doc_type = map_chr(filepath, detect_doc_type)
#  ) %>%
#  filter(doc_type != "unknown") %>%
#  arrange(case_id, doc_type)

#cat(sprintf("Retrying %d documents across %d cases:\n",
#            nrow(doc_inventory), n_distinct(doc_inventory$case_id)))
#print(count(doc_inventory, doc_type))
```

## ── PROMPTS (Claude) ─────────────────────────────────────────────────────────

```{r prompts}

# ── VERDICT ───────────────────────────────────────────────────────────────────
# All verdict fields are extracted in a single API call.
# Claude reads the PDF directly including handwritten content.

verdict_system_prompt <- "You are a legal data analyst extracting structured information
from jury verdict forms in US civil cases. The form may be handwritten. Read all
handwritten text carefully. Return ONLY valid JSON with no additional text.
Do not include explanations, reasoning, markdown, or commentary.
Do not wrap the JSON in markdown code fences."

verdict_user_prompt <- "Extract the following fields from this jury verdict form and
return them as a single JSON object with exactly these key names.

--- PARTY TYPE (Pl_type_verdict, Def_type_verdict) ---
Record the type of each plaintiff and defendant. Use: individual, corporation, or the
specific government entity type such as city, county, or school. If all parties on one
side are the same type do not repeat — list each distinct type once. If an individual
is represented by their estate, record as individual. If multiple types exist, separate
with a comma.

--- GENDER (Pl_gender_verdict, Def_gender_verdict) ---
For individual plaintiffs/defendants only, infer gender from the name (Male / Female /
Unknown). If there are both male and female parties on one side, write mixed. Leave
null if all parties on that side are not individuals.

--- COUNTS (Number_pl_verdict, Number_def_verdict) ---
Count the total number of plaintiffs and defendants. If an individual is represented
by their estate, count as one. Include consolidated parties in the total. Exclude
counter-plaintiffs, counter-defendants, and third parties. Exclude terminated parties.
Do not count separately an individual who appears only as a guardian/representative
for a minor unless they also appear individually.

--- OUTCOME (Outcome_verdict, Verdict_note) ---
Determine whether the verdict favors the plaintiff or defendant. If a successful
counterclaim means the defense wins more money than the plaintiff, record Outcome as
defendant. If the plaintiff is found 50% or more liable, record Outcome as defendant.
Otherwise record as plaintiff. 
Other outcomes may include:
settlement: if the jury was selected but a settlement happened before they could 
make a decision. 
hung jury: a jury was selected but they could not come to a decision 
mistrial: a jury was selected but the judge declared a mistrial (for a reason 
other than a hung jury) 
judgement as a matter of law: a jury was selected but the judge grants a 
judgement as a matter of law and the jury is dismissed
If the jury is deciding only liability (damages already
determined), record Verdict_note as liability only. If only deciding damages (liability already determined), record as damages only. 

--- NON-ECONOMIC DAMAGES REQUESTED (Non_economic_damages_requested) ---
If the verdict form contains a line or space for a dollar value for non-economic
damages — including pain and suffering, loss of consortium, emotional distress,
physical impairment or disfigurement, mental anguish, impairment of quality of life,
loss of enjoyment of life, deprivation of civil rights, or similar — record YES.
Otherwise record NO.

--- PUNITIVE DAMAGES REQUESTED (Punitive_damages_requested) ---
If the verdict form contains a line or space for punitive or exemplary damages,
record YES. Otherwise record NO.

--- MONETARY AWARD (Monetary_award) ---
Total monetary value awarded to the plaintiff including economic, non-economic, and
punitive damages combined. Record 0 if the defendant won. If the defendant is less
than 100% liable, scale the total damages by the defendant liability percentage. If
the verdict indicates the plaintiff award will be reduced by a specific amount (due to
a counterclaim or failure to mitigate), subtract that amount.

--- NON-ECONOMIC DAMAGES AWARDED (Non_economic_damages_awarded) ---
Total non-economic damages awarded. Record 0 if the defendant won. Keywords include:
pain and suffering, loss of consortium, emotional distress, physical impairment,
mental anguish, impairment of quality of life, loss of enjoyment of life, deprivation
of civil rights, and similar. Leave null if the verdict does not specify the nature or
division of damages.

--- PUNITIVE DAMAGES AWARDED (Punitive_damages_awarded) ---
Total punitive or exemplary damages awarded. Record 0 if the defendant won.

--- PLAINTIFF LIABILITY (Percent_plaintiff_liable) ---
If the verdict finds the plaintiff partially liable, record the percentage. Otherwise null.

--- FORMAT RULES ---
Record all dollar amounts as plain numbers with no commas or dollar signs.
Use null for any field that is not present, not applicable, or cannot be determined.
Return ONLY the JSON object below with no additional text.

{
  \"Pl_type_verdict\": \"string — comma-separated distinct plaintiff types\",
  \"Def_type_verdict\": \"string — comma-separated distinct defendant types\",
  \"Pl_gender_verdict\": \"Male / Female / Mixed / null\",
  \"Def_gender_verdict\": \"Male / Female / Mixed / null\",
  \"Number_pl_verdict\": numeric,
  \"Number_def_verdict\": numeric,
  \"Outcome_verdict\": \"plaintiff or defendant\",
  \"Verdict_note\": \"string or null — liability only / damages only / or other notable context\",
  \"Non_economic_damages_requested\": \"YES or NO\",
  \"Punitive_damages_requested\": \"YES or NO\",
  \"Monetary_award\": numeric,
  \"Non_economic_damages_awarded\": numeric or null,
  \"Punitive_damages_awarded\": numeric,
  \"Percent_plaintiff_liable\": numeric or null,
  \"verdict_date_verdict\": \"MM/DD/YYYY or null\"
}"


# ── judgement ──────────────────────────────────────────────────────────────────
judgement_system_prompt <- "You are a legal data analyst extracting structured information
from court judgement documents in US civil cases. Return ONLY valid JSON with
no additional text. Do not include explanations, reasoning, markdown, or commentary.
Do not wrap the JSON in markdown code fences."

judgement_user_prompt <- "Extract the following field from this judgement document and
return it as a JSON object:

--- PARTY TYPE (Pl_type_judgement, Def_type_judgement) ---
Record the type of each plaintiff and defendant. Use: individual, corporation, or the
specific government entity type such as city, county, or school. If all parties on one
side are the same type do not repeat — list each distinct type once. If an individual
is represented by their estate, record as individual. If multiple types exist, separate
with a comma.

--- GENDER (Pl_gender_judgement, Def_gender_judgement) ---
For individual plaintiffs/defendants only, infer gender from the name (Male / Female /
Unknown). If there are both male and female parties on one side, write mixed. Leave
null if all parties on that side are not individuals.

--- COUNTS (Number_pl_judgement, Number_def_judgement) ---
Count the total number of plaintiffs and defendants. If an individual is represented
by their estate, count as one. Include consolidated parties in the total. Exclude
counter-plaintiffs, counter-defendants, and third parties. Exclude terminated parties.
Do not count separately an individual who appears only as a guardian/representative
for a minor unless they also appear individually.

--- OUTCOME (Outcome_judgement) ---
Determine whether the verdict favors the plaintiff or defendant. Other outcomes may include:
settlement: if the jury was selected but a settlement happened before they could 
make a decision. 
hung jury: a jury was selected but they could not come to a decision 
mistrial: a jury was selected but the judge declared a mistrial (for a reason 
other than a hung jury) 
judgement as a matter of law: a jury was selected but the judge grants a 
judgement as a matter of law and the jury is dismissed

--- FINAL JURY SIZE (SeatedJurySize_end) ---
Record the size of the jury that decided the verdict if included. Usually appears
as something like 'tried before a jury of X', 'tried before a jury of X duly sworn',
or 'tried before an empaneled jury of X'. Record the number X as a plain integer. 
Leave null if no such statementappears in the document.

{
  \"Pl_type_judgement\": \"string — comma-separated distinct plaintiff types\",
  \"Def_type_judgement\": \"string — comma-separated distinct defendant types\",
  \"Pl_gender_judgement\": \"Male / Female / Mixed / null\",
  \"Def_gender_judgement\": \"Male / Female / Mixed / null\",
  \"Number_pl_judgement\": numeric,
  \"Number_def_judgement\": numeric,
  \"Outcome_judgement\": \"plaintiff or defendant\",
  \"SeatedJurySize_end\": numeric or null
}"


# ── MINUTE ENTRY — DAY 1 ─────────────────────────────────────────────────────
# Used for minute files whose name contains both "minute" and "day_1".
# Extracts jury selection details and voir dire timing.

minute_day1_system_prompt <- "You are a legal data analyst extracting structured
information from Day 1 trial minute entries in US civil cases. These are chronological
logs of court proceedings. Times are recorded as timestamps (e.g. 9:05 a.m.).
Return ONLY valid JSON with no additional text. Do not include explanations, 
reasoning, markdown, or commentary. Do not wrap the JSON in markdown code fences."

minute_day1_user_prompt <- "Extract the following fields from this Day 1 minute entry
and return them as a single JSON object with exactly these key names. Do not include
anything else in your response.

--- TRIAL DATE (Trial_start_minutes) ---
The date of the first day of the jury trial as MM/DD/YYYY.

--- JUDGE (Judge_jury_trial_minutes) ---
The full name and title of the presiding judge as listed at the top of the document.
Include titles such as Judge, Magistrate Judge, or Chief Judge exactly as written.

--- FINAL JURY SIZE (SeatedJurySize_beg) ---
The number of jurors sworn to try the case after voir dire is complete. The minutes
may list individual juror IDs rather than a count — if so, count the IDs listed under
the swearing-in or selection entry. Do not count alternates separately unless the
document distinguishes them.

--- JURORS BROUGHT TO COURT (JuryPoolSize) ---
If the minutes state how many jurors were brought to court, record that number. This is 
different from the number called to the box for voir dire. Look for wording like X 
potential jurors are brought to the court. Ignore sentences like not X jurors are 
seated in the jury box prior to the court calling the case. Leave null if not mentioned.

--- EXCUSED FOR CAUSE (Excused_by_court) ---
The number of potential jurors excused by the court during voir dire for cause,
hardship, or at the court's direction. Include challenges for cause by either party
that result in removal. If individual juror IDs are listed as excused, count them
(do not double-count IDs that appear more than once). Leave null if the minutes make
no reference to jurors being excused for any reason other than peremptory challenge.
Do not include peremptory challenges in this count.

--- PLAINTIFF PEREMPTORY CHALLENGES (Plaintiff_challenges) ---
The number of peremptory challenges used by the plaintiff(s). Look for headings such
as Plaintiff's Peremptory Challenges, Plaintiff's Challenges, or Challenges by the
Plaintiff followed by a list of juror IDs. If not explicitly stated, count the juror
IDs listed under the plaintiff's challenges section.

--- DEFENDANT PEREMPTORY CHALLENGES (Defendant_challenges) ---
The number of peremptory challenges used by the defendant(s). Look for headings such
as Defendant's Peremptory Challenges, Defendant's Challenges, or Challenges by the
Defendant followed by a list of juror IDs. If not explicitly stated, count the juror
IDs listed under the defendant's challenges section.

--- VOIR DIRE LENGTH (Voir_dire_time, Voir_dire_recess_length) ---
The duration of voir dire in minutes (integer). Calculate as follows:
  Start time: the timestamp at or directly before any of these events:
    Voir dire by the court commences / Court voir dires jurors /
    Voir dire begins by the Court / Voir dire of prospective jurors by the Court /
    Voir dire commences / Voir dire begins / or similar.
  End time: the earliest timestamp at or directly after any of these events:
    Jurors selected to try the case / Voir dire completed /
    Jurors sworn to try the case / Jurors called to try case / or similar.
Subtract any recess time that falls within the voir dire window. Store the total amount 
of court recess time subtracted as voir_dire_recess_length as a plain integer number of 
minutes. It should specifically say Court in Recess followed by Court in Session. Do not 
subtract other breaks aside from this type of recess. Record the net duration as a plain 
integer number of minutes.

--- VOIR DIRE TIMESTAMPS (Voir_dire_start, Voir_dire_end, Voir_dire_recess_times) ---
Record the timestaps corresponding to the start and end of voir dire as well as timestamps
for court recesses during voir dire. List the recess timestamps as 'hh:mm AM/PM to 
hh:mm AM/PM'. List the start and end timestamp as 'hh:mm AM/PM'. If the line noting the
start/end of voir dire does not fall neatly on a timestamp, record the nearest associated
timestamp of the start/end of voir dire.

--- VOIR DIRE EXTRAS (VD_extras) ---
There may be other entries or events listed at the timestamp marking the start or
end of voir dire. Note any activity or event that occurred between the nearest 
timestamp and the actual start or end of voir dire (i.e. events recorded between 
the timestamp marker and the voir dire boundary event). Leave null if none.

{
  \"Trial_start_minutes\": \"MM/DD/YYYY or null\",
  \"Judge_jury_trial_minutes\": \"string or null\",
  \"SeatedJurySize_beg\": numeric or null,
  \"JuryPoolSize\": numeric or null,
  \"Excused_by_court\": numeric or null,
  \"Plaintiff_challenges\": numeric or null,
  \"Defendant_challenges\": numeric or null,
  \"Voir_dire_time\": numeric or null,
  \"Voir_dire_recess_length\": numeric or null,
  \"Voir_dire_start\": HH:MM AM/PM or null,
  \"Voir_dire_end\": HH:MM AM/PM or null,
  \"Voir_dire_recess_times\": HH:MM AM/PM to HH:MM AM/PM or null,
  \"VD_extras\": \"string or null\"
}"

# ── MINUTE ENTRY — FINAL DAY ──────────────────────────────────────────────────
# Used for minute files whose name contains "minute" and "final".
# This file records the day the verdict was reached. It contains the verdict date,
# final trial day number, and the end of deliberations. The deliberation start time
# may appear here OR at the end of the previous day's deliberation minutes.

minute_final_system_prompt <- "You are a legal data analyst extracting structured
information from final-day trial minute entries in US civil cases. These are
chronological logs with timestamps. Return ONLY valid JSON with
no additional text. Do not include explanations, reasoning, markdown, or commentary.
Do not wrap the JSON in markdown code fences."

minute_final_user_prompt <- "Extract the following fields from this final-day minute
entry and return them as a single JSON object with exactly these key names.


--- FINAL TRIAL DAY (NumberofDaysinTrial) ---
The day number of the jury trial recorded at the top of these minutes, found in a
heading such as 'Trial to Jury - Day X'. Record the integer X.

--- VERDICT DATE (Verdict_date_minutes) ---
The date that the verdict was decided, in the format MM/DD/YYYY.

--- DELIBERATION START TIME (Delib_start_time) ---
The timestamp marking the start of jury deliberations if it appears in this document.
Look for 'Jury excused to begin deliberations', 'Jury to commence deliberations', or
similar. Record the time exactly as written (e.g. 2:15 p.m.). Leave null if the
start of deliberations is not recorded in this document — it may appear at the end of
the previous day's minutes instead.

--- DELIBERATION END TIME (Delib_end_time) ---
The timestamp marking the end of jury deliberations. Look for the court resuming
session in connection with the verdict: 'Court in session' immediately before or after
'verdict reached', 'the jury has reached a verdict', 'jury present' for the verdict
reading, or similar. Use the earliest such timestamp if multiple qualify.
Record the time exactly as written.

--- PARTY TYPE (Pl_type_minutes, Def_type_minutes) ---
Record the type of each plaintiff and defendant. Use: individual, corporation, or the
specific government entity type such as city, county, or school. If all parties on one
side are the same type do not repeat — list each distinct type once. If an individual
is represented by their estate, record as individual. If multiple types exist, separate
with a comma.

--- GENDER (Pl_gender_minutes, Def_gender_minutes) ---
For individual plaintiffs/defendants only, infer gender from the name (Male / Female /
Unknown). If there are both male and female parties on one side, write mixed. Leave
null if all parties on that side are not individuals.

--- COUNTS (Number_pl_minutes, Number_def_minutes) ---
Count the total number of plaintiffs and defendants. If an individual is represented
by their estate, count as one. Include consolidated parties in the total. Exclude
counter-plaintiffs, counter-defendants, and third parties. Exclude terminated parties.
Do not count separately an individual who appears only as a guardian/representative
for a minor unless they also appear individually.

--- OUTCOME (Outcome_minutes) ---
Determine whether the verdict favors the plaintiff or defendant. Other outcomes may include:
settlement: if the jury was selected but a settlement happened before they could 
make a decision. 
hung jury: a jury was selected but they could not come to a decision 
mistrial: a jury was selected but the judge declared a mistrial (for a reason 
other than a hung jury) 
judgement as a matter of law: a jury was selected but the judge grants a 
judgement as a matter of law and the jury is dismissed


{
  \"NumberofDaysinTrial\": numeric or null,
  \"Verdict_date_minutes\": MM/DD/YYYY or null,
  \"Delib_start_time\": \"string or null\",
  \"Delib_end_time\": \"string or null\",
  \"Pl_type_minutes\": \"string — comma-separated distinct plaintiff types\",
  \"Def_type_minutes\": \"string — comma-separated distinct defendant types\",
  \"Pl_gender_minutes\": \"Male / Female / Mixed / null\",
  \"Def_gender_minutes\": \"Male / Female / Mixed / null\",
  \"Number_pl_minutes\": numeric,
  \"Number_def_minutes\": numeric,
  \"Outcome_minutes\": \"plaintiff or defendant\"
}"


# ── MINUTE ENTRY — DELIBERATION DAYS ──────────────────────────────────────────
# Used for all minute files that are not Day 1 or the final day.
# These correspond to days where deliberations were ongoing but no verdict was reached.
# Each file may record:
#   - The end-of-day adjournment time (when the jury stopped deliberating)
#   - The start-of-day resumption time (when the jury resumed the next morning)
#   - A deliberation start time if deliberations first began on this day
# The R assembly step uses these times across all deliberation-day files to compute
# total deliberation time.

minute_deliberation_system_prompt <- "You are a legal data analyst extracting
structured information from mid-trial deliberation day minute entries in US civil
cases. These are chronological logs with timestamps. Return ONLY valid JSON with
no additional text. Do not include explanations, reasoning, markdown, or commentary.
Do not wrap the JSON in markdown code fences."

minute_deliberation_user_prompt <- "Extract the following fields from this deliberation
day minute entry and return them as a single JSON object with exactly these key names.

--- DELIBERATION START TIME (Delib_start_time) ---
The timestamp marking the first start of jury deliberations IF deliberations began for
the first time on this day. Look for 'Jury excused to begin deliberations',
'Jury to commence deliberations', or similar. Record the time exactly as written.
Leave null if deliberations had already been underway from a prior day.

--- END OF DAY ADJOURNMENT (Delib_adjourn_time) ---
The last timestamp before the court adjourned for the day while deliberations were
ongoing (i.e. the jury was sent home without reaching a verdict). Look for
'Court in recess', 'Jury excused until [date/time]', 'Court adjourned', or similar
at the end of the document. Record the time exactly as written.

--- NEXT DAY RESUMPTION (Delib_resume_time) ---
If this document also records the time deliberations resumed after a prior adjournment
(i.e. the jury returned and continued deliberating from a previous day), record that
timestamp. Look for 'Jury present', 'Court in session', 'Deliberations resume', or
similar at the start of deliberation activity. Leave null if deliberations first began
on this day rather than resuming.

{
  \"Delib_start_time\": \"string or null\",
  \"Delib_adjourn_time\": \"string or null\",
  \"Delib_resume_time\": \"string or null\"
}"


minute_system_prompt        <- minute_deliberation_system_prompt
minute_user_prompt          <- minute_deliberation_user_prompt


# ── DOCKET ────────────────────────────────────────────────────────────────────
# Docket PDFs are pre-processed with pdftools to extract only the header and
# docket entries, skipping the lengthy plaintiff/defendant party block.
# The extracted plain text is sent to Claude as a text message (not a PDF),
# which is cheaper and faster since the text layer is already clean.

docket_system_prompt <- "You are a legal data analyst extracting structured information
from US federal district court dockets (PACER). The document includes a case header
followed by chronological docket entries. Ignore the plaintiff and defendant party
sections entirely. Extract information only from the header and docket entries.
Return ONLY valid JSON with no additional text. Do not include explanations,
reasoning, markdown, or commentary. Do not wrap the JSON in markdown code fences."

docket_user_prompt <- "Extract the following fields from this court docket and return
them as a single JSON object with exactly these key names.

--- INITIAL DISTRICT JUDGE — HEADER (Judge_initial_assignment_docket_header) ---
Look in the case header for a line reading 'Assigned to: [title] [name]'. Record the
judge's full name and title exactly as written (e.g. 'Chief Judge Wiley Y. Daniel',
'Senior Judge Christine M. Arguello'). Store in Judge_initial_assignment_docket_header.

--- INITIAL DISTRICT JUDGE — DOCKET ENTRIES (Judge_initial_assignment_docket_entry) ---
Scan the docket entries to find the first explicit assignment of a district judge.
Look for entries such as:
  'Case assigned to Judge XXX'
  'Case drawn to Judge XXX'
  'Memorandum returning case for reassignment by Judge XXX'
  'Case reassigned to Judge YYY. Judge XXX no longer assigned to the case'
In the reassignment examples, record Judge XXX (the departing judge) as the initial
assignment. If a magistrate judge is the first judge assigned to dispositive matters,
record that magistrate judge as the initial judge. Ignore any earlier appearances of a
judge's name in entries related to summary dismissal screening or other preliminary
administrative matters — those do not constitute assignment. If no explicit assignment
entry exists, leave null.
Store in Judge_initial_assignment_docket_entry.

--- MAGISTRATE JUDGE — HEADER (Magistrate_assignment_docket_header) ---
Look in the case header for a line reading 'Referred to: Magistrate Judge [name]'.
Record the full name and title exactly as written (e.g. 'Magistrate Judge Michael E.
Hegarty'). Store in Magistrate_assignment_docket_header.

--- MAGISTRATE JUDGE — DOCKET ENTRIES (Magistrate_assignment_docket_entry) ---
Scan the docket entries to find the first explicit referral or assignment of a
magistrate judge. Look for entries such as:
  'Order referring case to Magistrate Judge XXX'
  'Case referred to Magistrate Judge XXX'
  'Case assigned to Magistrate Judge XXX'
Ignore earlier appearances of a magistrate judge's name in entries related to
summary dismissal screening or other preliminary administrative matters.
If no explicit referral entry exists, leave null.
Store in Magistrate_assignment_docket_entry.

--- JURY TRIAL IDENTIFICATION ---
Scan all docket entries for jury trial proceedings. These appear as entries like
'Jury Trial Day 1', 'Jury Trial - Day One', 'Day 1 Jury Trial', or similar.
Group consecutive jury trial day entries into distinct trial sequences.

If there are multiple trial sequences (e.g., a first trial that ended in a mistrial
or hung jury followed by a second trial), identify each separately. Select the LAST
trial sequence that ended with a jury verdict, judgment, or other final resolution —
NOT one that ended in a mistrial, hung jury, or was declared incomplete.

For each date: read the date from WITHIN the docket entry text itself — look for
phrases like 'held on [date]' or 'proceedings held on [date]'. Do NOT use the date
in the leftmost date column, which is the filing or entry date, not the proceeding date.

--- JURY TRIAL FIRST DATE (Trial_start_docket) ---
The date of Day 1 of the final completed jury trial, in MM/DD/YYYY format. Extract
from the docket entry text (e.g. 'Jury Trial Day One held on [date]').

--- JURY TRIAL LAST DATE (Verdict_date_docket) ---
The date of the final day of the last completed jury trial — the day a verdict was
reached or the trial otherwise concluded. Extract from the docket entry text.

--- PRESIDING JUDGE (Judge_jury_trial_docket) ---
The judge named in the jury trial day entries as presiding over the final completed
trial. Include full name and title as written. If different judges presided on
different days, record the judge who presided on the day the verdict was reached.

--- TRIAL SEQUENCE NOTE (Multiple_trials_note) ---
If only one trial sequence is found, leave null. If multiple trial sequences are
found, briefly describe them — e.g. 'Two trial sequences: first trial March 2007
ended in mistrial; second trial August 2005 returned verdict.' Note if multiple
sequences were found so the researcher can verify.

--- OUTCOME (Outcome_docket) ---
Determine whether the verdict favors the plaintiff or defendant. If a successful
counterclaim means the defense wins more money than the plaintiff, record Outcome as
defendant. If the plaintiff is found 50% or more liable, record Outcome as defendant.
Otherwise record as plaintiff. 
Other outcomes may include:
settlement: if the jury was selected but a settlement happened before they could 
make a decision. 
hung jury: a jury was selected but they could not come to a decision 
mistrial: a jury was selected but the judge declared a mistrial (for a reason 
other than a hung jury) 
judgement as a matter of law: a jury was selected but the judge grants a 
judgement as a matter of law and the jury is dismissed

{
  \"Judge_initial_assignment_docket_header\": \"string or null\",
  \"Judge_initial_assignment_docket_entry\": \"string or null\",
  \"Magistrate_assignment_docket_header\": \"string or null\",
  \"Magistrate_assignment_docket_entry\": \"string or null\",
  \"Trial_start_docket\": \"MM/DD/YYYY or null\",
  \"Verdict_date_docket\": \"MM/DD/YYYY or null\",
  \"Judge_jury_trial_docket\": \"string or null\",
  \"Outcome_docket\": \"plaintiff or defendant\",
  \"Multiple_trials_note\": \"string or null\"
}"
```

## ── CLAUDE API FUNCTION ─────────────────────────────────────────────────────

```{r claude_function}
get_claude_response <- function(filepath, doc_type) {

  sys_prompt  <- switch(doc_type,
    verdict              = verdict_system_prompt,
    judgement            = judgement_system_prompt,
    docket               = docket_system_prompt,
    minute_day1          = minute_day1_system_prompt,
    minute_final         = minute_final_system_prompt,
    minute_deliberation  = minute_deliberation_system_prompt
  )
  user_prompt <- switch(doc_type,
    verdict              = verdict_user_prompt,
    judgement            = judgement_user_prompt,
    docket               = docket_user_prompt,
    minute_day1          = minute_day1_user_prompt,
    minute_final         = minute_final_user_prompt,
    minute_deliberation  = minute_deliberation_user_prompt
  )

  # Dockets: extract header + entries as plain text, send as a text message.
  # This skips the lengthy party block, reduces tokens, and is faster/cheaper
  # than sending the full PDF. All other document types are sent as base64 PDFs.
  if (doc_type == "docket") {
    docket_text <- extract_docket_text(filepath)
    combined    <- paste0(user_prompt, "\n\n--- DOCKET TEXT ---\n", docket_text)

    body <- list(
      model       = "claude-sonnet-4-6",
      max_tokens  = 1500,
      temperature = 0,
      system      = sys_prompt,
      messages    = list(
        list(
          role    = "user",
          content = combined   # plain text only — no PDF attachment
        )
      )
    )

  } else {
    pdf_b64 <- encode_pdf(filepath)

    body <- list(
      model       = "claude-sonnet-4-6",
      max_tokens  = 1500,    # increased to accommodate expanded verdict JSON output
      temperature = 0,       # deterministic — always pick the single most likely answer
      system      = sys_prompt,
      messages    = list(
        list(
          role    = "user",
          content = list(
            list(
              type   = "document",
              source = list(
                type       = "base64",
                media_type = "application/pdf",
                data       = pdf_b64
              )
            ),
            list(type = "text", text = user_prompt)
          )
        )
      )
    )
  }

  request_start <- Sys.time()

  response <- POST(
    url     = "https://api.anthropic.com/v1/messages",
    add_headers(
      `x-api-key`         = anthropic_key,
      `anthropic-version` = "2023-06-01",
      `content-type`      = "application/json"
    ),
    body   = toJSON(body, auto_unbox = TRUE),
    encode = "raw"
  )

  elapsed         <- as.numeric(difftime(Sys.time(), request_start, units = "secs"))
  parsed_response <- content(response, as = "parsed", type = "application/json")

  if (http_error(response)) {
    stop(paste0("Claude API error [", status_code(response), "]: ",
                parsed_response$error$message %||% "Unknown error"))
  }

  raw_text     <- parsed_response$content[[1]]$text %||% NA_character_
  total_tokens <- (parsed_response$usage$input_tokens  %||% 0) +
                  (parsed_response$usage$output_tokens %||% 0)
  clean_text   <- str_replace_all(raw_text, "```json|```", "") %>% str_trim()

  list(
    raw_text     = raw_text,
    parsed_json  = tryCatch(fromJSON(clean_text, simplifyVector = FALSE),
                            error = function(e) NULL),
    total_tokens = total_tokens,
    elapsed_sec  = elapsed
  )
}

safe_claude <- purrr::safely(get_claude_response, otherwise = NULL)
```

## ── TOKEN PRE-CHECK (optional — run before main pipeline to estimate cost) ───

```{r token_precheck, eval=FALSE}
# Calls the free token-counting endpoint on one sample doc of each type.
# Does not run inference. Use this to verify cost before running the full pipeline.

count_tokens_claude <- function(filepath, doc_type) {
  sys_prompt  <- switch(doc_type,
    verdict  = verdict_system_prompt,
    judgement = judgement_system_prompt,
    minute   = minute_system_prompt)
  user_prompt <- switch(doc_type,
    verdict  = verdict_user_prompt,
    judgement = judgement_user_prompt,
    minute   = minute_user_prompt)
  pdf_b64 <- encode_pdf(filepath)
  body <- list(
    model    = "claude-sonnet-4-6",
    system   = sys_prompt,
    messages = list(list(
      role    = "user",
      content = list(
        list(type = "document",
             source = list(type = "base64", media_type = "application/pdf", data = pdf_b64)),
        list(type = "text", text = user_prompt)
      )
    ))
  )
  response <- POST(
    url     = "https://api.anthropic.com/v1/messages/count_tokens",
    add_headers(`x-api-key` = anthropic_key,
                `anthropic-version` = "2023-06-01",
                `content-type` = "application/json"),
    body   = toJSON(body, auto_unbox = TRUE),
    encode = "raw"
  )
  parsed <- content(response, as = "parsed", type = "application/json")
  parsed$input_tokens %||% NA_real_
}

sample_docs <- doc_inventory %>% group_by(doc_type) %>% slice(1) %>% ungroup()
token_ests  <- sample_docs %>%
  mutate(input_tokens = map2_dbl(filepath, doc_type, count_tokens_claude))

avg_input       <- mean(token_ests$input_tokens, na.rm = TRUE)
n_docs          <- nrow(doc_inventory)
est_input_cost  <- (avg_input * n_docs / 1e6) * 3
est_output_cost <- (300 * n_docs / 1e6) * 15

cat(sprintf(
  "\n=== COST ESTIMATE ===
Claude -- %d documents:
  Avg input tokens/doc: %.0f
  Est. input cost:      $%.4f
  Est. output cost:     $%.4f
  Est. total:           $%.4f\n",
  n_docs, avg_input,
  est_input_cost, est_output_cost, est_input_cost + est_output_cost
))
```

## ── MAIN PIPELINE: CLAUDE ON ALL DOCUMENTS ───────────────────────────────────

# 

# Processes one document at a time, saves a checkpoint after every document,

# and writes a CSV every batch_size rows. If the run is interrupted, simply

# re-run this chunk — already-processed rows are skipped automatically.

```{r main_pipeline}
# Change after:
doc_inventory <- combined_docs
checkpoint_file <- "court_pipeline_checkpoint.rds"
batch_size      <- 20   # save a CSV snapshot every this many documents

if (file.exists(checkpoint_file)) {
  results <- readRDS(checkpoint_file)
  message("Resumed from checkpoint: ", sum(results$processed), " docs already done")
} else {
  results <- doc_inventory %>%
    mutate(
      raw_reply    = NA_character_,
      total_tokens = NA_real_,
      elapsed_sec  = NA_real_,
      api_error    = NA_character_,
      processed    = FALSE
    )
}

run_id  <- format(Sys.time(), "%Y%m%d_%H%M%S")
out_dir <- file.path(getwd(), paste0("court_run_", run_id))
dir.create(out_dir, showWarnings = FALSE)
checkpoint_file <- file.path(out_dir, "court_pipeline_checkpoint.rds")

n_total       <- nrow(results)
pb            <- txtProgressBar(min = 0, max = n_total, style = 3)
overall_start <- Sys.time()

for (j in seq_len(n_total)) {

  # Skip rows already completed (enables safe resumption after interruption)
  if (isTRUE(results$processed[j])) {
    setTxtProgressBar(pb, j)
    next
  }

  elapsed_mins <- as.numeric(difftime(Sys.time(), overall_start, units = "mins"))
  cat(sprintf("
[%d/%d] Case: %s | Type: %s | Elapsed: %.1f min
",
              j, n_total, results$case_id[j], results$doc_type[j], elapsed_mins))
  flush.console()

  ans <- safe_claude(results$filepath[j], results$doc_type[j])
  Sys.sleep(61)

  if (is.null(ans$result)) {
    results$api_error[j] <- conditionMessage(ans$error) %||% "Unknown error"
  } else {
    results$raw_reply[j]    <- ans$result$raw_text
    results$total_tokens[j] <- ans$result$total_tokens
    results$elapsed_sec[j]  <- ans$result$elapsed_sec
  }

  results$processed[j] <- TRUE
  saveRDS(results, checkpoint_file)   # checkpoint after every document
  setTxtProgressBar(pb, j)

  if (j %% batch_size == 0 || j == n_total) {
    write_csv(results, 
              file.path(out_dir, sprintf("court_pipeline_batch_row%04d.csv", j)))
    message(sprintf("
Batch checkpoint saved at row %d", j))
  }
}

close(pb)
message("All Claude calls complete.")
```
# TEMPORARY (REMOVE LATER) MANUALLY PUT IN RESULTS
```{r}
#results <- read.csv("court_pipeline_combined.csv")
```

## ── PARSE AND MERGE OUTPUTS INTO CSVs ────────────────────────────────────────

```{r parse_outputs}

# ── VERDICT CSV ──────────────────────────────────────────────────────────────
verdict_claude <- results %>%
  filter(doc_type == "verdict", !is.na(raw_reply)) %>%
  mutate(parsed = map(raw_reply, ~{
    clean <- str_replace_all(.x, "```json|```", "") %>% str_trim()
    tryCatch(fromJSON(clean, simplifyVector = FALSE), error = function(e) NULL)
  })) %>%
  filter(!map_lgl(parsed, is.null)) %>%
  mutate(
    Pl_type_verdict                      = map_chr(parsed, ~safe_field(.x, "Pl_type_verdict")),
    Def_type_verdict                     = map_chr(parsed, ~safe_field(.x, "Def_type_verdict")),
    Pl_gender_verdict                    = map_chr(parsed, ~safe_field(.x, "Pl_gender_verdict")),
    Def_gender_verdict                   = map_chr(parsed, ~safe_field(.x, "Def_gender_verdict")),
    Number_pl_verdict                    = map_chr(parsed, ~safe_field(.x, "Number_pl_verdict")),
    Number_def_verdict                   = map_chr(parsed, ~safe_field(.x, "Number_def_verdict")),
    Outcome_verdict                      = map_chr(parsed, ~safe_field(.x, "Outcome_verdict")),
    Verdict_note                 = map_chr(parsed, ~safe_field(.x, "Verdict_note")),
    Non_economic_damages_requested = map_chr(parsed, ~safe_field(.x, "Non_economic_damages_requested")),
    Punitive_damages_requested   = map_chr(parsed, ~safe_field(.x, "Punitive_damages_requested")),
    Monetary_award               = map_chr(parsed, ~safe_field(.x, "Monetary_award")),
    Non_economic_damages_awarded = map_chr(parsed, ~safe_field(.x, "Non_economic_damages_awarded")),
    Punitive_damages_awarded     = map_chr(parsed, ~safe_field(.x, "Punitive_damages_awarded")),
    Percent_plaintiff_liable     = map_chr(parsed, ~safe_field(.x, "Percent_plaintiff_liable")),
    verdict_date_verdict                 = map_chr(parsed, ~safe_field(.x, "verdict_date_verdict")),
  ) %>%
  select(case_id, filepath,
         Pl_type_verdict, Def_type_verdict, Pl_gender_verdict, Def_gender_verdict,
         Number_pl_verdict, Number_def_verdict,
         Outcome_verdict, Verdict_note,
         Non_economic_damages_requested, Punitive_damages_requested,
         Monetary_award, Non_economic_damages_awarded, Punitive_damages_awarded,
         Percent_plaintiff_liable, verdict_date_verdict) 

output_verdicts <- verdict_claude

#write_csv(output_verdicts, "output_verdicts.csv")
#message("Saved output_verdicts.csv — ", nrow(output_verdicts), " rows")

# ── judgement CSV ──────────────────────────────────────────────────────────────
output_judgement <- results %>%
  filter(doc_type == "judgement", !is.na(raw_reply)) %>%
  mutate(parsed = map(raw_reply, ~{
    clean <- str_replace_all(.x, "```json|```", "") %>% str_trim()
    tryCatch(fromJSON(clean, simplifyVector = FALSE), error = function(e) NULL)
  })) %>%
  filter(!map_lgl(parsed, is.null)) %>%
  mutate(
    Pl_type_judgement            = map_chr(parsed, ~safe_field(.x, "Pl_type_judgement")),
    Def_type_judgement         = map_chr(parsed, ~safe_field(.x, "Def_type_judgement")),
    Pl_gender_judgement        = map_chr(parsed, ~safe_field(.x, "Pl_gender_judgement")),
    Def_gender_judgement      = map_chr(parsed, ~safe_field(.x, "Def_gender_judgement")),
    Number_pl_judgement       = map_chr(parsed, ~safe_field(.x, "Number_pl_judgement")),
    Number_def_judgement      = map_chr(parsed, ~safe_field(.x, "Number_def_judgement")),
    Outcome_judgement     = map_chr(parsed, ~safe_field(.x, "Outcome_judgement")),
    SeatedJurySize_end = map_chr(parsed, ~safe_field(.x, "SeatedJurySize_end"))) %>%
  select(case_id, filepath,
         Pl_type_judgement, Def_type_judgement, Pl_gender_judgement, 
         Def_gender_judgement, Number_pl_judgement, Number_def_judgement,
         Outcome_judgement, SeatedJurySize_end)

#write_csv(output_judgement, "output_judgement.csv")
#message("Saved output_judgement.csv — ", nrow(output_judgement), " rows")

# ── MINUTE DAY 1 CSV ─────────────────────────────────────────────────────────
output_minutes_day1 <- results %>%
  filter(doc_type == "minute_day1", !is.na(raw_reply)) %>%
  #mutate(parsed = map(raw_reply, ~{
  #  clean <- str_replace_all(.x, "```json|```", "") %>% str_trim()
  #  tryCatch(fromJSON(clean, simplifyVector = FALSE), error = function(e) NULL)
  #})) %>%
  mutate(parsed = map(raw_reply, ~{
  json_str <- stringr::str_extract(.x, "\\{[\\s\\S]*\\}")
  tryCatch(jsonlite::fromJSON(json_str, simplifyVector = FALSE),
           error = function(e) NULL)
  }))%>%
  filter(!map_lgl(parsed, is.null)) %>%
  mutate(
    Trial_start_minutes        = map_chr(parsed, ~safe_field(.x, "Trial_start_minutes")),
    Judge_jury_trial_minutes             = map_chr(parsed, ~safe_field(.x, "Judge_jury_trial_minutes")),
    SeatedJurySize_beg         = map_chr(parsed, ~safe_field(.x, "SeatedJurySize_beg")),
    JuryPoolSize    = map_chr(parsed, ~safe_field(.x, "JuryPoolSize")),
    Excused_by_court = map_chr(parsed, ~safe_field(.x, "Excused_by_court")),
    Plaintiff_challenges     = map_chr(parsed, ~safe_field(.x, "Plaintiff_challenges")),
    Defendant_challenges    = map_chr(parsed, ~safe_field(.x, "Defendant_challenges")),
    Voir_dire_time = map_chr(parsed, ~safe_field(.x, "Voir_dire_time")),
    Voir_dire_start = map_chr(parsed, ~safe_field(.x, "Voir_dire_start")),
    Voir_dire_end = map_chr(parsed, ~safe_field(.x, "Voir_dire_end")),
    Voir_dire_recess_length = map_chr(parsed, ~safe_field(.x, "Voir_dire_recess_length")),
    Voir_dire_recess_times = map_chr(parsed, ~{
      val <- safe_field(.x, "Voir_dire_recess_times")
      if (length(val) == 0 || is.null(val)) return(NA_character_)
      paste(val, collapse = "; ")
    }),
    VD_extras  = map_chr(parsed, ~safe_field(.x, "VD_extras"))
  ) %>%
  select(case_id, filepath, Trial_start_minutes, Judge_jury_trial_minutes, 
         SeatedJurySize_beg, JuryPoolSize,
         Excused_by_court, Plaintiff_challenges, Defendant_challenges,
         Voir_dire_time, Voir_dire_start, Voir_dire_end, Voir_dire_recess_length, 
         Voir_dire_recess_times, VD_extras)

#write_csv(output_minutes_day1, "output_minutes_day1.csv")
#message("Saved output_minutes_day1.csv — ", nrow(output_minutes_day1), " rows")

# ── MINUTE FINAL CSV ─────────────────────────────────────────────────────────
output_minutes_final <- results %>%
  filter(doc_type == "minute_final", !is.na(raw_reply)) %>%
  mutate(parsed = map(raw_reply, ~{
    clean <- str_replace_all(.x, "```json|```", "") %>% str_trim()
    tryCatch(fromJSON(clean, simplifyVector = FALSE), error = function(e) NULL)
  })) %>%
  filter(!map_lgl(parsed, is.null)) %>%
  mutate(
    NumberofDaysinTrial      = map_chr(parsed, ~safe_field(.x, "NumberofDaysinTrial")),
    Verdict_date_minutes = map_chr(parsed, ~safe_field(.x, "Verdict_date_minutes")),
    Delib_start_time     = map_chr(parsed, ~safe_field(.x, "Delib_start_time")),
    Delib_end_time       = map_chr(parsed, ~safe_field(.x, "Delib_end_time")),
    Pl_type_minutes = map_chr(parsed, ~safe_field(.x, "Pl_type_minutes")),
    Def_type_minutes   = map_chr(parsed, ~safe_field(.x, "Def_type_minutes")),
    Pl_gender_minutes  = map_chr(parsed, ~safe_field(.x, "Pl_gender_minutes")),
    Def_gender_minutes  = map_chr(parsed, ~safe_field(.x, "Def_gender_minutes")),
    Number_pl_minutes    = map_chr(parsed, ~safe_field(.x, "Number_pl_minutes")),
    Number_def_minutes   = map_chr(parsed, ~safe_field(.x, "Number_def_minutes")),
    Outcome_minutes   = map_chr(parsed, ~safe_field(.x, "Outcome_minutes"))
  ) %>%
  select(case_id, filepath, Pl_type_minutes, Def_type_minutes, Pl_gender_minutes, 
         Def_gender_minutes, Number_pl_minutes, Number_def_minutes, 
         Outcome_minutes, NumberofDaysinTrial, Verdict_date_minutes, 
         Delib_start_time, Delib_end_time)

#write_csv(output_minutes_final, "output_minutes_final.csv")
#message("Saved output_minutes_final.csv — ", nrow(output_minutes_final), " rows")


# ── MINUTE DELIBERATION DAYS CSV ──────────────────────────────────────────────
output_minutes_delib <- results %>%
  filter(doc_type == "minute_deliberation", !is.na(raw_reply)) %>%
  mutate(parsed = map(raw_reply, ~{
    clean <- str_replace_all(.x, "```json|```", "") %>% str_trim()
    tryCatch(fromJSON(clean, simplifyVector = FALSE), error = function(e) NULL)
  })) %>%
  filter(!map_lgl(parsed, is.null)) %>%
  mutate(
    Delib_start_time     = map_chr(parsed, ~safe_field(.x, "Delib_start_time")),
    Delib_adjourn_time   = map_chr(parsed, ~safe_field(.x, "Delib_adjourn_time")),
    Delib_resume_time    = map_chr(parsed, ~safe_field(.x, "Delib_resume_time")),
  ) %>%
  select(case_id, filepath, Delib_start_time, Delib_adjourn_time,
         Delib_resume_time)

#write_csv(output_minutes_delib, "output_minutes_delib.csv")
#message("Saved output_minutes_delib.csv — ", nrow(output_minutes_delib), " rows")


# ── DELIBERATION LENGTH ASSEMBLY ──────────────────────────────────────────────
# Assembles total deliberation time per case from the final and deliberation-day
# minute files. The key insight is that deliberation start time may appear either
# in a deliberation-day file OR in the final-day file, and adjournment/resumption
# times are needed to calculate time on each day when deliberations span multiple
# days. All time arithmetic is done here in R.
#
# Per-day logic:
#   Deliberation-day files (not the final day):
#     Active delib time = adjourn_time - resume_or_start_time
#     If resume_time is present, use that as the start of that day's session.
#     If only start_time is present, deliberations first began that day.
#     If neither is present, that day's contribution cannot be calculated.
#
#   Final-day file:
#     Active delib time = end_time - resume_or_start_time
#     Use Delib_start_time if present (single-day deliberations or started here),
#     otherwise use no start anchor — will be NA and flagged for manual review.
#
# Total = sum of per-day contributions. NA if any day is unresolvable.

parse_time <- function(t) {
  if (is.na(t) || !nzchar(t)) return(NA_real_)
  t_clean <- str_replace_all(t, "\\.", "") %>%
             str_replace_all("(?i)\\bam\\b", "AM") %>%
             str_replace_all("(?i)\\bpm\\b", "PM") %>%
             str_trim()
  parsed <- suppressWarnings(
    as.POSIXct(paste("2000-01-01", t_clean), format = "%Y-%m-%d %I:%M %p")
  )
  if (is.na(parsed)) return(NA_real_)
  as.numeric(parsed) / 60   # minutes since epoch; differences give duration in minutes
}

time_diff_mins <- function(start_str, end_str) {
  s <- parse_time(start_str)
  e <- parse_time(end_str)
  if (is.na(s) || is.na(e)) return(NA_real_)
  e - s
}

# Per-day contribution from deliberation-day files
delib_day_contributions <- output_minutes_delib %>%
  mutate(
    # Use resume time if present (continuing from prior day), else start time (began this day)
    day_start  = ifelse(!is.na(Delib_resume_time) & nzchar(Delib_resume_time),
                        Delib_resume_time, Delib_start_time),
    day_mins   = map2_dbl(day_start, Delib_adjourn_time, time_diff_mins)
  ) %>%
  select(case_id, filepath, day_mins)

# Per-case contribution from final-day file
final_day_contributions <- output_minutes_final %>%
  mutate(
    day_mins   = map2_dbl(Delib_start_time, Delib_end_time, time_diff_mins)
  ) %>%
  select(case_id, filepath, day_mins)

# Combine and sum per case
all_delib_days <- bind_rows(
  delib_day_contributions %>% select(case_id, day_mins),
  final_day_contributions  %>% select(case_id, day_mins)
)

deliberation_totals <- all_delib_days %>%
  group_by(case_id) %>%
  summarise(
    Deliberation_time = if (any(is.na(day_mins))) NA_real_ else sum(day_mins),
    any_na = any(is.na(day_mins)),
    .groups = "drop"
  ) %>%
  left_join(
    final_day_contributions %>% select(case_id),
    by = "case_id"
  ) %>%
  mutate(
    Deliberation_time_flag = if_else(
      any_na,
      "one or more days had unresolvable times — verify manually",
      NA_character_
    )
  ) %>%
  select(case_id,
         Deliberation_time, Deliberation_time_flag)

#write_csv(deliberation_totals, "output_deliberation_totals.csv")
#message("Saved output_deliberation_totals.csv — ", nrow(deliberation_totals), " cases")

# ── DOCKET CSV ────────────────────────────────────────────────────────────────
output_docket <- results %>%
  filter(doc_type == "docket", !is.na(raw_reply)) %>%
  mutate(parsed = map(raw_reply, ~{
    clean <- str_replace_all(.x, "```json|```", "") %>% str_trim()
    tryCatch(fromJSON(clean, simplifyVector = FALSE), error = function(e) NULL)
  })) %>%
  filter(!map_lgl(parsed, is.null)) %>%
  mutate(
    Judge_initial_assignment_docket_header = map_chr(parsed, ~safe_field(.x, "Judge_initial_assignment_docket_header")),
    Judge_initial_assignment_docket_entry  = map_chr(parsed, ~safe_field(.x, "Judge_initial_assignment_docket_entry")),
    Magistrate_assignment_docket_header    = map_chr(parsed, ~safe_field(.x, "Magistrate_assignment_docket_header")),
    Magistrate_assignment_docket_entry     = map_chr(parsed, ~safe_field(.x, "Magistrate_assignment_docket_entry")),
    Trial_start_docket                       = map_chr(parsed, ~safe_field(.x, "Trial_start_docket")),
    Verdict_date_docket                         = map_chr(parsed, ~safe_field(.x, "Verdict_date_docket")),
    Judge_jury_trial_docket                            = map_chr(parsed, ~safe_field(.x, "Judge_jury_trial_docket")),
    Outcome_docket       = map_chr(parsed, ~safe_field(.x, "Outcome_docket")),
    Multiple_trials_note                    = map_chr(parsed, ~safe_field(.x, "Multiple_trials_note"))
  ) %>%
  select(case_id, filepath,
         Judge_initial_assignment_docket_header, Judge_initial_assignment_docket_entry,
         Magistrate_assignment_docket_header, Magistrate_assignment_docket_entry,
         Trial_start_docket, Verdict_date_docket, Judge_jury_trial_docket, 
         Outcome_docket, Multiple_trials_note)

#write_csv(output_docket, "output_docket.csv")
#message("Saved output_docket.csv — ", nrow(output_docket), " rows")


# Merge all into one CSV
dfs <- list(
  output_verdicts,
  output_judgement,
  output_minutes_day1,
  output_minutes_final,
  deliberation_totals,
  output_docket
) %>%
  map(~ select(.x, -any_of("filepath")))

final_df <- reduce(dfs, full_join, by = "case_id")
readr::write_excel_csv(
  final_df,
  file.path(out_dir, paste0("merged_output_", run_id, ".csv"))
)

message("  Cases needing manual review for deliberation: ",
        sum(!is.na(deliberation_totals$Deliberation_time_flag)))


# ── ERROR LOG ─────────────────────────────────────────────────────────────────
errors <- results %>%
  filter(!is.na(api_error)) %>%
  mutate(source = "Claude") %>%
  select(case_id, doc_type, filepath, source, error = api_error)

if (nrow(errors) > 0) {
  write_csv(errors, file.path(out_dir, "output_errors.csv"))
  message("Saved output_errors.csv — ", nrow(errors), " failed calls to investigate")
} else {
  message("No errors — all API calls succeeded")
}
```
# Reorders columns (Not the optimal fix but will do for now)
```{r}
merged <- read.csv("/Users/jasonliang/Desktop/plab-parser/court_run_20260511_095501/merged_output_20260511_095501.csv", check.names = FALSE)

# Column order following the ground truth structure.
# Where ground truth has a single column (e.g. Pl_type), we group all
# source-suffixed variants together (_verdict, _judgement, _minutes).

col_order <- c(
  # ── Case identifier ──────────────────────────────────────────────────────────
  "case_id",

  # ── Party type ───────────────────────────────────────────────────────────────
  "Pl_type_verdict",
  "Pl_type_judgement",
  "Pl_type_minutes",
  "Def_type_verdict",
  "Def_type_judgement",
  "Def_type_minutes",

  # ── Party gender ─────────────────────────────────────────────────────────────
  "Pl_gender_verdict",
  "Pl_gender_judgement",
  "Pl_gender_minutes",
  "Def_gender_verdict",
  "Def_gender_judgement",
  "Def_gender_minutes",

  # ── Party counts ─────────────────────────────────────────────────────────────
  "Number_pl_verdict",
  "Number_pl_judgement",
  "Number_pl_minutes",
  "Number_def_verdict",
  "Number_def_judgement",
  "Number_def_minutes",

  # ── Trial dates ──────────────────────────────────────────────────────────────
  "Trial_start_minutes",   
  "Trial_start_docket",
  "verdict_date_verdict",
  "Verdict_date_minutes",
  "Verdict_date_docket",
  "NumberofDaysinTrial",
  "Multiple_trials_note",

  # ── Judge assignments ────────────────────────────────────────────────────────
  "Judge_initial_assignment_docket_header",
  "Judge_initial_assignment_docket_entry",
  "Magistrate_assignment_docket_header",
  "Magistrate_assignment_docket_entry",
  
   # ── Judge / jury type ────────────────────────────────────────────────────────
  "Judge_jury_trial_minutes",
  "Judge_jury_trial_docket",

  # ── Jury selection ───────────────────────────────────────────────────────────
  "SeatedJurySize_beg",
  "SeatedJurySize_end",
  "JuryPoolSize",
  "Excused_by_court",
  "Plaintiff_challenges",
  "Defendant_challenges",
  "Voir_dire_time",
  "Voir_dire_start",
  "Voir_dire_end",
  "Voir_dire_recess_length",
  "Voir_dire_recess_times",
  "VD_extras",

  # ── Deliberation ─────────────────────────────────────────────────────────────
  "Deliberation_time",
  "Delib_start_time",
  "Delib_end_time",
  "Deliberation_time_flag",

  # ── Damages ──────────────────────────────────────────────────────────────────
  "Non_economic_damages_requested",
  "Punitive_damages_requested",
  "Monetary_award",
  
  # ── Outcome ──────────────────────────────────────────────────────────────────
  "Outcome_verdict",
  "Outcome_judgement",
  "Outcome_minutes",
  "Outcome_docket",
  "Verdict_note",
  "Non_economic_damages_awarded",
  "Punitive_damages_awarded",
  "Percent_plaintiff_liable"
)

# Keep only columns that actually exist in merged (guards against name changes)
col_order_valid <- col_order[col_order %in% names(merged)]

# Append any remaining columns not explicitly listed above
remaining <- setdiff(names(merged), col_order_valid)
final_order <- c(col_order_valid, remaining)

merged_reordered <- merged %>% select(all_of(final_order), 
                                      -any_of(c("Delib_start_time", "Delib_end_time")))

write.csv(merged_reordered, file.path(out_dir, "merged_output_reordered.csv")
          , row.names = FALSE)

cat("Columns in final order:\n")
print(names(merged_reordered))
```

