# Court Document Analysis Pipeline

# 

# All document types processed by Claude:

# VERDICT forms (handwritten): Claude reads PDFs directly

# JUDGEMENT and MINUTE documents (typed PDFs): Claude reads PDFs directly

# 

# Output: one merged CSV plus per-type CSVs

## ── SETUP ────────────────────────────────────────────────────────────────────

# Before running:

# 1. Install packages if needed:

# install.packages(c("tidyverse","httr","jsonlite","purrr","base64enc"))

# 2. Create a config.R file in the same directory as this script (see template below)

# 3. Add config.R to your .gitignore — NEVER commit it to version control

# config.R should define these variables:

# anthropic_key \<- "sk-ant-..."

# cases_root \<- "\~/path/to/your/cases"

```{r setup}
rm(list = ls())
library(tidyverse)
library(httr)
library(jsonlite)
library(dplyr)
library(purrr)
library(base64enc)
library(pdftools)      # for docket text extraction — install.packages("pdftools")
library(qpdf)          # for combining multi-part PDFs — install.packages("qpdf")

# Load API key and config (DO NOT SHARE THIS FILE)
source("config.R")
```

## ── HELPERS ──────────────────────────────────────────────────────────────────

```{r helpers}
`%||%` <- function(x, y) {
  if (is.null(x) || length(x) == 0) y else x
}

# Encode a local PDF to base64 string
encode_pdf <- function(filepath) {
  base64encode(readBin(filepath, "raw", file.info(filepath)$size))
}

# Detect document type from filename.
# More-specific minute types are checked first so they take priority over the
# general "minute" fallback.
#   minute_day1         — filename contains "minute" and "day1"
#   minute_final        — filename contains "minute" and "final"
#   minute_deliberation — all other minute files (contain "minute" but not day1 or final)
detect_doc_type <- function(filename) {
  fname <- tolower(basename(filename))
  if (str_detect(fname, "verdict"))                                return("verdict")
  if (str_detect(fname, "judg[e]?ment")) return("judgement")
  if (str_detect(fname, "docket"))                                 return("docket")
  if (str_detect(fname, "minute") && str_detect(fname, "day1(?!\\d)")) return("minute_day1")
  if (str_detect(fname, "minute") && str_detect(fname, "final"))  return("minute_final")
  if (str_detect(fname, "minute"))                                 return("minute_deliberation")
  return("unknown")
}

# Safely extract a named field from a parsed JSON list
safe_field <- function(json_list, field, default = NA_character_) {
  val <- json_list[[field]]
  if (is.null(val) || length(val) == 0) default else as.character(val)
}

# Extract only the header and docket entries from a PACER docket PDF,
# skipping the plaintiff/defendant party block which can be very long.
# Dockets are digitally generated PDFs so pdftools extracts clean text.
#
# Strategy:
#   - Header ends when the party block begins (first line starting with
#     "Plaintiff", "Petitioner", "Defendant", or "In Re")
#   - Docket entries begin at the first line matching a date + entry number
#     pattern (MM/DD/YYYY followed by a docket number)
#   - We keep the header + everything from the first docket entry onward,
#     discarding the party/attorney block in between
extract_docket_text <- function(filepath) {
  raw_pages <- pdftools::pdf_text(filepath)
  full_text <- paste(raw_pages, collapse = "\n")
  lines     <- str_split(full_text, "\n")[[1]]

  # Party block starts at a line that is just whitespace + "Plaintiff" and nothing else
  party_start <- which(str_detect(lines, "^\\s*Plaintiff\\s*$"))
  party_start <- if (length(party_start) > 0) party_start[1] else length(lines)

  # Docket entries begin at the header line "   Date Filed   #   Docket Text"
  entry_start <- which(str_detect(lines, "^\\s*Date Filed\\s+#\\s+Docket Text\\s*$"))
  entry_start <- if (length(entry_start) > 0) entry_start[1] else (party_start + 1)

  # Keep: header (lines before party block) + docket column header + entries
  header_lines <- lines[seq_len(party_start - 1)]
  entry_lines  <- lines[entry_start:length(lines)]

  paste(c(header_lines, "", entry_lines),
        collapse = "\n") %>%
    str_trim()
}

sleep_if_needed <- function(results, j, limit = 30000) {

  # look back ~60 seconds worth of recent calls (approx via last N docs)
  window <- max(1, j - 10):j

  recent_tokens <- sum(results$total_tokens[window], na.rm = TRUE)

  if (recent_tokens > limit) {
    message("Rate limit protection triggered: sleeping 10s...")
    Sys.sleep(10)
  }
}

parse_time <- function(t) {
  if (is.na(t) || !nzchar(t)) return(NA_real_)
  t_clean <- str_replace_all(t, "\\.", "") %>%
             str_replace_all("(?i)\\bam\\b", "AM") %>%
             str_replace_all("(?i)\\bpm\\b", "PM") %>%
             str_trim()

  # Try standard parse with AM/PM first
  parsed <- suppressWarnings(
    as.POSIXct(paste("2000-01-01", t_clean), format = "%Y-%m-%d %I:%M %p")
  )

  # Fallback: bare H:MM or HH:MM with no AM/PM — infer from hour
  if (is.na(parsed) && str_detect(t_clean, "^\\d{1,2}:\\d{2}$")) {
    hour <- as.integer(str_extract(t_clean, "^\\d{1,2}"))
    suffix <- if (hour >= 7 && hour < 12) "AM" else "PM"
    parsed <- suppressWarnings(
      as.POSIXct(paste("2000-01-01", t_clean, suffix),
                 format = "%Y-%m-%d %I:%M %p")
    )
  }

  if (is.na(parsed)) return(NA_real_)
  as.numeric(parsed) / 60
}

time_diff_mins <- function(start_str, end_str) {
  s <- parse_time(start_str)
  e <- parse_time(end_str)
  if (is.na(s) || is.na(e)) return(NA_real_)
  e - s
}

```

## ── BUILD CASE INVENTORY ─────────────────────────────────────────────────────

```{r inventory}
case_folders <- list.dirs(cases_root, recursive = FALSE)

doc_inventory <- map_dfr(case_folders, function(folder) {
  case_id <- basename(folder)
  pdfs    <- list.files(folder, pattern = "\\.pdf$", full.names = TRUE, ignore.case = TRUE)
  tibble(
    case_id  = case_id,
    filepath = pdfs,
    doc_type = map_chr(pdfs, detect_doc_type)
  )
}) %>%
  filter(doc_type != "unknown") %>%
  arrange(case_id, doc_type)

#doc_inventory <- doc_inventory %>% filter(case_id == "1077")

cat(sprintf("Found %d documents across %d cases:\n",
            nrow(doc_inventory), n_distinct(doc_inventory$case_id)))
print(count(doc_inventory, doc_type))
```

## ── COMBINE MULTI-PART VERDICTS AND JUDGEMENTS ───────────────────────────────

```{r combine_pdfs}
# For cases with more than one verdict or judgement file, merge all PDFs into a
# single combined PDF using qpdf::pdf_combine(). This works for both scanned/
# handwritten and digital PDFs since it merges at the page level without touching
# content. The combined PDF is written to a session temp file and replaces the
# individual rows in doc_inventory so the pipeline makes only one API call per
# case per doc type.
#
# Cases with a single file are passed through unchanged.
# Files are sorted alphabetically before combining (e.g. Verdict_A, Verdict_B)
# to ensure deterministic ordering.

combine_dir <- file.path(tempdir(), "combined_pdfs")
dir.create(combine_dir, showWarnings = FALSE)

# Collect temp file paths so they can be cleaned up after the pipeline finishes
combined_temp_files <- character(0)

doc_inventory <- doc_inventory %>%
  group_by(case_id, doc_type) %>%
  group_modify(function(rows, key) {
    if (!(key$doc_type %in% c("verdict", "judgement"))) {
      return(rows)  # all other doc types passed through unchanged
    }

    sorted_files <- sort(rows$filepath)

    if (length(sorted_files) == 1) {
      return(rows)  # single file — no combining needed
    }

    # Build a descriptive temp filename, e.g. "1077_verdict_combined.pdf"
    out_name <- paste0(key$case_id, "_", key$doc_type, "_combined.pdf")
    out_path <- file.path(combine_dir, out_name)

    tryCatch(
      qpdf::pdf_combine(sorted_files, output = out_path),
      error = function(e) {
        warning(sprintf(
          "Could not combine %s PDFs for case %s: %s — using first file only.",
          key$doc_type, key$case_id, conditionMessage(e)
        ))
        file.copy(sorted_files[1], out_path, overwrite = TRUE)
      }
    )

    combined_temp_files <<- c(combined_temp_files, out_path)

    # Return a single-row tibble replacing all individual rows
    tibble(filepath = out_path)
  }) %>%
  ungroup() %>%
  arrange(case_id, doc_type)

n_combined <- sum(combined_temp_files %in% doc_inventory$filepath)
cat(sprintf(
  "PDF combining complete. %d combined file(s) created across %d cases.\n",
  length(combined_temp_files), n_distinct(doc_inventory$case_id)
))
cat(sprintf("doc_inventory now has %d rows (%d unique cases).\n",
            nrow(doc_inventory), n_distinct(doc_inventory$case_id)))
print(count(doc_inventory, doc_type))
```

## ── PROMPTS (Claude) ─────────────────────────────────────────────────────────

```{r prompts}

# ── VERDICT ───────────────────────────────────────────────────────────────────
# All verdict fields are extracted in a single API call.
# Claude reads the PDF directly including handwritten content.

verdict_system_prompt <- "Respond with only a valid JSON object. Do not include any text, analysis, explanation,
or markdown before or after the JSON. Do not use code fences. Begin your response
with { and end with }. You are a legal data analyst extracting structured information
from jury verdict forms in US civil cases. The form may be handwritten. Read all
handwritten text carefully. In some cases the document you receive is a combined PDF
containing multiple verdict forms concatenated together — for example, one form per
plaintiff in a multi-plaintiff case. When multiple forms are present, aggregate values across all of them (e.g.
sum monetary awards, union party lists, take the total plaintiff and defendant counts
across all forms). If forms conflict on outcome, note the conflict in Verdict_note. Return ONLY the JSON object with no preamble, analysis, or explanation before or
after it. Do not summarize the document or explain your reasoning. Output nothing
except the JSON object itself. Do not include explanations, reasoning, markdown, or
commentary. Do not wrap the JSON in markdown code fences."

verdict_user_prompt <- "Extract the following fields from this jury verdict form and
return them as a single JSON object with exactly these key names.

--- PARTY TYPE (Pl_type_verdict, Def_type_verdict) ---
Record the type of each plaintiff and defendant. Use: individual, corporation, or the specific government entity type such as city, county, or school. If all parties on one side are the same type, do not repeat. List each distinct type once. If an individual is represented by their estate, record as individual. If multiple types exist, separate with a comma. 
Individuals may appear in their professional capacity (like
sheriffs or superintendents) with their position included in their title. Treat
them as individuals irrespective of their position. 

--- GENDER (Pl_gender_verdict, Def_gender_verdict) ---
For individual plaintiffs/defendants only, infer gender from the name (Male /
Female / Unknown). If there are both male and female parties on one side, write
mixed. Leave null if all parties on that side are not individuals. Record the
gender of the individual even if they appear in a professional capacity.

--- COUNTS (Number_pl_verdict, Number_def_verdict) ---
Count the total number of plaintiffs and defendants. If an individual is represented by their estate, count as one. Include consolidated parties in the total. Exclude counter-plaintiffs, counter-defendants, and third parties. Exclude terminated parties. Do not count separately an individual who appears only as a guardian/representative for a minor unless they also appear individually.

--- OUTCOME (Outcome_verdict, Verdict_note) ---
Determine whether the verdict favors the plaintiff or defendant. If a successful counterclaim means the defense wins more money than the plaintiff, record Outcome as defendant. If the plaintiff is found 50% or more liable, record Outcome as defendant. Otherwise record as plaintiff.
Other outcomes may include:
settlement: if the jury was selected but a settlement happened before they could make a decision.
hung jury: a jury was selected but they could not come to a decision.
mistrial: a jury was selected but the judge declared a mistrial (for a reason other than a hung jury).
judgement as a matter of law: a jury was selected but the judge grants a judgement as a matter of law and the jury is dismissed.
If the jury is deciding only liability (damages already determined), record Verdict_note as liability only. If only deciding damages (liability already determined), record as damages only.

--- NON-ECONOMIC DAMAGES REQUESTED (Non_economic_damages_requested) ---
If the verdict form contains a line or space for a dollar value for non-economic damages — including pain and suffering, loss of consortium, emotional distress, physical impairment or disfigurement, mental anguish, impairment of quality of life, loss of enjoyment of life, deprivation of civil rights, or similar — record YES. Otherwise record NO.
Only record YES if the verdict form contains an explicit label or description identifying a line as non-economic damages. Do not infer that a generic 'actual damages' or 'compensatory damages' line includes non-economic damages unless the form expressly says so.
Example of YES: \"What amount of non-economic damages, including pain and suffering, does the jury award? $___\"
Example of NO: \"What amount of actual damages does the jury award? $___\" — record NO even in a civil rights case, because the form does not explicitly label the line as non-economic damages.

--- PUNITIVE DAMAGES REQUESTED (Punitive_damages_requested) ---
If the verdict form contains a line or space for punitive or exemplary damages, record YES. Otherwise record NO.

--- PLAINTIFF LIABILITY (Percent_plaintiff_liable) ---
If the verdict finds the plaintiff partially liable, record the percentage and the claim or amount that the percentage applies to. Otherwise null.

--- DAMAGES ITEMIZED (Damages_itemized) ---
For each question or line item on the verdict form that requests or awards a dollar
amount, record an entry with the following fields:
  question: the label or question text on the form, shortened to a clear description
  amount: the dollar amount filled in, as a plain number with no commas or dollar
    signs; 0 if the defendant won that line item; null if the space was left blank
    or no amount was awarded
  recipient: plaintiff if the amount is awarded to the plaintiff, defendant if
    awarded to the defendant
  type: noneconomic if the item is a non-economic damage (pain and suffering, loss
    of consortium, emotional distress, physical impairment, mental anguish, loss of
    enjoyment of life, deprivation of civil rights, or similar); punitive if the
    item is punitive or exemplary damages; economic for all other damage types;
    null if indeterminate
Include every line item that has a dollar amount field, even if the amount is blank
or zero. If the document contains multiple verdict forms, include line items from
all forms. If a damages line item has a blank or unfilled amount, record \"amount\": 0, not an
empty object or empty string. Only use null for the amount if the line item does not
exist on the form at all. For each line item, record the amount after applying any applicable defendant
liability percentage. For example, if the jury awards $100,000 but finds the
defendant only 70% liable, record the amount as $70,000.

--- MULTI-DOCUMENT HANDLING ---
This document may be a combined PDF containing multiple verdict forms. If so, apply
the following rules:
- Party type: take the union of types across all forms.
- Gender: take the union of gender types across all forms.
- Counts: count total unique plaintiffs and defendants across all forms; do not
  double-count the same party appearing on multiple forms.
- Outcome: the plaintiff wins overall if any form results in a monetary award to
  the plaintiff, even if other forms find for the defendant. Only record defendant
  if every form finds for the defendant or awards nothing to the plaintiff.
- Non-economic damages requested: record YES if any form contains a space for
  non-economic damages, even if other forms do not.
- Punitive damages requested: record YES if any form contains a space for punitive
  damages, even if other forms do not.
- Damages itemized: include line items from all forms; if forms cover different
  plaintiffs or claims, note which form each item came from in the question field
  (e.g. 'Form 1 — Pain and suffering').
- Plaintiff liability: consider the percentage across all forms; if multiple forms
  specify different percentages, record the one that applies to the largest award.
- Verdict_note: note that the document contains multiple verdict forms and briefly
  describe the structure (e.g. '3 verdict forms: one per plaintiff').

--- FORMAT RULES ---
Record all dollar amounts as plain numbers with no commas or dollar signs.
Use null for any field that is not present, not applicable, or cannot be determined.
Return ONLY the JSON object below with no additional text.

{
  \"Pl_type_verdict\": \"string — comma-separated distinct plaintiff types\",
  \"Def_type_verdict\": \"string — comma-separated distinct defendant types\",
  \"Pl_gender_verdict\": \"Male / Female / Mixed / null\",
  \"Def_gender_verdict\": \"Male / Female / Mixed / null\",
  \"Number_pl_verdict\": numeric,
  \"Number_def_verdict\": numeric,
  \"Outcome_verdict\": \"plaintiff or defendant\",
  \"Verdict_note\": \"string or null — liability only / damages only / or other notable context\",
  \"Non_economic_damages_requested\": \"YES or NO\",
  \"Punitive_damages_requested\": \"YES or NO\",
  \"Percent_plaintiff_liable\": string or null,
  \"Damages_itemized\": [
    {
      \"question\": \"string — label or description of the line item\",
      \"amount\": numeric or null,
      \"recipient\": \"plaintiff or defendant\",
      \"type\": \"economic / noneconomic / punitive / null\"
    }
  ]
}"


# ── judgement ──────────────────────────────────────────────────────────────────
judgement_system_prompt <- "Respond with only a valid JSON object. Do not include any text, analysis, explanation,
or markdown before or after the JSON. Do not use code fences. Begin your response
with { and end with }. You are a legal data analyst extracting structured information
from court judgement documents in US civil cases. In some cases the document you receive
is a combined PDF containing multiple judgement documents concatenated together for example, as separate judgements for different plaintiffs. When multiple documents are present, aggregate values across
all of them (e.g. union party lists, take total plaintiff and defendant counts across
all documents). If documents conflict on outcome, note the conflict in a Verdict_note field. Return ONLY
valid JSON with no additional text. Do not include explanations, reasoning, markdown,
or commentary. Do not wrap the JSON in markdown code fences."

judgement_user_prompt <- "Extract the following field from this judgement document and
return it as a JSON object:

--- PARTY TYPE (Pl_type_judgement, Def_type_judgement) ---
Record the type of each plaintiff and defendant. Use: individual, corporation, or the
specific government entity type such as city, county, or school. If all parties on one
side are the same type do not repeat — list each distinct type once. If an individual
is represented by their estate, record as individual. If multiple types exist, separate
with a comma. Individuals may appear in their professional capacity (like
sheriffs or superintendents) with their position included in their title. Treat
them as individuals irrespective of their position. When in doubt, if a human name is present, classify as individual.

--- GENDER (Pl_gender_judgement, Def_gender_judgement) ---
For individual plaintiffs/defendants only, infer gender from the name (Male / Female /
Unknown). If there are both male and female parties on one side, write mixed. Leave
null if all parties on that side are not individuals. Record the gender of the individual even if they appear in a professional capacity. When in doubt, if a human name is present, classify as individual.

--- COUNTS (Number_pl_judgement, Number_def_judgement) ---
Count the total number of plaintiffs and defendants. If an individual is represented
by their estate, count as one. Include consolidated parties in the total. Exclude
counter-plaintiffs, counter-defendants, and third parties. Exclude terminated parties.
Do not count separately an individual who appears only as a guardian/representative
for a minor unless they also appear individually.

--- OUTCOME (Outcome_judgement) ---
Determine whether the verdict favors the plaintiff or defendant. Other outcomes may include:
settlement: if the jury was selected but a settlement happened before they could 
make a decision. 
hung jury: a jury was selected but they could not come to a decision 
mistrial: a jury was selected but the judge declared a mistrial (for a reason 
other than a hung jury) 
judgement as a matter of law: a jury was selected but the judge grants a 
judgement as a matter of law and the jury is dismissed

--- FINAL JURY SIZE (SeatedJurySize_end) ---
Record the size of the jury that decided the verdict if included. Look through the entire verdict for any mention of jury size. It usually appears in the
first couple paragraphs of the document as something like 'tried before a jury
of X', 'tried before a jury of X duly sworn',
or 'tried before an empaneled jury of X'. Record the number X as a plain integer. 
Leave null if the verdict makes no mention of jury size.

--- MULTI-DOCUMENT HANDLING ---
This document may be a combined PDF containing multiple judgement documents. If so,
apply the following rules:
- Party type: take the union of types across all documents.
- Gender: take the union of gender types across all documents.
- Counts: count total unique plaintiffs and defendants across all documents; do not
  double-count the same party appearing on multiple documents.
- Outcome: the plaintiff wins overall if any document results in a monetary award to
  the plaintiff, even if other documents find for the defendant. Only record defendant
  if every document finds for the defendant or awards nothing to the plaintiff.
- Final jury size: look throughout all judgement documents for any mention of the
  size of the jury; record the first value found if consistent, or note a conflict
  in Verdict_note if documents disagree.
- Verdict_note: note that the document contains multiple judgement documents and
  briefly describe the structure (e.g. '3 judgement documents: one per plaintiff').

--- FORMAT RULES ---
Use null for any field that is not present, not applicable, or cannot be determined.
Return ONLY the JSON object below with no additional text.

{
  \"Pl_type_judgement\": \"string — comma-separated distinct plaintiff types\",
  \"Def_type_judgement\": \"string — comma-separated distinct defendant types\",
  \"Pl_gender_judgement\": \"Male / Female / Mixed / null\",
  \"Def_gender_judgement\": \"Male / Female / Mixed / null\",
  \"Number_pl_judgement\": numeric,
  \"Number_def_judgement\": numeric,
  \"Outcome_judgement\": \"plaintiff or defendant\",
  \"SeatedJurySize_end\": numeric or null
}"


# ── MINUTE ENTRY — DAY 1 ─────────────────────────────────────────────────────
# Used for minute files whose name contains both "minute" and "day_1".
# Extracts jury selection details and voir dire timing.

minute_day1_system_prompt <- "Respond with only a valid JSON object. Do not include any text, analysis, explanation,
or markdown before or after the JSON. Do not use code fences. Begin your response
with { and end with }. You are a legal data analyst extracting structured
information from Day 1 trial minute entries in US civil cases. These are chronological
logs of court proceedings. Times are recorded as timestamps (e.g. 9:05 a.m.).
Return ONLY valid JSON with no additional text. Do not include explanations, 
reasoning, markdown, or commentary. Do not wrap the JSON in markdown code fences."

minute_day1_user_prompt <- "Extract the following fields from this Day 1 minute entry
and return them as a single JSON object with exactly these key names. Do not include
anything else in your response.

--- TRIAL DATE (Trial_start_minutes) ---
The date of the first day of the jury trial as MM/DD/YYYY.

--- JUDGE (Judge_jury_trial_minutes) ---
The full name and title of the presiding judge as listed at the top of the document.
Include titles such as Judge, Magistrate Judge, or Chief Judge exactly as written.

--- FINAL JURY SIZE (SeatedJurySize_beg) ---
The number of jurors sworn to try the case after voir dire is complete. The minutes
may list individual juror IDs rather than a count — if so, count the IDs listed under
the swearing-in or selection entry. Do not count alternates separately unless the
document distinguishes them.

--- JURORS BROUGHT TO COURT (JuryPoolSize) ---
If the minutes state how many jurors were brought to court, record that number. This is 
different from the number called to the box for voir dire. Look for wording like X 
potential jurors are brought to the court. Ignore sentences like not X jurors are 
seated in the jury box prior to the court calling the case. Leave null if not mentioned.

--- EXCUSED FOR CAUSE (Excused_by_court) ---
The number of potential jurors excused by the court during voir dire for cause,
hardship, or at the court's direction. Include challenges for cause by either party
that result in removal. If individual juror IDs are listed as excused, count them
(do not double-count IDs that appear more than once). Leave null if the minutes make
no reference to jurors being excused for any reason other than peremptory challenge.
Do not include peremptory challenges in this count.

--- PLAINTIFF PEREMPTORY CHALLENGES (Plaintiff_challenges) ---
The number of peremptory challenges used by the plaintiff(s). Look for headings such
as Plaintiff's Peremptory Challenges, Plaintiff's Challenges, or Challenges by the
Plaintiff followed by a list of juror IDs. If not explicitly stated, count the juror
IDs listed under the plaintiff's challenges section.

--- DEFENDANT PEREMPTORY CHALLENGES (Defendant_challenges) ---
The number of peremptory challenges used by the defendant(s). Look for headings such
as Defendant's Peremptory Challenges, Defendant's Challenges, or Challenges by the
Defendant followed by a list of juror IDs. If not explicitly stated, count the juror
IDs listed under the defendant's challenges section.

--- VOIR DIRE START TIME (Voir_dire_start) ---
Record the timestamp at or directly before the start of voir dire. Look for events such
as: Voir dire by the court commences / Court voir dires jurors / Voir dire begins by
the Court / Voir dire of prospective jurors by the Court / Voir dire commences /
Voir dire begins / or similar. If the line noting the start of voir dire does not fall
neatly on a timestamp, record the nearest associated timestamp. Record as HH:MM AM/PM.
If no timestamps are present in the document, record null.

--- VOIR DIRE END TIME (Voir_dire_end) ---
Record the timestamp marking the end of voir dire. The end of voir dire is signaled by
the jury being sworn to try the case — look for a phrase like 'jurors sworn to try the
case', 'jury sworn', 'jury is empaneled', or similar.

Use the timestamp directly associated with the swearing entry. Only defer to the NEXT
timestamp if the swearing entry shares a timestamp with another event that has its own
explicit timestamp listed before it on the same line or entry. Untimed content such as
lists of juror numbers, peremptory challenges, or other unnumbered text appearing before
the swearing does NOT count as a prior event — in that case, still use the swearing
timestamp directly.

If the jury is sworn or empaneled with NO timestamp of its own, look at the most recent
timestamp before the swearing. If other substantive events occurred under that same
timestamp before the swearing (such as rulings, arguments, or court remarks), defer to
the NEXT timestamp after the swearing instead.

If no timestamps are present in the document, record null.

Examples:

Case 1 — swearing has its own timestamp with only untimed content before it, use it:
  [Peremptory challenges listed]
  10:10 a.m. Seven jurors sworn to try the case:  <-- use 10:10

Case 2 — swearing shares a timestamp with a prior TIMESTAMPED event, use the next:
  11:17 a.m. At the bench, counsel pass the panel for cause.
  [Jurors sworn to try the case]
  11:26 a.m. The Court instructs the jury.  <-- use 11:26

Case 3 — swearing has no timestamp and substantive events occurred under the prior
timestamp before the swearing, use the next timestamp after the swearing:
  12:33 p.m. Court in session.
  [Batson ruling, peremptory challenges listed]
  Jury is empaneled.
  12:56 p.m. Court in recess.  <-- use 12:56

Record as HH:MM AM/PM.

--- VOIR DIRE RECESSES (Voir_dire_recess_times) ---
Record each court recess that falls within the voir dire window (between Voir_dire_start
and Voir_dire_end, inclusive). A recess is marked by 'Court in Recess' followed by
'Court in Session'. Include any recess that begins before the jury is sworn, even if
it occurs after the last explicit voir dire activity and immediately precedes the
swearing. Do not include other types of breaks. For each recess record the start and
end time as a JSON array of objects with 'recess_start' and 'recess_end' fields.
If there are no recesses during voir dire, record an empty array [].
If no timestamps are present in the document, record null.

--- VOIR DIRE EXTRAS (VD_extras) ---
There may be other entries or events listed at the timestamp marking the start or
end of voir dire. Note any activity or event that occurred between the nearest 
timestamp and the actual start or end of voir dire (i.e. events recorded between 
the timestamp marker and the voir dire boundary event). Leave null if none.

{
  \"Trial_start_minutes\": \"MM/DD/YYYY or null\",
  \"Judge_jury_trial_minutes\": \"string or null\",
  \"SeatedJurySize_beg\": numeric or null,
  \"JuryPoolSize\": numeric or null,
  \"Excused_by_court\": numeric or null,
  \"Plaintiff_challenges\": numeric or null,
  \"Defendant_challenges\": numeric or null,
  \"Voir_dire_start\": \"HH:MM AM/PM or null\",
  \"Voir_dire_end\": \"HH:MM AM/PM or null\",
  \"Voir_dire_recess_times\": [
    {\"recess_start\": \"HH:MM AM/PM\", \"recess_end\": \"HH:MM AM/PM\"}
  ],
  \"VD_extras\": \"string or null\"
}"

# ── MINUTE ENTRY — FINAL DAY ──────────────────────────────────────────────────
# Used for minute files whose name contains "minute" and "final".
# This file records the day the verdict was reached. It contains the verdict date,
# final trial day number, and the end of deliberations. The deliberation start time
# may appear here OR at the end of the previous day's deliberation minutes.

minute_final_system_prompt <- "Respond with only a valid JSON object. Do not include any text, analysis, explanation,
or markdown before or after the JSON. Do not use code fences. Begin your response
with { and end with }. You are a legal data analyst extracting structured
information from final-day trial minute entries in US civil cases. These are
chronological logs with timestamps. Return ONLY valid JSON with
no additional text. Do not include explanations, reasoning, markdown, or commentary.
Do not wrap the JSON in markdown code fences."

minute_final_user_prompt <- "Extract the following fields from this final-day minute
entry and return them as a single JSON object with exactly these key names.


--- FINAL TRIAL DAY (NumberofDaysinTrial) ---
The day number of the jury trial recorded at the top of these minutes, found in a
heading such as 'Trial to Jury - Day X'. Record the integer X.

--- VERDICT DATE (Verdict_date_minutes) ---
The date that the verdict was decided, in the format MM/DD/YYYY.

--- DELIBERATION START TIME (Delib_start_time) ---
The timestamp marking the start of jury deliberations if it appears in this document.
Look for 'Jury to begin deliberations', 'Jury excused to begin deliberations',
'Jury to commence deliberations', or similar.

Use the timestamp directly associated with the deliberation entry. However, if that
same timestamp also contains other events listed before the deliberation entry (such
as closing arguments), do not use that timestamp — instead
use the timestamp of the next 'Court in recess' entry, as this marks when the jury
physically leaves to begin deliberating.

If no timestamps are present in the document, record null. If the document opens 
with a statement that the jury is already in deliberations (e.g. 'Jury is in deliberations')
without a preceding start entry, leave null — deliberations began on a prior day.

Examples:

Case 1 — deliberation entry has its own timestamp, use it directly:
  2:15 p.m. Jury excused to begin deliberations.  <-- use 2:15

Case 2 — deliberation entry shares a timestamp with prior events, use next recess:
  12:04 p.m. Rebuttal closing argument by Mr. Sulton.
  Bailiff sworn. Jury to begin deliberations.
  12:30 p.m. Court in recess.  <-- use 12:30

--- DELIBERATION END TIME (Delib_end_time) ---
The timestamp marking the end of jury deliberations. Look for the moment the court
is informed the jury has reached a verdict — phrases like 'Court Security Officer
advises the jurors have reached a verdict', 'jury has reached a verdict', 'verdict
reached', or similar notification to the court. Use that timestamp as the end of
deliberations, not the later timestamp when the jury is escorted back into the
courtroom.

If no such notification timestamp exists, fall back to the earliest timestamp
associated with 'Court in session' immediately before the verdict is read.
Record the time exactly as written.

--- PARTY TYPE (Pl_type_minutes, Def_type_minutes) ---
Record the type of each plaintiff and defendant. Use: individual, corporation, or the
specific government entity type such as city, county, or school. If all parties on one
side are the same type do not repeat — list each distinct type once. If an individual
is represented by their estate, record as individual. If multiple types exist, separate
with a comma.

--- TIMESTAMP FORMAT ---
When recording any timestamp, always include AM or PM (e.g. '1:00 PM', '3:38 PM',
'9:07 AM'). If the document does not include AM/PM, infer it from context — trial
proceedings typically run between 8 AM and 6 PM.

{
  \"NumberofDaysinTrial\": numeric or null,
  \"Verdict_date_minutes\": MM/DD/YYYY or null,
  \"Delib_start_time\": \"string or null\",
  \"Delib_end_time\": \"string or null\",
  \"Pl_type_minutes\": \"string — comma-separated distinct plaintiff types\",
  \"Def_type_minutes\": \"string — comma-separated distinct defendant types\"
}"


# ── MINUTE ENTRY — DELIBERATION DAYS ──────────────────────────────────────────
# Used for all minute files that are not Day 1 or the final day.
# These correspond to days where deliberations were ongoing but no verdict was reached.
# Each file may record:
#   - The end-of-day adjournment time (when the jury stopped deliberating)
#   - The start-of-day resumption time (when the jury resumed the next morning)
#   - A deliberation start time if deliberations first began on this day
# The R assembly step uses these times across all deliberation-day files to compute
# total deliberation time.

minute_deliberation_system_prompt <- "Respond with only a valid JSON object. Do not include any text, analysis, explanation,
or markdown before or after the JSON. Do not use code fences. Begin your response
with { and end with }. You are a legal data analyst extracting
structured information from mid-trial deliberation day minute entries in US civil
cases. These are chronological logs with timestamps. Return ONLY valid JSON with
no additional text. Do not include explanations, reasoning, markdown, or commentary.
Do not wrap the JSON in markdown code fences."

minute_deliberation_user_prompt <- "Extract the following fields from this deliberation day minute entry and return them as a single JSON object with exactly these key names.
--- DELIBERATION START TIME (Delib_start_time) ---
The timestamp marking the first start of jury deliberations IF deliberations began for the first time on this day. Look for 'Jury excused to begin deliberations', 'Jury to commence deliberations', 'The Jury excused to begin deliberations', or similar. Use the timestamp directly associated with the deliberation entry. However, if that same timestamp also contains other events listed before the deliberation entry (such as closing arguments), do not use that timestamp — instead use the timestamp of the next 'Court in recess' entry, as this marks when the jury physically leaves to begin deliberating.
If the deliberation entry has its own distinct timestamp that appears alone or with only untimed content, use that timestamp directly even if a 'Court in recess' entry follows shortly after.
Leave null if deliberations had already been underway from a prior day.
Leave null if the jury was instructed but sent home before deliberating — i.e., if deliberations are only scheduled to begin on a future day. A time announced for a future day's deliberations belongs only in Delib_next_day_start, never in Delib_start_time.
If no timestamps are present in the document, record null.
--- END OF DAY ADJOURNMENT (Delib_adjourn_time) ---
The time at which the jury stopped deliberating for the day without reaching a verdict. Look first for an explicit timestamp near the end of the document associated with 'Court in recess', 'Jury excused until [date/time]', 'Court adjourned', or similar.
If no explicit timestamp exists for the adjournment, also check for a parenthetical or narrative note embedded in the document (e.g. 'Jury recessed deliberations at 4:50 p.m. and will resume tomorrow morning at 9:00 a.m.'). If such a note exists, extract the adjournment time from it and record it.
Record the time exactly as written.
--- NEXT DAY RESUMPTION (Delib_resume_time) ---
If this document also records the time deliberations resumed after a prior adjournment (i.e. the jury returned and continued deliberating from a previous day), record that timestamp. Look for 'Jury present', 'Court in session', 'Deliberations resume', or similar at the start of deliberation activity. Leave null if deliberations first began on this day rather than resuming.
--- NEXT DAY DELIBERATION START (Delib_next_day_start) ---
If the jury is sent home at the end of this day and given a specific time to return and begin deliberations the next day, record that future start time. Look for phrases like 'Jury is in recess until [date], commencing at [time] to commence deliberations', 'Jury adjourned to return at [time] to begin deliberations', 'Jury in recess until [date] at [time]', or parenthetical notes like 'will resume tomorrow morning at 9:00 a.m.'. Record only the time (e.g. '9:00 AM'), not the date.
Leave null if no such instruction appears or if deliberations have already begun.

--- TIMESTAMP FORMAT ---
When recording any timestamp, always include AM or PM (e.g. '1:00 PM', '3:38 PM',
'9:07 AM'). If the document does not include AM/PM, infer it from context — trial
proceedings typically run between 8 AM and 6 PM.

{
  \"Delib_start_time\": \"string or null\",
  \"Delib_adjourn_time\": \"string or null\",
  \"Delib_resume_time\": \"string or null\",
  \"Delib_next_day_start\": \"string or null\"
}"


# ── DOCKET ────────────────────────────────────────────────────────────────────
# Docket PDFs are pre-processed with pdftools to extract only the header and
# docket entries, skipping the lengthy plaintiff/defendant party block.
# The extracted plain text is sent to Claude as a text message (not a PDF),
# which is cheaper and faster since the text layer is already clean.

docket_system_prompt <- "Respond with only a valid JSON object. Do not include any text, analysis, explanation,
or markdown before or after the JSON. Do not use code fences. Begin your response
with { and end with }. You are a legal data analyst extracting structured information
from US federal district court dockets (PACER). The document includes a case header
followed by chronological docket entries. Ignore the plaintiff and defendant party
sections entirely. Extract information only from the header and docket entries.
Return ONLY valid JSON with no additional text. Do not include explanations,
reasoning, markdown, or commentary. Do not wrap the JSON in markdown code fences."

docket_user_prompt <- "Extract the following fields from this court docket and return
them as a single JSON object with exactly these key names.

--- INITIAL JUDGE — DOCKET ENTRIES (Judge_initial_assignment) ---
Scan the docket entries to find the FIRST entry that explicitly assigns or draws
any judge — whether a district judge, chief judge, or magistrate judge — to the
case. The first assignment is almost always one of these forms:
  'Case assigned to [Judge Name]'
  'Case assigned to Magistrate Judge [Name]'
  'Case drawn to Judge [Name]'
  'Case reassigned to [Judge Name]. [Prior judge] no longer assigned.'
In the reassignment case, record the DEPARTING judge as the initial assignment.

Record the judge's full name and title exactly as written in the docket entry text
(e.g. 'Magistrate Judge Boyd N. Boland', 'Chief Judge Marcia S. Krieger').

Do NOT use the 'Assigned to:' line from the case header — that reflects the judge
at the time the docket was printed, not the initial assignment.

Do NOT skip an entry simply because the assigned judge is a magistrate judge —
magistrate judges are frequently the first judge assigned to a case, especially
in prisoner civil rights cases.

Ignore entries related to summary dismissal screening, IFP motions, or other
purely administrative preliminary matters that do not constitute a formal case
assignment. A 'Case assigned to' or 'Case drawn to' entry always constitutes a
formal assignment regardless of the judge's title.

--- MAGISTRATE JUDGE — DOCKET ENTRIES (Magistrate_assignment) ---
Scan the docket entries to find the FIRST entry that explicitly assigns or draws
a magistrate judge to the case. Look for any of these patterns:
  'Case assigned to Judge [X] and drawn to Magistrate Judge [Y]' — record [Y]
  'Case assigned to Magistrate Judge [Y]' — record [Y]
  'Case drawn to Magistrate Judge [Y]' — record [Y]
  'Case reassigned to Magistrate Judge [Y]' — record [Y]
  'Order referring case to Magistrate Judge [Y]' — record [Y]
  'Order of reference to Magistrate Judge [Y]' — record [Y]
  'Case referred to Magistrate Judge [Y]' — record [Y]

The first magistrate assignment often appears in the same entry as the initial
district judge assignment, as 'Case assigned to Judge [X] and drawn to Magistrate
Judge [Y]'. Do not skip this entry — 'drawn to' is equivalent to 'assigned to'
for magistrate judges.

Record the judge's full name and title exactly as written (e.g. 'Magistrate Judge
Kathleen M. Tafoya'). Do NOT record a later reassignment as the initial assignment
even if that magistrate judge handles most of the subsequent proceedings.

Ignore entries related to purely administrative preliminary matters that do not
constitute a formal assignment. If no explicit assignment entry exists, leave null.

--- JURY TRIAL IDENTIFICATION ---
Scan all docket entries for jury trial proceedings. These appear as entries like
'Jury Trial Day 1', 'Jury Trial - Day One', 'Day 1 Jury Trial', or similar.
Group consecutive jury trial day entries into distinct trial sequences.

If there are multiple trial sequences (e.g., a first trial that ended in a mistrial
or hung jury followed by a second trial), identify each separately. Select the LAST
trial sequence that ended with a jury verdict, judgment, or other final resolution —
NOT one that ended in a mistrial, hung jury, or was declared incomplete.

For each date: read the date from WITHIN the docket entry text itself — look for
phrases like 'held on [date]' or 'proceedings held on [date]'. Do NOT use the date
in the leftmost date column, which is the filing or entry date, not the proceeding date.

--- JURY TRIAL FIRST DATE (Trial_start_docket) ---
The date of Day 1 of the final completed jury trial, in MM/DD/YYYY format. Extract
from the docket entry text (e.g. 'Jury Trial Day One held on [date]').

--- JURY TRIAL LAST DATE (Verdict_date_docket) ---
The date of the final day of the last completed jury trial — the day a verdict was
reached or the trial otherwise concluded. Extract from the docket entry text.

--- PRESIDING JUDGE (Judge_jury_trial_docket) ---
The judge named in the jury trial day entries as presiding over the final completed
trial. Include full name and title as written. If different judges presided on
different days, record the judge who presided on the day the verdict was reached.

--- TRIAL SEQUENCE NOTE (Multiple_trials_note) ---
If only one trial sequence is found, leave null. If multiple trial sequences are
found, briefly describe them — e.g. 'Two trial sequences: first trial March 2007
ended in mistrial; second trial August 2005 returned verdict.' Note if multiple
sequences were found so the researcher can verify.

--- OUTCOME (Outcome_docket) ---
Determine whether the verdict favors the plaintiff or defendant. If a successful
counterclaim means the defense wins more money than the plaintiff, record Outcome as
defendant. If the plaintiff is found 50% or more liable, record Outcome as defendant.
Otherwise record as plaintiff. 
Other outcomes may include:
settlement: if the jury was selected but a settlement happened before they could 
make a decision. 
hung jury: a jury was selected but they could not come to a decision 
mistrial: a jury was selected but the judge declared a mistrial (for a reason 
other than a hung jury) 
judgement as a matter of law: a jury was selected but the judge grants a 
judgement as a matter of law and the jury is dismissed

--- NUMBER OF TRIAL DAYS (NumberofDaysinTrial_docket) ---
Count the number of jury trial day entries in the final completed trial sequence.
Each day appears as a separate docket entry with text like 'Minute Entry - Courtroom
Minutes for Jury Trial held on [date]' or 'Jury Trial completed on [date]'. Count
each distinct date as one trial day. Include the final day (the day the verdict was
reached) in the count. If there are multiple trial sequences, count only the days
belonging to the final completed sequence.
If multiple trial sequences are present, count only the days belonging to the
final completed trial sequence, consistent with the sequence identified for
Trial_start_docket and Verdict_date_docket. Note the total across all sequences
in Multiple_trials_note (e.g. 'Final trial: 4 days; first trial (mistrial): 3 days').

{
  \"Judge_initial_assignment\": \"string or null\",
  \"Magistrate_assignment\": \"string or null\",
  \"Trial_start_docket\": \"MM/DD/YYYY or null\",
  \"Verdict_date_docket\": \"MM/DD/YYYY or null\",
  \"Judge_jury_trial_docket\": \"string or null\",
  \"Outcome_docket\": \"plaintiff or defendant\",
  \"NumberofDaysinTrial_docket\": numeric or null,
  \"Multiple_trials_note\": \"string or null\"
}"
```

## ── CLAUDE API FUNCTION ─────────────────────────────────────────────────────

```{r claude_function}
# Builds a single batch request object for one document.
# Returns a named list compatible with the Anthropic batch API format.
build_batch_request <- function(custom_id, filepath, doc_type) {

  sys_prompt <- switch(doc_type,
    verdict             = verdict_system_prompt,
    judgement           = judgement_system_prompt,
    docket              = docket_system_prompt,
    minute_day1         = minute_day1_system_prompt,
    minute_final        = minute_final_system_prompt,
    minute_deliberation = minute_deliberation_system_prompt
  )
  user_prompt <- switch(doc_type,
    verdict             = verdict_user_prompt,
    judgement           = judgement_user_prompt,
    docket              = docket_user_prompt,
    minute_day1         = minute_day1_user_prompt,
    minute_final        = minute_final_user_prompt,
    minute_deliberation = minute_deliberation_user_prompt
  )

  if (doc_type == "docket") {
    docket_text <- extract_docket_text(filepath)
    combined    <- paste0(user_prompt, "\n\n--- DOCKET TEXT ---\n", docket_text)
    params <- list(
      model       = "claude-sonnet-4-6",
      max_tokens  = 3000,
      temperature = 0,
      system      = sys_prompt,
      messages    = list(
        list(role = "user", content = combined)
      )
    )
  } else {
    pdf_b64 <- encode_pdf(filepath)
    params <- list(
      model       = "claude-sonnet-4-6",
      max_tokens  = 3000,
      temperature = 0,
      system      = sys_prompt,
      messages    = list(
        list(
          role    = "user",
          content = list(
            list(
              type   = "document",
              source = list(
                type       = "base64",
                media_type = "application/pdf",
                data       = pdf_b64
              )
            ),
            list(type = "text", text = user_prompt)
          )
        )
      )
    )
  }

  list(custom_id = custom_id, params = params)
}

# Submit a list of batch requests to the Anthropic batch API.
# Returns the batch ID for polling.
submit_batch <- function(requests) {
  body <- list(requests = requests)
  response <- POST(
    url   = "https://api.anthropic.com/v1/messages/batches",
    add_headers(
      `x-api-key`         = anthropic_key,
      `anthropic-version` = "2023-06-01",
      `anthropic-beta`    = "message-batches-2024-09-24",
      `content-type`      = "application/json"
    ),
    body   = toJSON(body, auto_unbox = TRUE),
    encode = "raw"
  )
  parsed <- content(response, as = "parsed", type = "application/json")
  if (http_error(response)) {
    stop(paste0("Batch submit error [", status_code(response), "]: ",
                parsed$error$message %||% "Unknown error"))
  }
  message("Batch submitted. ID: ", parsed$id)
  parsed$id
}

# Poll the batch status until it completes (processing_status == "ended").
# Checks every poll_interval_secs seconds.
poll_batch <- function(batch_id, poll_interval_secs = 60) {
  repeat {
    response <- GET(
      url = paste0("https://api.anthropic.com/v1/messages/batches/", batch_id),
      add_headers(
        `x-api-key`         = anthropic_key,
        `anthropic-version` = "2023-06-01",
        `anthropic-beta`    = "message-batches-2024-09-24"
      )
    )
    parsed <- content(response, as = "parsed", type = "application/json")
    status <- parsed$processing_status
    counts <- parsed$request_counts
    message(sprintf(
      "[%s] Batch status: %s | succeeded: %d, errored: %d, processing: %d",
      format(Sys.time(), "%H:%M:%S"),
      status,
      counts$succeeded %||% 0,
      counts$errored   %||% 0,
      counts$processing %||% 0
    ))
    if (status == "ended") break
    Sys.sleep(poll_interval_secs)
  }
  message("Batch complete.")
  parsed$results_url
}

# Download and parse batch results from the results URL.
# Returns a named list: custom_id -> list(raw_text, total_tokens, error)
fetch_batch_results <- function(results_url) {
  response <- GET(
    url = results_url,
    add_headers(
      `x-api-key`         = anthropic_key,
      `anthropic-version` = "2023-06-01",
      `anthropic-beta`    = "message-batches-2024-09-24"
    )
  )
  raw_text <- content(response, as = "text", encoding = "UTF-8")
  # Results are newline-delimited JSON
  lines <- str_split(raw_text, "\n")[[1]]
  lines <- lines[nzchar(lines)]
  results_list <- map(lines, ~{
    tryCatch(fromJSON(.x, simplifyVector = FALSE), error = function(e) NULL)
  })
  results_list <- Filter(Negate(is.null), results_list)
  # Index by custom_id for easy lookup
  setNames(results_list, map_chr(results_list, ~.x$custom_id))
}
```

## ── TOKEN PRE-CHECK (optional — run before main pipeline to estimate cost) ───

```{r token_precheck, eval=FALSE}
# Calls the free token-counting endpoint on one sample doc of each type.
# Does not run inference. Use this to verify cost before running the full pipeline.

count_tokens_claude <- function(filepath, doc_type) {
  sys_prompt  <- switch(doc_type,
    verdict  = verdict_system_prompt,
    judgement = judgement_system_prompt,
    minute   = minute_deliberation_system_prompt)
  user_prompt <- switch(doc_type,
    verdict  = verdict_user_prompt,
    judgement = judgement_user_prompt,
    minute   = minute_deliberation_user_prompt)
  pdf_b64 <- encode_pdf(filepath)
  body <- list(
    model    = "claude-sonnet-4-6",
    system   = sys_prompt,
    messages = list(list(
      role    = "user",
      content = list(
        list(type = "document",
             source = list(type = "base64", media_type = "application/pdf", data = pdf_b64)),
        list(type = "text", text = user_prompt)
      )
    ))
  )
  response <- POST(
    url     = "https://api.anthropic.com/v1/messages/count_tokens",
    add_headers(`x-api-key` = anthropic_key,
                `anthropic-version` = "2023-06-01",
                `content-type` = "application/json"),
    body   = toJSON(body, auto_unbox = TRUE),
    encode = "raw"
  )
  parsed <- content(response, as = "parsed", type = "application/json")
  parsed$input_tokens %||% NA_real_
}

sample_docs <- doc_inventory %>% group_by(doc_type) %>% slice(1) %>% ungroup()
token_ests  <- sample_docs %>%
  mutate(input_tokens = map2_dbl(filepath, doc_type, count_tokens_claude))

avg_input       <- mean(token_ests$input_tokens, na.rm = TRUE)
n_docs          <- nrow(doc_inventory)
est_input_cost  <- (avg_input * n_docs / 1e6) * 3
est_output_cost <- (300 * n_docs / 1e6) * 15

cat(sprintf(
  "\n=== COST ESTIMATE ===
Claude -- %d documents:
  Avg input tokens/doc: %.0f
  Est. input cost:      $%.4f
  Est. output cost:     $%.4f
  Est. total:           $%.4f\n",
  n_docs, avg_input,
  est_input_cost, est_output_cost, est_input_cost + est_output_cost
))
```

## ── MAIN PIPELINE: BATCH SUBMISSION ──────────────────────────────────────────

```{r main_pipeline}
run_id  <- format(Sys.time(), "%Y%m%d_%H%M%S")
out_dir <- file.path(getwd(), paste0("court_run_", run_id))
dir.create(out_dir, showWarnings = FALSE)

# ── STEP 1: Build batch requests ─────────────────────────────────────────────
# Each request gets a unique custom_id encoding its row index, case_id, and
# doc_type so results can be matched back to doc_inventory after retrieval.
message("Building batch requests for ", nrow(doc_inventory), " documents...")

batch_requests <- pmap(
  list(
    seq_len(nrow(doc_inventory)),
    doc_inventory$filepath,
    doc_inventory$doc_type
  ),
  function(i, filepath, doc_type) {
    custom_id <- paste0("row", sprintf("%04d", i),
                        "_", doc_inventory$case_id[i],
                        "_", doc_type)
    tryCatch(
      build_batch_request(custom_id, filepath, doc_type),
      error = function(e) {
        message(sprintf("  Skipping row %d (%s / %s): %s",
                        i, doc_inventory$case_id[i], doc_type,
                        conditionMessage(e)))
        NULL
      }
    )
  }
)

# Remove any requests that failed to build
batch_requests <- Filter(Negate(is.null), batch_requests)
message(sprintf("Built %d requests successfully.", length(batch_requests)))

# Save the request index for matching results later
request_index <- doc_inventory %>%
  mutate(
    row_idx   = seq_len(n()),
    custom_id = paste0("row", sprintf("%04d", row_idx),
                       "_", case_id, "_", doc_type)
  )
saveRDS(request_index, file.path(out_dir, "request_index.rds"))

# ── STEP 2: Submit batch ──────────────────────────────────────────────────────
batch_id <- submit_batch(batch_requests)
saveRDS(batch_id, file.path(out_dir, "batch_id.rds"))
message("Batch ID saved to: ", file.path(out_dir, "batch_id.rds"))
message("Batch is processing. Results available within 24 hours.")
message("Run the 'retrieve_batch' chunk below once the batch is complete.")
```

## ── RETRIEVE BATCH RESULTS (run after batch completes) ───────────────────────

```{r retrieve_batch}
# Load batch ID and request index from the run directory.
# Set out_dir to the folder from your batch submission run before running this.
# run_id <- "20260522_220306"
# out_dir <- "court_run_20260522_220306"

batch_id      <- readRDS(file.path(out_dir, "batch_id.rds"))
request_index <- readRDS(file.path(out_dir, "request_index.rds"))

# Poll until complete (skips polling if already ended — safe to re-run)
results_url <- poll_batch(batch_id)

# Download results
message("Downloading results...")
batch_results <- fetch_batch_results(results_url)
message(sprintf("Retrieved %d results.", length(batch_results)))

# ── Match results back to doc_inventory ──────────────────────────────────────
results <- request_index %>%
  mutate(
    raw_reply = map_chr(custom_id, function(cid) {
      res <- batch_results[[cid]]
      if (is.null(res)) return(NA_character_)
      if (res$result$type == "error") return(NA_character_)
      res$result$message$content[[1]]$text %||% NA_character_
    }),
    total_tokens = map_dbl(custom_id, function(cid) {
      res <- batch_results[[cid]]
      if (is.null(res) || res$result$type == "error") return(NA_real_)
      usage <- res$result$message$usage
      (usage$input_tokens %||% 0) + (usage$output_tokens %||% 0)
    }),
    api_error = map_chr(custom_id, function(cid) {
      res <- batch_results[[cid]]
      if (is.null(res)) return("No result returned for this custom_id")
      if (res$result$type == "error") {
        return(paste0(res$result$error$type, ": ",
                      res$result$error$message %||% "Unknown error"))
      }
      NA_character_
    }),
    elapsed_sec = NA_real_,
    processed   = !is.na(raw_reply)
  ) %>%
  select(-row_idx, -custom_id)

# Save results checkpoint
saveRDS(results, file.path(out_dir, "court_pipeline_checkpoint.rds"))
write_csv(results, file.path(out_dir, "court_pipeline_batch_results.csv"))

n_success <- sum(results$processed)
n_error   <- sum(!is.na(results$api_error))
message(sprintf("Results: %d succeeded, %d errors, %d total.",
                n_success, n_error, nrow(results)))
```

## ── OUTPUTS TO CSVs ────────────────────────────────────────

```{r parse_outputs}
# ── VERDICT CSV ──────────────────────────────────────────────────────────────
verdict_claude <- results %>%
  filter(doc_type == "verdict", !is.na(raw_reply)) %>%
  mutate(parsed = map(raw_reply, ~{
    json_str <- str_extract(.x, "\\{[\\s\\S]*\\}")
    tryCatch(fromJSON(json_str, simplifyVector = FALSE), error = function(e) NULL)
  })) %>%
  filter(!map_lgl(parsed, is.null)) %>%
  mutate(
    Pl_type_verdict               = map_chr(parsed, ~safe_field(.x, "Pl_type_verdict")),
    Def_type_verdict              = map_chr(parsed, ~safe_field(.x, "Def_type_verdict")),
    Pl_gender_verdict             = map_chr(parsed, ~safe_field(.x, "Pl_gender_verdict")),
    Def_gender_verdict            = map_chr(parsed, ~safe_field(.x, "Def_gender_verdict")),
    Number_pl_verdict             = map_chr(parsed, ~safe_field(.x, "Number_pl_verdict")),
    Number_def_verdict            = map_chr(parsed, ~safe_field(.x, "Number_def_verdict")),
    Outcome_verdict               = map_chr(parsed, ~safe_field(.x, "Outcome_verdict")),
    Verdict_note                  = map_chr(parsed, ~safe_field(.x, "Verdict_note")),
    Non_economic_damages_requested = map_chr(parsed, ~safe_field(.x, "Non_economic_damages_requested")),
    Punitive_damages_requested    = map_chr(parsed, ~safe_field(.x, "Punitive_damages_requested")),
    Percent_plaintiff_liable      = map_chr(parsed, ~safe_field(.x, "Percent_plaintiff_liable")),

    # Store itemized damages array as a JSON string for the CSV
    Damages_itemized = map_chr(parsed, ~{
      val <- .x[["Damages_itemized"]]
      if (is.null(val) || length(val) == 0) return(NA_character_)
      tryCatch(toJSON(val, auto_unbox = TRUE), error = function(e) NA_character_)
    }),

    Monetary_award = map_dbl(parsed, ~{
      items <- .x[["Damages_itemized"]]
      if (is.null(items) || length(items) == 0) return(NA_real_)
      amounts <- map_dbl(items, function(item) {
        amt <- item[["amount"]]
        if (is.null(amt) || length(amt) == 0) return(0)
        val <- suppressWarnings(as.numeric(amt))
        if (is.na(val)) return(0)
        if (identical(item[["recipient"]], "plaintiff")) return(val)
        if (identical(item[["recipient"]], "defendant"))  return(-val)
        return(0)
      })
      sum(amounts, na.rm = TRUE)
    }),

    Non_economic_damages_awarded = map_dbl(parsed, ~{
      items <- .x[["Damages_itemized"]]
      if (is.null(items) || length(items) == 0) return(NA_real_)
      amounts <- map_dbl(items, function(item) {
        if (!identical(item[["recipient"]], "plaintiff")) return(0)
        if (!identical(item[["type"]], "noneconomic")) return(0)
        amt <- item[["amount"]]
        if (is.null(amt) || length(amt) == 0) return(NA_real_)
        suppressWarnings(as.numeric(amt))
      })
      if (all(amounts == 0, na.rm = TRUE) && !any(is.na(amounts))) NA_real_
      else if (any(is.na(amounts))) NA_real_
      else sum(amounts)
    }),

    Punitive_damages_awarded = map_dbl(parsed, ~{
      items <- .x[["Damages_itemized"]]
      if (is.null(items) || length(items) == 0) return(NA_real_)
      amounts <- map_dbl(items, function(item) {
        if (!identical(item[["recipient"]], "plaintiff")) return(0)
        if (!identical(item[["type"]], "punitive")) return(0)
        amt <- item[["amount"]]
        if (is.null(amt) || length(amt) == 0) return(NA_real_)
        suppressWarnings(as.numeric(amt))
      })
      if (all(amounts == 0, na.rm = TRUE) && !any(is.na(amounts))) NA_real_
      else if (any(is.na(amounts))) NA_real_
      else sum(amounts)
    }),

    Damages_sum_check = map_chr(parsed, ~{
      items <- .x[["Damages_itemized"]]
      if (is.null(items) || length(items) == 0) return("no itemized damages")
      any_null <- any(map_lgl(items, function(item) {
        amt <- item[["amount"]]
        is.null(amt) || length(amt) == 0
      }))
      if (any_null) "verify — one or more line items had no amount" else "ok"
    })
  ) %>%
  select(case_id, filepath,
         Pl_type_verdict, Def_type_verdict, Pl_gender_verdict, Def_gender_verdict,
         Number_pl_verdict, Number_def_verdict,
         Outcome_verdict, Verdict_note,
         Non_economic_damages_requested, Punitive_damages_requested,
         Monetary_award, Non_economic_damages_awarded, Punitive_damages_awarded,
         Percent_plaintiff_liable, Damages_itemized, Damages_sum_check)

output_verdicts <- verdict_claude

#write_csv(output_verdicts, "output_verdicts.csv")
#message("Saved output_verdicts.csv — ", nrow(output_verdicts), " rows")

# ── judgement CSV ──────────────────────────────────────────────────────────────
output_judgement <- results %>%
  filter(doc_type == "judgement", !is.na(raw_reply)) %>%
  mutate(parsed = map(raw_reply, ~{
    json_str <- str_extract(.x, "\\{[\\s\\S]*\\}")
    tryCatch(fromJSON(json_str, simplifyVector = FALSE), error = function(e) NULL)
  })) %>%
  filter(!map_lgl(parsed, is.null)) %>%
  mutate(
    Pl_type_judgement    = map_chr(parsed, ~safe_field(.x, "Pl_type_judgement")),
    Def_type_judgement   = map_chr(parsed, ~safe_field(.x, "Def_type_judgement")),
    Pl_gender_judgement  = map_chr(parsed, ~safe_field(.x, "Pl_gender_judgement")),
    Def_gender_judgement = map_chr(parsed, ~safe_field(.x, "Def_gender_judgement")),
    Number_pl_judgement  = map_chr(parsed, ~safe_field(.x, "Number_pl_judgement")),
    Number_def_judgement = map_chr(parsed, ~safe_field(.x, "Number_def_judgement")),
    Outcome_judgement    = map_chr(parsed, ~safe_field(.x, "Outcome_judgement")),
    SeatedJurySize_end   = map_chr(parsed, ~safe_field(.x, "SeatedJurySize_end"))
  ) %>%
  select(case_id, filepath,
         Pl_type_judgement, Def_type_judgement, Pl_gender_judgement,
         Def_gender_judgement, Number_pl_judgement, Number_def_judgement,
         Outcome_judgement, SeatedJurySize_end)

#write_csv(output_judgement, "output_judgement.csv")
#message("Saved output_judgement.csv — ", nrow(output_judgement), " rows")

# ── MINUTE DAY 1 CSV ─────────────────────────────────────────────────────────
output_minutes_day1 <- results %>%
  filter(doc_type == "minute_day1", !is.na(raw_reply)) %>%
  mutate(parsed = map(raw_reply, ~{
    json_str <- stringr::str_extract(.x, "\\{[\\s\\S]*\\}")
    tryCatch(jsonlite::fromJSON(json_str, simplifyVector = FALSE),
             error = function(e) NULL)
  })) %>%
  filter(!map_lgl(parsed, is.null)) %>%
  mutate(
    Trial_start_minutes      = map_chr(parsed, ~safe_field(.x, "Trial_start_minutes")),
    Judge_jury_trial_minutes = map_chr(parsed, ~safe_field(.x, "Judge_jury_trial_minutes")),
    SeatedJurySize_beg       = map_chr(parsed, ~safe_field(.x, "SeatedJurySize_beg")),
    JuryPoolSize             = map_chr(parsed, ~safe_field(.x, "JuryPoolSize")),
    Excused_by_court         = map_chr(parsed, ~safe_field(.x, "Excused_by_court")),
    Plaintiff_challenges     = map_chr(parsed, ~safe_field(.x, "Plaintiff_challenges")),
    Defendant_challenges     = map_chr(parsed, ~safe_field(.x, "Defendant_challenges")),
    Voir_dire_start          = map_chr(parsed, ~safe_field(.x, "Voir_dire_start")),
    Voir_dire_end            = map_chr(parsed, ~safe_field(.x, "Voir_dire_end")),

    Voir_dire_recess_times = map_chr(parsed, ~{
      val <- .x[["Voir_dire_recess_times"]]
      if (is.null(val) || length(val) == 0) return(NA_character_)
      tryCatch(toJSON(val, auto_unbox = TRUE), error = function(e) NA_character_)
    }),

    Voir_dire_recess_length = map_dbl(parsed, ~{
      val <- .x[["Voir_dire_recess_times"]]
      if (is.null(val) || length(val) == 0) return(0)
      recess_mins <- map_dbl(val, function(r) {
        s <- r[["recess_start"]]
        e <- r[["recess_end"]]
        if (is.null(s) || is.null(e)) return(NA_real_)
        time_diff_mins(s, e)
      })
      if (any(is.na(recess_mins))) NA_real_ else sum(recess_mins)
    }),

    Voir_dire_time = map_dbl(parsed, ~{
      vd_start <- safe_field(.x, "Voir_dire_start")
      vd_end   <- safe_field(.x, "Voir_dire_end")
      if (is.na(vd_start) || is.na(vd_end)) return(NA_real_)
      gross <- time_diff_mins(vd_start, vd_end)
      if (is.na(gross)) return(NA_real_)
      val <- .x[["Voir_dire_recess_times"]]
      recess_total <- if (is.null(val) || length(val) == 0) {
        0
      } else {
        recess_mins <- map_dbl(val, function(r) {
          s <- r[["recess_start"]]
          e <- r[["recess_end"]]
          if (is.null(s) || is.null(e)) return(NA_real_)
          time_diff_mins(s, e)
        })
        if (any(is.na(recess_mins))) return(NA_real_)
        sum(recess_mins)
      }
      gross - recess_total
    }),

    VD_extras = map_chr(parsed, ~safe_field(.x, "VD_extras"))
  ) %>%
  select(case_id, filepath, Trial_start_minutes, Judge_jury_trial_minutes,
         SeatedJurySize_beg, JuryPoolSize,
         Excused_by_court, Plaintiff_challenges, Defendant_challenges,
         Voir_dire_start, Voir_dire_end, Voir_dire_recess_times,
         Voir_dire_recess_length, Voir_dire_time, VD_extras)

#write_csv(output_minutes_day1, "output_minutes_day1.csv")
#message("Saved output_minutes_day1.csv — ", nrow(output_minutes_day1), " rows")

# ── MINUTE FINAL CSV ─────────────────────────────────────────────────────────
output_minutes_final <- results %>%
  filter(doc_type == "minute_final", !is.na(raw_reply)) %>%
  mutate(parsed = map(raw_reply, ~{
    json_str <- str_extract(.x, "\\{[\\s\\S]*\\}")
    tryCatch(fromJSON(json_str, simplifyVector = FALSE), error = function(e) NULL)
  })) %>%
  filter(!map_lgl(parsed, is.null)) %>%
  mutate(
    NumberofDaysinTrial  = map_chr(parsed, ~safe_field(.x, "NumberofDaysinTrial")),
    Verdict_date_minutes = map_chr(parsed, ~safe_field(.x, "Verdict_date_minutes")),
    Delib_start_time     = map_chr(parsed, ~safe_field(.x, "Delib_start_time")),
    Delib_end_time       = map_chr(parsed, ~safe_field(.x, "Delib_end_time")),
    Pl_type_minutes      = map_chr(parsed, ~safe_field(.x, "Pl_type_minutes")),
    Def_type_minutes     = map_chr(parsed, ~safe_field(.x, "Def_type_minutes"))
  ) %>%
  select(case_id, filepath, Pl_type_minutes, Def_type_minutes,
         NumberofDaysinTrial, Verdict_date_minutes,
         Delib_start_time, Delib_end_time)

#write_csv(output_minutes_final, "output_minutes_final.csv")
#message("Saved output_minutes_final.csv — ", nrow(output_minutes_final), " rows")


# ── MINUTE DELIBERATION DAYS CSV ──────────────────────────────────────────────
output_minutes_delib <- results %>%
  filter(doc_type == "minute_deliberation", !is.na(raw_reply)) %>%
  mutate(parsed = map(raw_reply, ~{
    json_str <- str_extract(.x, "\\{[\\s\\S]*\\}")
    tryCatch(fromJSON(json_str, simplifyVector = FALSE), error = function(e) NULL)
  })) %>%
  filter(!map_lgl(parsed, is.null)) %>%
  mutate(
    Delib_start_time     = map_chr(parsed, ~safe_field(.x, "Delib_start_time")),
    Delib_adjourn_time   = map_chr(parsed, ~safe_field(.x, "Delib_adjourn_time")),
    Delib_resume_time    = map_chr(parsed, ~safe_field(.x, "Delib_resume_time")),
    Delib_next_day_start = map_chr(parsed, ~safe_field(.x, "Delib_next_day_start")),
  ) %>%
  select(case_id, filepath, Delib_start_time, Delib_adjourn_time,
         Delib_resume_time, Delib_next_day_start)

#write_csv(output_minutes_delib, "output_minutes_delib.csv")
#message("Saved output_minutes_delib.csv — ", nrow(output_minutes_delib), " rows")


# ── DELIBERATION LENGTH ASSEMBLY ──────────────────────────────────────────────
# Per-day contribution from deliberation-day files
delib_day_contributions <- output_minutes_delib %>%
  mutate(
    day_start = as.character(ifelse(!is.na(Delib_resume_time) & nzchar(Delib_resume_time),
                                    Delib_resume_time, Delib_start_time)),
    day_end   = as.character(Delib_adjourn_time),
    day_mins  = map2_dbl(day_start, day_end, time_diff_mins)
  ) %>%
  select(case_id, filepath, day_start, day_end, day_mins)

# Get next-day deliberation start times from deliberation-day files as fallback
delib_next_day_starts <- output_minutes_delib %>%
  filter(!is.na(Delib_next_day_start) & nzchar(Delib_next_day_start)) %>%
  select(case_id, Delib_next_day_start)

# Per-case contribution from final-day file
final_day_contributions <- output_minutes_final %>%
  left_join(delib_next_day_starts, by = "case_id") %>%
  mutate(
    day_start = as.character(case_when(
      !is.na(Delib_start_time) & nzchar(Delib_start_time) ~ Delib_start_time,
      !is.na(Delib_next_day_start)                         ~ Delib_next_day_start,
      TRUE                                                  ~ NA_character_
    )),
    day_end  = as.character(Delib_end_time),
    day_mins = map2_dbl(day_start, day_end, time_diff_mins)
  ) %>%
  select(case_id, filepath, day_start, day_end, day_mins)

# Combine all days per case with a deliberation day number
all_delib_days <- bind_rows(
  delib_day_contributions %>% 
    filter(!is.na(day_start) | !is.na(day_end)) %>%  # drop empty holding days
    select(case_id, day_start, day_end, day_mins),
  final_day_contributions %>% distinct(case_id, .keep_all = TRUE) %>%
    select(case_id, day_start, day_end, day_mins)
) %>%
  group_by(case_id) %>%
  mutate(delib_day = row_number()) %>%
  ungroup()

# Build Delib_schedule JSON array: one entry per deliberation day
delib_schedule <- all_delib_days %>%
  group_by(case_id) %>%
  summarise(
    Delib_schedule = {
      entries <- cur_data()
      toJSON(map(seq_len(nrow(entries)), function(i) {
        list(
          day   = entries$delib_day[i],
          start = if (is.na(entries$day_start[i])) NULL else entries$day_start[i],
          end   = if (is.na(entries$day_end[i]))   NULL else entries$day_end[i],
          mins  = if (is.na(entries$day_mins[i]))  NULL else entries$day_mins[i]
        )
      }), auto_unbox = TRUE)
    },
    .groups = "drop"
  )

# Count deliberation days: one per delib-day file + 1 for the final day
deliberation_days <- output_minutes_delib %>%
  group_by(case_id) %>%
  summarise(Deliberation_days = n(), .groups = "drop")

deliberation_totals <- all_delib_days %>%
  group_by(case_id) %>%
  summarise(
    Deliberation_time = if (any(is.na(day_mins))) NA_real_ else sum(day_mins),
    any_na = any(is.na(day_mins)),
    .groups = "drop"
  ) %>%
  left_join(
    final_day_contributions %>% distinct(case_id),
    by = "case_id"
  ) %>%
  left_join(deliberation_days, by = "case_id") %>%
  left_join(delib_schedule, by = "case_id") %>%
  mutate(
    Deliberation_time_flag = if_else(
      any_na,
      "one or more days had unresolvable times — verify manually",
      NA_character_
    ),
    Deliberation_days = replace_na(Deliberation_days, 0) + 1
  ) %>%
  select(case_id, Deliberation_time, Deliberation_time_flag,
         Deliberation_days, Delib_schedule)

#write_csv(deliberation_totals, "output_deliberation_totals.csv")
#message("Saved output_deliberation_totals.csv — ", nrow(deliberation_totals), " cases")

# ── DOCKET CSV ────────────────────────────────────────────────────────────────
output_docket <- results %>%
  filter(doc_type == "docket", !is.na(raw_reply)) %>%
  mutate(parsed = map(raw_reply, ~{
    json_str <- str_extract(.x, "\\{[\\s\\S]*\\}")
    tryCatch(fromJSON(json_str, simplifyVector = FALSE), error = function(e) NULL)
  })) %>%
  filter(!map_lgl(parsed, is.null)) %>%
  mutate(
    Judge_initial_assignment = map_chr(parsed, ~safe_field(.x, "Judge_initial_assignment")),
    Magistrate_assignment    = map_chr(parsed, ~safe_field(.x, "Magistrate_assignment")),
    Trial_start_docket                    = map_chr(parsed, ~safe_field(.x, "Trial_start_docket")),
    Verdict_date_docket                   = map_chr(parsed, ~safe_field(.x, "Verdict_date_docket")),
    Judge_jury_trial_docket               = map_chr(parsed, ~safe_field(.x, "Judge_jury_trial_docket")),
    NumberofDaysinTrial_docket            = map_chr(parsed, ~safe_field(.x, "NumberofDaysinTrial_docket")),
    Outcome_docket                        = map_chr(parsed, ~safe_field(.x, "Outcome_docket")),
    Multiple_trials_note                  = map_chr(parsed, ~safe_field(.x, "Multiple_trials_note"))
  ) %>%
  select(case_id, filepath,
         Judge_initial_assignment,
         Magistrate_assignment,
         Trial_start_docket, Verdict_date_docket, Judge_jury_trial_docket,
         Outcome_docket, NumberofDaysinTrial_docket, Multiple_trials_note)

#write_csv(output_docket, "output_docket.csv")
#message("Saved output_docket.csv — ", nrow(output_docket), " rows")

# Merge all tibbles into one CSV
dfs <- list(
  output_verdicts,
  output_judgement,
  output_minutes_day1,
  output_minutes_final,
  deliberation_totals,
  output_docket
) %>%
  map(~ select(.x, -any_of("filepath")))

final_df <- reduce(dfs, full_join, by = "case_id")

# ── REORDER COLUMNS ───────────────────────────────────────────────────────────
col_order <- c(
  "case_id",
  "Pl_type_verdict", "Pl_type_judgement", "Pl_type_minutes",
  "Def_type_verdict", "Def_type_judgement", "Def_type_minutes",
  "Pl_gender_verdict", "Pl_gender_judgement", 
  "Def_gender_verdict", "Def_gender_judgement",
  "Number_pl_verdict", "Number_pl_judgement",
  "Number_def_verdict", "Number_def_judgement", "Number_def_minutes",
  "Trial_start_minutes", "Trial_start_docket",
  "Verdict_date_minutes", "Verdict_date_docket",
  "NumberofDaysinTrial", "NumberofDaysinTrial_docket", "Multiple_trials_note",
  "Judge_initial_assignment", "Magistrate_assignment",
  "Judge_jury_trial_minutes", "Judge_jury_trial_docket",
  "SeatedJurySize_beg", "SeatedJurySize_end",
  "JuryPoolSize", "Excused_by_court",
  "Plaintiff_challenges", "Defendant_challenges",
  "Voir_dire_start", "Voir_dire_end",
  "Voir_dire_recess_times", "Voir_dire_recess_length", "Voir_dire_time",
  "VD_extras",
  "Deliberation_time", "Deliberation_time_flag", "Deliberation_days",
  "Delib_schedule",
  "Non_economic_damages_requested", "Punitive_damages_requested",
  "Monetary_award", "Damages_itemized", "Damages_sum_check",
  "Outcome_verdict", "Outcome_judgement", "Outcome_docket",
  "Verdict_note",
  "Non_economic_damages_awarded", "Punitive_damages_awarded",
  "Percent_plaintiff_liable" 
)

col_order_valid <- col_order[col_order %in% names(final_df)]
remaining <- setdiff(names(final_df), col_order_valid)
final_df <- final_df %>% select(all_of(c(col_order_valid, remaining)))

# ── CONVERT JSON COLUMNS TO READABLE TEXT FOR CSV OUTPUT ─────────────────────

format_recess_times <- function(json_str) {
  if (is.na(json_str) || !nzchar(json_str)) return(NA_character_)
  tryCatch({
    items <- fromJSON(json_str, simplifyVector = FALSE)
    if (length(items) == 0) return(NA_character_)
    map_chr(items, function(r) {
      paste0(r[["recess_start"]], " to ", r[["recess_end"]])
    }) %>% paste(collapse = "; ")
  }, error = function(e) NA_character_)
}

format_delib_schedule <- function(json_str) {
  if (is.na(json_str) || !nzchar(json_str)) return(NA_character_)
  tryCatch({
    items <- fromJSON(json_str, simplifyVector = FALSE)
    if (length(items) == 0) return(NA_character_)
    map_chr(items, function(d) {
      mins <- if (!is.null(d[["mins"]])) paste0(", ", round(d[["mins"]]), " min") else ""
      paste0("Day ", d[["day"]], ": ", d[["start"]], " to ", d[["end"]], mins)
    }) %>% paste(collapse = "; ")
  }, error = function(e) NA_character_)
}

final_df <- final_df %>%
  mutate(
    Voir_dire_recess_times = map_chr(Voir_dire_recess_times, format_recess_times),
    Delib_schedule         = map_chr(Delib_schedule, format_delib_schedule)
  )

final_df <- final_df %>% select(-any_of(c("Delib_start_time", "Delib_end_time")))

readr::write_excel_csv(
  final_df,
  file.path(out_dir, paste0("merged_output_", run_id, ".csv"))
)

message("  Cases needing manual review for deliberation: ",
        sum(!is.na(deliberation_totals$Deliberation_time_flag)))

# ── ERROR LOG ─────────────────────────────────────────────────────────────────
errors <- results %>%
  filter(!is.na(api_error)) %>%
  mutate(source = "Claude") %>%
  select(case_id, doc_type, filepath, source, error = api_error)

if (nrow(errors) > 0) {
  write_csv(errors, file.path(out_dir, "output_errors.csv"))
  message("Saved output_errors.csv — ", nrow(errors), " failed calls to investigate")
} else {
  message("No errors — all API calls succeeded")
}

# ── CLEANUP COMBINED TEMP FILES ───────────────────────────────────────────────
if (length(combined_temp_files) > 0) {
  file.remove(combined_temp_files[file.exists(combined_temp_files)])
  message("Cleaned up ", length(combined_temp_files), " temporary combined PDF(s).")
}
```

