# Court Document Analysis Pipeline (Two-Step Hybrid)
#
# VERDICT forms (handwritten):
#   Step 1 — Google Document AI Form Parser extracts handwritten field values
#             with per-field confidence scores
#   Step 2 — Claude reads the same PDF for Yes/No findings and overall context
#             The two outputs are merged: Google DAI numbers + Claude decisions
#
# judgement and MINUTE documents (typed PDFs):
#   Claude only — no OCR step needed
#
# Output: three CSVs, one per document type


## ── SETUP ────────────────────────────────────────────────────────────────────
# Before running:
#   1. Install packages if needed:
#        install.packages(c("tidyverse","httr","jsonlite","purrr","base64enc","gargle"))
#   2. Create a config.R file in the same directory as this script (see template below)
#   3. Add config.R to your .gitignore — NEVER commit it to version control
#
# config.R should define these variables:
#   anthropic_key        <- "***REMOVED***..."
#   google_key_path      <- "~/path/to/google-service-account-key.json"
#   google_project_id    <- "your-gcp-project-id"
#   google_location      <- "us"   # "us" or "eu"
#   google_processor_id  <- "your-processor-id"
#   cases_root           <- "~/path/to/your/cases"
#   confidence_threshold <- 0.90
#
# Google Document AI one-time setup:
#   a. Create a Google Cloud project at console.cloud.google.com
#   b. Enable the Document AI API
#   c. Create a Form Parser processor:
#        Document AI > Overview > Explore Processors > Form Parser > Create
#   d. Note your Project ID, Processor ID (hex string), and Location ("us" or "eu")
#   e. Create a Service Account with the "Document AI API User" role
#   f. Download the JSON key file and set its path in config.R

```{r setup}
library(tidyverse)
library(httr)
library(jsonlite)
library(dplyr)
library(purrr)
library(base64enc)
library(gargle)        # handles Google OAuth — install.packages("gargle")

# Load Google Cloud credentials and API key (DO NOT SHARE THIS FILE)
source("config.R")
```


## ── HELPERS ──────────────────────────────────────────────────────────────────

```{r helpers}
`%||%` <- function(x, y) {
  if (is.null(x) || length(x) == 0) y else x
}

# Encode a local PDF to base64 string
encode_pdf <- function(filepath) {
  base64encode(readBin(filepath, "raw", file.info(filepath)$size))
}

# Detect document type from filename.
# More-specific minute types are checked first so they take priority over the
# general "minute" fallback.
#   minute_day1         — filename contains "minute" and "day1"
#   minute_final        — filename contains "minute" and "final"
#   minute_deliberation — all other minute files (contain "minute" but not day1 or final)
detect_doc_type <- function(filename) {
  fname <- tolower(basename(filename))
  if (str_detect(fname, "verdict"))                                return("verdict")
  if (str_detect(fname, "judgement"))                              return("judgement")
  if (str_detect(fname, "minute") && str_detect(fname, "day1"))   return("minute_day1")
  if (str_detect(fname, "minute") && str_detect(fname, "final"))  return("minute_final")
  if (str_detect(fname, "minute"))                                 return("minute_deliberation")
  return("unknown")
}

# Safely extract a named field from a parsed JSON list
safe_field <- function(json_list, field, default = NA_character_) {
  val <- json_list[[field]]
  if (is.null(val) || length(val) == 0) default else as.character(val)
}

# Serialize Google DAI form fields into a compact text block for Claude.
# This is appended to the verdict user prompt so Claude can cross-reference
# the OCR readings rather than reading handwritten dollar amounts cold.
# Only fields with a non-empty value are included to keep the block concise.
format_dai_for_prompt <- function(fields_df) {
  if (is.null(fields_df) || nrow(fields_df) == 0) {
    return("(No OCR reference data available for this document.)")
  }
  rows <- fields_df %>%
    filter(!is.na(field_value), nzchar(field_value)) %>%
    mutate(line = sprintf("  %s: %s (confidence: %.0f%%)",
                          field_name, field_value,
                          value_confidence * 100))
  if (nrow(rows) == 0) return("(No OCR reference data available for this document.)")
  paste0(
    "--- OCR REFERENCE BLOCK (Google Document AI pre-extraction) ---\n",
    paste(rows$line, collapse = "\n"),
    "\n--- END OF OCR REFERENCE BLOCK ---"
  )
}

sleep_if_needed <- function(results, j, limit = 30000) {

  # look back ~60 seconds worth of recent calls (approx via last N docs)
  window <- max(1, j - 10):j

  recent_tokens <- sum(results$total_tokens[window], na.rm = TRUE)

  if (recent_tokens > limit) {
    message("Rate limit protection triggered: sleeping 10s...")
    Sys.sleep(10)
  }
}
```


## ── BUILD CASE INVENTORY ─────────────────────────────────────────────────────

```{r inventory}
case_folders <- list.dirs(cases_root, recursive = FALSE)

doc_inventory <- map_dfr(case_folders, function(folder) {
  case_id <- basename(folder)
  pdfs    <- list.files(folder, pattern = "\\.pdf$", full.names = TRUE, ignore.case = TRUE)
  tibble(
    case_id  = case_id,
    filepath = pdfs,
    doc_type = map_chr(pdfs, detect_doc_type)
  )
}) %>%
  filter(doc_type != "unknown") %>%
  arrange(case_id, doc_type)

#doc_inventory <- doc_inventory %>% filter(case_id == "1000309")

cat(sprintf("Found %d documents across %d cases:\n",
            nrow(doc_inventory), n_distinct(doc_inventory$case_id)))
print(count(doc_inventory, doc_type))
```


## ── PROMPTS (Claude) ─────────────────────────────────────────────────────────
# Verdict prompts ask only for Yes/No findings and fault percentages.
# Dollar amounts come from Google Document AI — Claude is not asked for them.

```{r prompts}

# ── VERDICT ───────────────────────────────────────────────────────────────────
# All verdict fields are extracted in a single API call.
# Handwritten dollar amounts are read by Google Document AI and passed in as an
# OCR reference block appended to the user prompt at runtime — see
# format_dai_for_prompt() and get_claude_response() below.

verdict_system_prompt <- "You are a legal data analyst extracting structured information
from jury verdict forms in US civil cases. The form may be handwritten. You will be
provided with a reference block of field values pre-extracted by an OCR tool — use
these as your primary source for dollar amounts and percentages, but use the document
itself as the authoritative source for all other fields. Return ONLY valid JSON with
no additional text. Do not include explanations, reasoning, markdown, or commentary.
Do not wrap the JSON in markdown code fences."

verdict_user_prompt <- "Extract the following fields from this jury verdict form and
return them as a single JSON object with exactly these key names.

--- PARTY TYPE (Pl_type, Def_type) ---
Record the type of each plaintiff and defendant. Use: individual, corporation, or the
specific government entity type such as city, county, or school. If all parties on one
side are the same type do not repeat — list each distinct type once. If an individual
is represented by their estate, record as individual. If multiple types exist, separate
with a comma.

--- GENDER (Pl_gender, Def_gender) ---
For individual plaintiffs/defendants only, infer gender from the name (Male / Female /
Unknown). If there are both male and female parties on one side, write mixed. Leave
null if all parties on that side are not individuals.

--- COUNTS (Number_pl, Number_def) ---
Count the total number of plaintiffs and defendants. If an individual is represented
by their estate, count as one. Include consolidated parties in the total. Exclude
counter-plaintiffs, counter-defendants, and third parties. Exclude terminated parties.
Do not count separately an individual who appears only as a guardian/representative
for a minor unless they also appear individually.

--- OUTCOME (Outcome, Verdict_note) ---
Determine whether the verdict favors the plaintiff or defendant. Use the verdict
document as the primary source; if outcome cannot be determined from the verdict alone,
note that the judgement document should be consulted. If the jury is deciding only
liability (damages already determined), record Verdict_note as liability only. If only
deciding damages (liability already determined), record as damages only. If a
successful counterclaim means the defense wins more money than the plaintiff, record
Outcome as defendant. If the plaintiff is found 50% or more liable, record Outcome as
defendant. Otherwise record as plaintiff.

--- NON-ECONOMIC DAMAGES REQUESTED (Non_economic_damages_requested) ---
If the verdict form contains a line or space for a dollar value for non-economic
damages — including pain and suffering, loss of consortium, emotional distress,
physical impairment or disfigurement, mental anguish, impairment of quality of life,
loss of enjoyment of life, deprivation of civil rights, or similar — record YES.
Otherwise record NO.

--- PUNITIVE DAMAGES REQUESTED (Punitive_damages_requested) ---
If the verdict form contains a line or space for punitive or exemplary damages,
record YES. Otherwise record NO.

--- MONETARY AWARD (Monetary_award) ---
Total monetary value awarded to the plaintiff including economic, non-economic, and
punitive damages combined. Record 0 if the defendant won. If the defendant is less
than 100% liable, scale the total damages by the defendant liability percentage. If
the verdict indicates the plaintiff award will be reduced by a specific amount (due to
a counterclaim or failure to mitigate), subtract that amount. Use the OCR reference
block below as the primary source for dollar amounts.

--- NON-ECONOMIC DAMAGES AWARDED (Non_economic_damages_awarded) ---
Total non-economic damages awarded. Record 0 if the defendant won. Keywords include:
pain and suffering, loss of consortium, emotional distress, physical impairment,
mental anguish, impairment of quality of life, loss of enjoyment of life, deprivation
of civil rights, and similar. Leave null if the verdict does not specify the nature or
division of damages.

--- PUNITIVE DAMAGES AWARDED (Punitive_damages_awarded) ---
Total punitive or exemplary damages awarded. Record 0 if the defendant won.

--- PLAINTIFF LIABILITY (Percent_plaintiff_liable) ---
If the verdict finds the plaintiff partially liable, record the percentage. Otherwise null.

--- FORMAT RULES ---
Record all dollar amounts as plain numbers with no commas or dollar signs.
Use null for any field that is not present, not applicable, or cannot be determined.
Return ONLY the JSON object below with no additional text.

{
  \"Pl_type\": \"string — comma-separated distinct plaintiff types\",
  \"Def_type\": \"string — comma-separated distinct defendant types\",
  \"Pl_gender\": \"Male / Female / Mixed / null\",
  \"Def_gender\": \"Male / Female / Mixed / null\",
  \"Number_pl\": numeric,
  \"Number_def\": numeric,
  \"Outcome\": \"plaintiff or defendant\",
  \"Verdict_note\": \"string or null — liability only / damages only / or other notable context\",
  \"Non_economic_damages_requested\": \"YES or NO\",
  \"Punitive_damages_requested\": \"YES or NO\",
  \"Monetary_award\": numeric,
  \"Non_economic_damages_awarded\": numeric or null,
  \"Punitive_damages_awarded\": numeric,
  \"Percent_plaintiff_liable\": numeric or null,
  \"verdict_date\": \"MM/DD/YYYY or null\",
  \"notes\": \"string or null — anything unusual about the form or findings\"
}"


# ── judgement ──────────────────────────────────────────────────────────────────
judgement_system_prompt <- "You are a legal data analyst extracting structured information
from court judgement documents in US civil cases. Return ONLY valid JSON with
no additional text. Do not include explanations, reasoning, markdown, or commentary.
Do not wrap the JSON in markdown code fences."

judgement_user_prompt <- "Extract the following field from this judgement document and
return it as a JSON object:

{
  \"Number_jurors\": numeric or null
}

Number_jurors: the number of jurors present at the end of the trial. Look for phrases
such as 'tried before a jury of X duly sworn', 'tried before an empaneled jury of X',
or similar. Record the number X as a plain integer. Leave null if no such statement
appears in the document."


# ── MINUTE ENTRY — DAY 1 ─────────────────────────────────────────────────────
# Used for minute files whose name contains both "minute" and "day_1".
# Extracts jury selection details and voir dire timing.

minute_day1_system_prompt <- "You are a legal data analyst extracting structured
information from Day 1 trial minute entries in US civil cases. These are chronological
logs of court proceedings. Times are recorded as timestamps (e.g. 9:05 a.m.).
Return ONLY valid JSON with no additional text. Do not include explanations, 
reasoning, markdown, or commentary.Do not wrap the JSON in markdown code fences."

minute_day1_user_prompt <- "Extract the following fields from this Day 1 minute entry
and return them as a single JSON object with exactly these key names.

--- TRIAL DATE (Trial_date) ---
The date of the first day of the jury trial as MM/DD/YYYY.

--- JUDGE (Judge) ---
The full name and title of the presiding judge as listed at the top of the document.
Include titles such as Judge, Magistrate Judge, or Chief Judge exactly as written.

--- FINAL JURY SIZE (Jury_size) ---
The number of jurors sworn to try the case after voir dire is complete. The minutes
may list individual juror IDs rather than a count — if so, count the IDs listed under
the swearing-in or selection entry. Do not count alternates separately unless the
document distinguishes them.

--- JURORS BROUGHT TO COURT (Jurors_brought) ---
If the minutes state how many jurors were brought to court (the jury pool brought in
before voir dire begins), record that number. This is distinct from the number called
to the box for voir dire. Leave null if not mentioned.

--- EXCUSED FOR CAUSE (Excused_for_cause) ---
The number of potential jurors excused by the court during voir dire for cause,
hardship, or at the court's direction. Include challenges for cause by either party
that result in removal. If individual juror IDs are listed as excused, count them
(do not double-count IDs that appear more than once). Leave null if the minutes make
no reference to jurors being excused for any reason other than peremptory challenge.
Do not include peremptory challenges in this count.

--- PLAINTIFF PEREMPTORY CHALLENGES (Pl_peremptory) ---
The number of peremptory challenges used by the plaintiff(s). Look for headings such
as Plaintiff's Peremptory Challenges, Plaintiff's Challenges, or Challenges by the
Plaintiff followed by a list of juror IDs. If not explicitly stated, count the juror
IDs listed under the plaintiff's challenges section.

--- DEFENDANT PEREMPTORY CHALLENGES (Def_peremptory) ---
The number of peremptory challenges used by the defendant(s). Look for headings such
as Defendant's Peremptory Challenges, Defendant's Challenges, or Challenges by the
Defendant followed by a list of juror IDs. If not explicitly stated, count the juror
IDs listed under the defendant's challenges section.

--- VOIR DIRE LENGTH (Voir_dire_minutes) ---
The duration of voir dire in minutes (integer). Calculate as follows:
  Start time: the timestamp at or directly before any of these events:
    Voir dire by the court commences / Court voir dires jurors /
    Voir dire begins by the Court / Voir dire of prospective jurors by the Court /
    Voir dire commences / Voir dire begins / or similar.
  End time: the earliest timestamp at or directly after any of these events:
    Jurors selected to try the case / Voir dire completed /
    Jurors sworn to try the case / Jurors called to try case / or similar.
Subtract any recess time that falls within the voir dire window.
Record the net duration as a plain integer number of minutes.

--- VOIR DIRE EXTRAS (Voir_Dire_Extras) ---
Note any activity or event that occurred between the nearest timestamp and the actual
start or end of voir dire (i.e. events recorded between the timestamp marker and the
voir dire boundary event). Leave null if none.

{
  \"Trial_date\": \"MM/DD/YYYY or null\",
  \"Judge\": \"string or null\",
  \"Jury_size\": numeric or null,
  \"Jurors_brought\": numeric or null,
  \"Excused_for_cause\": numeric or null,
  \"Pl_peremptory\": numeric or null,
  \"Def_peremptory\": numeric or null,
  \"Voir_dire_minutes\": numeric or null,
  \"Voir_Dire_Extras\": \"string or null\"
}"


# ── MINUTE ENTRY — FINAL DAY ──────────────────────────────────────────────────
# Used for minute files whose name contains "minute" and "final".
# This file records the day the verdict was reached. It contains the verdict date,
# final trial day number, and the end of deliberations. The deliberation start time
# may appear here OR at the end of the previous day's deliberation minutes.

minute_final_system_prompt <- "You are a legal data analyst extracting structured
information from final-day trial minute entries in US civil cases. These are
chronological logs with timestamps. Return ONLY valid JSON with
no additional text. Do not include explanations, reasoning, markdown, or commentary.
Do not wrap the JSON in markdown code fences."

minute_final_user_prompt <- "Extract the following fields from this final-day minute
entry and return them as a single JSON object with exactly these key names.


--- FINAL TRIAL DAY (Final_trial_day) ---
The day number of the jury trial recorded at the top of these minutes, found in a
heading such as 'Trial to Jury - Day X'. Record the integer X.

--- DELIBERATION START TIME (Delib_start_time) ---
The timestamp marking the start of jury deliberations if it appears in this document.
Look for 'Jury excused to begin deliberations', 'Jury to commence deliberations', or
similar. Record the time exactly as written (e.g. 2:15 p.m.). Leave null if the
start of deliberations is not recorded in this document — it may appear at the end of
the previous day's minutes instead.

--- DELIBERATION END TIME (Delib_end_time) ---
The timestamp marking the end of jury deliberations. Look for the court resuming
session in connection with the verdict: 'Court in session' immediately before or after
'verdict reached', 'the jury has reached a verdict', 'jury present' for the verdict
reading, or similar. Use the earliest such timestamp if multiple qualify.
Record the time exactly as written.


{
  \"Final_trial_day\": numeric or null,
  \"Delib_start_time\": \"string or null\",
  \"Delib_end_time\": \"string or null\",
  \"notes\": \"string or null — anything unusual about this day's proceedings\"
}"


# ── MINUTE ENTRY — DELIBERATION DAYS ──────────────────────────────────────────
# Used for all minute files that are not Day 1 or the final day.
# These correspond to days where deliberations were ongoing but no verdict was reached.
# Each file may record:
#   - The end-of-day adjournment time (when the jury stopped deliberating)
#   - The start-of-day resumption time (when the jury resumed the next morning)
#   - A deliberation start time if deliberations first began on this day
# The R assembly step uses these times across all deliberation-day files to compute
# total deliberation time.

minute_deliberation_system_prompt <- "You are a legal data analyst extracting
structured information from mid-trial deliberation day minute entries in US civil
cases. These are chronological logs with timestamps. Return ONLY valid JSON with
no additional text. Do not include explanations, reasoning, markdown, or commentary.
Do not wrap the JSON in markdown code fences."

minute_deliberation_user_prompt <- "Extract the following fields from this deliberation
day minute entry and return them as a single JSON object with exactly these key names.

--- DELIBERATION START TIME (Delib_start_time) ---
The timestamp marking the first start of jury deliberations IF deliberations began for
the first time on this day. Look for 'Jury excused to begin deliberations',
'Jury to commence deliberations', or similar. Record the time exactly as written.
Leave null if deliberations had already been underway from a prior day.

--- END OF DAY ADJOURNMENT (Delib_adjourn_time) ---
The last timestamp before the court adjourned for the day while deliberations were
ongoing (i.e. the jury was sent home without reaching a verdict). Look for
'Court in recess', 'Jury excused until [date/time]', 'Court adjourned', or similar
at the end of the document. Record the time exactly as written.

--- NEXT DAY RESUMPTION (Delib_resume_time) ---
If this document also records the time deliberations resumed after a prior adjournment
(i.e. the jury returned and continued deliberating from a previous day), record that
timestamp. Look for 'Jury present', 'Court in session', 'Deliberations resume', or
similar at the start of deliberation activity. Leave null if deliberations first began
on this day rather than resuming.

{
  \"Delib_start_time\": \"string or null\",
  \"Delib_adjourn_time\": \"string or null\",
  \"Delib_resume_time\": \"string or null\",
  \"notes\": \"string or null — anything unusual about this day's deliberations\"
}"


minute_system_prompt        <- minute_deliberation_system_prompt
minute_user_prompt          <- minute_deliberation_user_prompt
```


## ── STEP 1: GOOGLE DOCUMENT AI FOR VERDICT HANDWRITING ──────────────────────
#
# Sends each verdict PDF to Google's Form Parser.
# Returns a dataframe of field name / value / confidence per document.
# We use this specifically to extract handwritten dollar amounts accurately.

```{r google_dai_verdicts}

# Get a Google OAuth2 token from the service account key file
get_google_token <- function(key_path) {
  gargle::credentials_service_account(
    path   = key_path,
    scopes = "https://www.googleapis.com/auth/cloud-platform"
  )
}

# Call Google Document AI Form Parser on one PDF.
# Returns a flat tibble of all detected form fields with confidence scores.
get_dai_form_fields <- function(filepath, token) {

  pdf_b64 <- encode_pdf(filepath)

  endpoint <- sprintf(
    "https://%s-documentai.googleapis.com/v1/projects/%s/locations/%s/processors/%s:process",
    google_location, google_project_id, google_location, google_processor_id
  )

  body <- list(
    rawDocument = list(
      content  = pdf_b64,
      mimeType = "application/pdf"
    )
  )

  response <- POST(
    url     = endpoint,
    add_headers(Authorization = paste("Bearer", token$credentials$access_token)),
    content_type_json(),
    body   = toJSON(body, auto_unbox = TRUE),
    encode = "raw"
  )

  if (http_error(response)) {
    stop(paste0("Google DAI error [", status_code(response), "]: ",
                content(response, as = "text", encoding = "UTF-8")))
  }

  parsed    <- content(response, as = "parsed", type = "application/json")
  full_text <- parsed$document$text %||% ""

  # Extract text from a textAnchor using character start/end positions
  extract_text <- function(anchor) {
    segs <- anchor$textSegments
    if (is.null(segs) || length(segs) == 0) return(NA_character_)
    start <- as.integer(segs[[1]]$startIndex %||% 0) + 1L
    end   <- as.integer(segs[[1]]$endIndex   %||% 0)
    substr(full_text, start, end) %>% str_trim()
  }

  pages <- parsed$document$pages %||% list()
  map_dfr(pages, function(page) {
    fields <- page$formFields %||% list()
    if (length(fields) == 0) return(tibble())
    map_dfr(fields, function(field) {
      tibble(
        field_name       = extract_text(field$fieldName$textAnchor),
        field_value      = extract_text(field$fieldValue$textAnchor),
        name_confidence  = field$fieldName$confidence  %||% NA_real_,
        value_confidence = field$fieldValue$confidence %||% NA_real_
      )
    })
  })
}

safe_dai <- purrr::safely(get_dai_form_fields, otherwise = NULL)

# Run Google DAI on verdict PDFs
verdict_files <- doc_inventory %>% filter(doc_type == "verdict")
cat(sprintf("Running Google Document AI on %d verdict PDFs...\n", nrow(verdict_files)))

# Fetch token once and reuse
google_token <- get_google_token(google_key_path)

dai_raw <- verdict_files %>%
  mutate(
    dai_fields = map(filepath, function(fp) {
      cat(sprintf("  DAI processing: %s\n", basename(fp)))
      flush.console()
      ans <- safe_dai(fp, google_token)
      if (!is.null(ans$error)) {
        message("  DAI ERROR on ", basename(fp), ": ", conditionMessage(ans$error))
        return(NULL)
      }
      ans$result
    }),
    dai_error = map_chr(filepath, function(fp) {
      ans <- safe_dai(fp, google_token)
      if (!is.null(ans$error)) conditionMessage(ans$error) else NA_character_
    })
  )

# Extract and clean damages fields from the DAI output.
# Filters for field names that suggest dollar amounts, parses values to numeric,
# and flags any value where DAI reported low confidence.
parse_damages_from_dai <- function(fields_df) {
  if (is.null(fields_df) || nrow(fields_df) == 0) return(tibble())
  fields_df %>%
    filter(str_detect(
      tolower(field_name),
      "damage|loss|award|economic|noneconomic|punitive|amount"
    )) %>%
    mutate(
      amount_numeric  = suppressWarnings(
        as.numeric(str_replace_all(field_value, "[$,\\s]", ""))
      ),
      flag_for_review = value_confidence < confidence_threshold
    )
}

dai_damages <- dai_raw %>%
  mutate(damages_fields = map(dai_fields, parse_damages_from_dai)) %>%
  select(case_id, filepath, damages_fields, dai_error) %>%
  unnest(damages_fields)

cat(sprintf("\nGoogle DAI extracted %d damages field entries from %d verdict forms\n",
            nrow(dai_damages), nrow(verdict_files)))
cat(sprintf("Fields flagged for manual review (confidence < %.0f%%): %d\n",
            confidence_threshold * 100,
            sum(dai_damages$flag_for_review, na.rm = TRUE)))
```


## ── STEP 2: CLAUDE API FUNCTION ─────────────────────────────────────────────

```{r claude_function}
# dai_fields_df: for verdict documents, pass the DAI fields tibble for this file
# so the OCR reference block is appended to the user prompt.
# For judgement and minute documents pass NULL (default).
get_claude_response <- function(filepath, doc_type, dai_fields_df = NULL) {

  sys_prompt  <- switch(doc_type,
    verdict              = verdict_system_prompt,
    judgement             = judgement_system_prompt,
    minute_day1          = minute_day1_system_prompt,
    minute_final         = minute_final_system_prompt,
    minute_deliberation  = minute_deliberation_system_prompt
  )
  user_prompt <- switch(doc_type,
    verdict              = verdict_user_prompt,
    judgement             = judgement_user_prompt,
    minute_day1          = minute_day1_user_prompt,
    minute_final         = minute_final_user_prompt,
    minute_deliberation  = minute_deliberation_user_prompt
  )

  # For verdict documents, append the DAI OCR reference block to the user prompt
  if (doc_type == "verdict") {
    dai_block   <- format_dai_for_prompt(dai_fields_df)
    user_prompt <- paste0(user_prompt, "\n\n", dai_block)
  }

  pdf_b64 <- encode_pdf(filepath)

  body <- list(
    model       = "claude-sonnet-4-6",
    max_tokens  = 1500,    # increased to accommodate expanded verdict JSON output
    temperature = 0,       # deterministic — always pick the single most likely answer
    system      = sys_prompt,
    messages    = list(
      list(
        role    = "user",
        content = list(
          list(
            type   = "document",
            source = list(
              type       = "base64",
              media_type = "application/pdf",
              data       = pdf_b64
            )
          ),
          list(type = "text", text = user_prompt)
        )
      )
    )
  )

  request_start <- Sys.time()

  response <- POST(
    url     = "https://api.anthropic.com/v1/messages",
    add_headers(
      `x-api-key`         = anthropic_key,
      `anthropic-version` = "2023-06-01",
      `content-type`      = "application/json"
    ),
    body   = toJSON(body, auto_unbox = TRUE),
    encode = "raw"
  )

  elapsed         <- as.numeric(difftime(Sys.time(), request_start, units = "secs"))
  parsed_response <- content(response, as = "parsed", type = "application/json")

  if (http_error(response)) {
    stop(paste0("Claude API error [", status_code(response), "]: ",
                parsed_response$error$message %||% "Unknown error"))
  }

  raw_text     <- parsed_response$content[[1]]$text %||% NA_character_
  total_tokens <- (parsed_response$usage$input_tokens  %||% 0) +
                  (parsed_response$usage$output_tokens %||% 0)
  clean_text   <- str_replace_all(raw_text, "```json|```", "") %>% str_trim()

  list(
    raw_text     = raw_text,
    parsed_json  = tryCatch(fromJSON(clean_text, simplifyVector = FALSE),
                            error = function(e) NULL),
    total_tokens = total_tokens,
    elapsed_sec  = elapsed
  )
}

safe_claude <- purrr::safely(get_claude_response, otherwise = NULL)
```


## ── TOKEN PRE-CHECK (optional — run before main pipeline to estimate cost) ───

```{r token_precheck, eval=FALSE}
# Calls the free token-counting endpoint on one sample doc of each type.
# Does not run inference. Use this to verify cost before running the full pipeline.

count_tokens_claude <- function(filepath, doc_type) {
  sys_prompt  <- switch(doc_type,
    verdict  = verdict_system_prompt,
    judgement = judgement_system_prompt,
    minute   = minute_system_prompt)
  user_prompt <- switch(doc_type,
    verdict  = verdict_user_prompt,
    judgement = judgement_user_prompt,
    minute   = minute_user_prompt)
  pdf_b64 <- encode_pdf(filepath)
  body <- list(
    model    = "claude-sonnet-4-6",
    system   = sys_prompt,
    messages = list(list(
      role    = "user",
      content = list(
        list(type = "document",
             source = list(type = "base64", media_type = "application/pdf", data = pdf_b64)),
        list(type = "text", text = user_prompt)
      )
    ))
  )
  response <- POST(
    url     = "https://api.anthropic.com/v1/messages/count_tokens",
    add_headers(`x-api-key` = anthropic_key,
                `anthropic-version` = "2023-06-01",
                `content-type` = "application/json"),
    body   = toJSON(body, auto_unbox = TRUE),
    encode = "raw"
  )
  parsed <- content(response, as = "parsed", type = "application/json")
  parsed$input_tokens %||% NA_real_
}

sample_docs <- doc_inventory %>% group_by(doc_type) %>% slice(1) %>% ungroup()
token_ests  <- sample_docs %>%
  mutate(input_tokens = map2_dbl(filepath, doc_type, count_tokens_claude))

avg_input       <- mean(token_ests$input_tokens, na.rm = TRUE)
n_docs          <- nrow(doc_inventory)
n_verdict_pages <- nrow(doc_inventory %>% filter(doc_type == "verdict")) * 5
est_input_cost  <- (avg_input * n_docs / 1e6) * 3
est_output_cost <- (300 * n_docs / 1e6) * 15
est_dai_cost    <- (n_verdict_pages / 1000) * 1.50

cat(sprintf(
  "\n=== COST ESTIMATE ===
Claude -- %d documents:
  Avg input tokens/doc: %.0f
  Est. input cost:      $%.4f
  Est. output cost:     $%.4f
  Claude subtotal:      $%.4f

Google Document AI -- %d verdict pages:
  Est. DAI cost:        $%.4f

TOTAL ESTIMATE:         $%.4f\n",
  n_docs, avg_input,
  est_input_cost, est_output_cost, est_input_cost + est_output_cost,
  n_verdict_pages, est_dai_cost,
  est_input_cost + est_output_cost + est_dai_cost
))
```


## ── MAIN PIPELINE: CLAUDE ON ALL DOCUMENTS ───────────────────────────────────
#
# Processes one document at a time, saves a checkpoint after every document,
# and writes a CSV every batch_size rows. If the run is interrupted, simply
# re-run this chunk — already-processed rows are skipped automatically.

```{r main_pipeline}
checkpoint_file <- "court_pipeline_checkpoint.rds"
batch_size      <- 20   # save a CSV snapshot every this many documents

if (file.exists(checkpoint_file)) {
  results <- readRDS(checkpoint_file)
  message("Resumed from checkpoint: ", sum(results$processed), " docs already done")
} else {
  results <- doc_inventory %>%
    mutate(
      raw_reply    = NA_character_,
      total_tokens = NA_real_,
      elapsed_sec  = NA_real_,
      api_error    = NA_character_,
      processed    = FALSE
    )
}

n_total       <- nrow(results)
pb            <- txtProgressBar(min = 0, max = n_total, style = 3)
overall_start <- Sys.time()

for (j in seq_len(n_total)) {

  # Skip rows already completed (enables safe resumption after interruption)
  if (isTRUE(results$processed[j])) {
    setTxtProgressBar(pb, j)
    next
  }

  elapsed_mins <- as.numeric(difftime(Sys.time(), overall_start, units = "mins"))
  cat(sprintf("
[%d/%d] Case: %s | Type: %s | Elapsed: %.1f min
",
              j, n_total, results$case_id[j], results$doc_type[j], elapsed_mins))
  flush.console()

  # For verdict documents, look up this file's DAI fields and pass them in
  dai_fields_for_this_doc <- NULL
  if (results$doc_type[j] == "verdict") {
    matched <- dai_raw %>% filter(filepath == results$filepath[j])
    if (nrow(matched) > 0 && !is.null(matched$dai_fields[[1]])) {
      dai_fields_for_this_doc <- matched$dai_fields[[1]]
    }
  }

  ans <- safe_claude(results$filepath[j], results$doc_type[j], dai_fields_for_this_doc)
  Sys.sleep(25)

  if (is.null(ans$result)) {
    results$api_error[j] <- conditionMessage(ans$error) %||% "Unknown error"
  } else {
    results$raw_reply[j]    <- ans$result$raw_text
    results$total_tokens[j] <- ans$result$total_tokens
    results$elapsed_sec[j]  <- ans$result$elapsed_sec
  }

  results$processed[j] <- TRUE
  saveRDS(results, checkpoint_file)   # checkpoint after every document
  setTxtProgressBar(pb, j)

  if (j %% batch_size == 0 || j == n_total) {
    write_csv(results, sprintf("court_pipeline_batch_row%04d.csv", j))
    message(sprintf("
Batch checkpoint saved at row %d", j))
  }
}

close(pb)
message("All Claude calls complete.")
```


## ── PARSE AND MERGE OUTPUTS INTO CSVs ────────────────────────────────────────

```{r parse_outputs}

# ── VERDICT CSV — merge Claude findings + Google DAI damages ──────────────────
#
# Claude provides:     Yes/No liability findings, fault percentages, verdict date
# Google DAI provides: dollar amounts with per-field confidence scores
# Merge key:           case_id + filepath

verdict_claude <- results %>%
  filter(doc_type == "verdict", !is.na(raw_reply)) %>%
  mutate(parsed = map(raw_reply, ~{
    clean <- str_replace_all(.x, "```json|```", "") %>% str_trim()
    tryCatch(fromJSON(clean, simplifyVector = FALSE), error = function(e) NULL)
  })) %>%
  filter(!map_lgl(parsed, is.null)) %>%
  mutate(
    Pl_type                      = map_chr(parsed, ~safe_field(.x, "Pl_type")),
    Def_type                     = map_chr(parsed, ~safe_field(.x, "Def_type")),
    Pl_gender                    = map_chr(parsed, ~safe_field(.x, "Pl_gender")),
    Def_gender                   = map_chr(parsed, ~safe_field(.x, "Def_gender")),
    Number_pl                    = map_chr(parsed, ~safe_field(.x, "Number_pl")),
    Number_def                   = map_chr(parsed, ~safe_field(.x, "Number_def")),
    Outcome                      = map_chr(parsed, ~safe_field(.x, "Outcome")),
    Verdict_note                 = map_chr(parsed, ~safe_field(.x, "Verdict_note")),
    Non_economic_damages_requested = map_chr(parsed, ~safe_field(.x, "Non_economic_damages_requested")),
    Punitive_damages_requested   = map_chr(parsed, ~safe_field(.x, "Punitive_damages_requested")),
    Monetary_award               = map_chr(parsed, ~safe_field(.x, "Monetary_award")),
    Non_economic_damages_awarded = map_chr(parsed, ~safe_field(.x, "Non_economic_damages_awarded")),
    Punitive_damages_awarded     = map_chr(parsed, ~safe_field(.x, "Punitive_damages_awarded")),
    Percent_plaintiff_liable     = map_chr(parsed, ~safe_field(.x, "Percent_plaintiff_liable")),
    verdict_date                 = map_chr(parsed, ~safe_field(.x, "verdict_date")),
    claude_notes                 = map_chr(parsed, ~safe_field(.x, "notes"))
  ) %>%
  select(case_id, filepath,
         Pl_type, Def_type, Pl_gender, Def_gender, Number_pl, Number_def,
         Outcome, Verdict_note,
         Non_economic_damages_requested, Punitive_damages_requested,
         Monetary_award, Non_economic_damages_awarded, Punitive_damages_awarded,
         Percent_plaintiff_liable, verdict_date, claude_notes)

# Google DAI damages — one row per extracted field per verdict PDF
dai_damages_clean <- dai_damages %>%
  select(case_id, filepath,
         dai_field_name   = field_name,
         dai_field_value  = field_value,
         dai_amount       = amount_numeric,
         value_confidence,
         flag_for_review)

# Left join: every Claude verdict row gets matched DAI damages rows
output_verdicts <- verdict_claude %>%
  left_join(dai_damages_clean, by = c("case_id", "filepath"))

#write_csv(output_verdicts, "output_verdicts.csv")
#message("Saved output_verdicts.csv — ", nrow(output_verdicts), " rows")

# ── judgement CSV ──────────────────────────────────────────────────────────────
output_judgement <- results %>%
  filter(doc_type == "judgement", !is.na(raw_reply)) %>%
  mutate(parsed = map(raw_reply, ~{
    clean <- str_replace_all(.x, "```json|```", "") %>% str_trim()
    tryCatch(fromJSON(clean, simplifyVector = FALSE), error = function(e) NULL)
  })) %>%
  filter(!map_lgl(parsed, is.null)) %>%
  mutate(Number_jurors = map_chr(parsed, ~safe_field(.x, "Number_jurors"))) %>%
  select(case_id, filepath, Number_jurors)

#write_csv(output_judgement, "output_judgement.csv")
#message("Saved output_judgement.csv — ", nrow(output_judgement), " rows")

# ── MINUTE DAY 1 CSV ─────────────────────────────────────────────────────────
output_minutes_day1 <- results %>%
  filter(doc_type == "minute_day1", !is.na(raw_reply)) %>%
  mutate(parsed = map(raw_reply, ~{
    clean <- str_replace_all(.x, "```json|```", "") %>% str_trim()
    tryCatch(fromJSON(clean, simplifyVector = FALSE), error = function(e) NULL)
  })) %>%
  filter(!map_lgl(parsed, is.null)) %>%
  mutate(
    Trial_date        = map_chr(parsed, ~safe_field(.x, "Trial_date")),
    Judge             = map_chr(parsed, ~safe_field(.x, "Judge")),
    Jury_size         = map_chr(parsed, ~safe_field(.x, "Jury_size")),
    Jurors_brought    = map_chr(parsed, ~safe_field(.x, "Jurors_brought")),
    Excused_for_cause = map_chr(parsed, ~safe_field(.x, "Excused_for_cause")),
    Pl_peremptory     = map_chr(parsed, ~safe_field(.x, "Pl_peremptory")),
    Def_peremptory    = map_chr(parsed, ~safe_field(.x, "Def_peremptory")),
    Voir_dire_minutes = map_chr(parsed, ~safe_field(.x, "Voir_dire_minutes")),
    Voir_Dire_Extras  = map_chr(parsed, ~safe_field(.x, "Voir_Dire_Extras"))
  ) %>%
  select(case_id, filepath, Trial_date, Judge, Jury_size, Jurors_brought,
         Excused_for_cause, Pl_peremptory, Def_peremptory,
         Voir_dire_minutes, Voir_Dire_Extras)

#write_csv(output_minutes_day1, "output_minutes_day1.csv")
#message("Saved output_minutes_day1.csv — ", nrow(output_minutes_day1), " rows")

# ── MINUTE FINAL CSV ─────────────────────────────────────────────────────────
output_minutes_final <- results %>%
  filter(doc_type == "minute_final", !is.na(raw_reply)) %>%
  mutate(parsed = map(raw_reply, ~{
    clean <- str_replace_all(.x, "```json|```", "") %>% str_trim()
    tryCatch(fromJSON(clean, simplifyVector = FALSE), error = function(e) NULL)
  })) %>%
  filter(!map_lgl(parsed, is.null)) %>%
  mutate(
    #Verdict_date         = map_chr(parsed, ~safe_field(.x, "Verdict_date")),
    Final_trial_day      = map_chr(parsed, ~safe_field(.x, "Final_trial_day")),
    Delib_start_time     = map_chr(parsed, ~safe_field(.x, "Delib_start_time")),
    Delib_end_time       = map_chr(parsed, ~safe_field(.x, "Delib_end_time")),
    notes                = map_chr(parsed, ~safe_field(.x, "notes"))
  ) %>%
  select(case_id, filepath, Final_trial_day,
         Delib_start_time, Delib_end_time, notes)

#write_csv(output_minutes_final, "output_minutes_final.csv")
#message("Saved output_minutes_final.csv — ", nrow(output_minutes_final), " rows")


# ── MINUTE DELIBERATION DAYS CSV ──────────────────────────────────────────────
output_minutes_delib <- results %>%
  filter(doc_type == "minute_deliberation", !is.na(raw_reply)) %>%
  mutate(parsed = map(raw_reply, ~{
    clean <- str_replace_all(.x, "```json|```", "") %>% str_trim()
    tryCatch(fromJSON(clean, simplifyVector = FALSE), error = function(e) NULL)
  })) %>%
  filter(!map_lgl(parsed, is.null)) %>%
  mutate(
    Delib_start_time     = map_chr(parsed, ~safe_field(.x, "Delib_start_time")),
    Delib_adjourn_time   = map_chr(parsed, ~safe_field(.x, "Delib_adjourn_time")),
    Delib_resume_time    = map_chr(parsed, ~safe_field(.x, "Delib_resume_time")),
    notes                = map_chr(parsed, ~safe_field(.x, "notes"))
  ) %>%
  select(case_id, filepath, Delib_start_time, Delib_adjourn_time,
         Delib_resume_time, notes)

#write_csv(output_minutes_delib, "output_minutes_delib.csv")
#message("Saved output_minutes_delib.csv — ", nrow(output_minutes_delib), " rows")


# ── DELIBERATION LENGTH ASSEMBLY ──────────────────────────────────────────────
# Assembles total deliberation time per case from the final and deliberation-day
# minute files. The key insight is that deliberation start time may appear either
# in a deliberation-day file OR in the final-day file, and adjournment/resumption
# times are needed to calculate time on each day when deliberations span multiple
# days. All time arithmetic is done here in R.
#
# Per-day logic:
#   Deliberation-day files (not the final day):
#     Active delib time = adjourn_time - resume_or_start_time
#     If resume_time is present, use that as the start of that day's session.
#     If only start_time is present, deliberations first began that day.
#     If neither is present, that day's contribution cannot be calculated.
#
#   Final-day file:
#     Active delib time = end_time - resume_or_start_time
#     Use Delib_start_time if present (single-day deliberations or started here),
#     otherwise use no start anchor — will be NA and flagged for manual review.
#
# Total = sum of per-day contributions. NA if any day is unresolvable.

parse_time <- function(t) {
  if (is.na(t) || !nzchar(t)) return(NA_real_)
  t_clean <- str_replace_all(t, "\\.", "") %>%
             str_replace_all("(?i)\\bam\\b", "AM") %>%
             str_replace_all("(?i)\\bpm\\b", "PM") %>%
             str_trim()
  parsed <- suppressWarnings(
    as.POSIXct(paste("2000-01-01", t_clean), format = "%Y-%m-%d %I:%M %p")
  )
  if (is.na(parsed)) return(NA_real_)
  as.numeric(parsed) / 60   # minutes since epoch; differences give duration in minutes
}

time_diff_mins <- function(start_str, end_str) {
  s <- parse_time(start_str)
  e <- parse_time(end_str)
  if (is.na(s) || is.na(e)) return(NA_real_)
  e - s
}

# Per-day contribution from deliberation-day files
delib_day_contributions <- output_minutes_delib %>%
  mutate(
    # Use resume time if present (continuing from prior day), else start time (began this day)
    day_start  = ifelse(!is.na(Delib_resume_time) & nzchar(Delib_resume_time),
                        Delib_resume_time, Delib_start_time),
    day_mins   = map2_dbl(day_start, Delib_adjourn_time, time_diff_mins)
  ) %>%
  select(case_id, filepath, day_mins)

# Per-case contribution from final-day file
final_day_contributions <- output_minutes_final %>%
  mutate(
    day_mins   = map2_dbl(Delib_start_time, Delib_end_time, time_diff_mins)
  ) %>%
  select(case_id, filepath, day_mins)

# Combine and sum per case
all_delib_days <- bind_rows(
  delib_day_contributions %>% select(case_id, day_mins),
  final_day_contributions  %>% select(case_id, day_mins)
)

deliberation_totals <- all_delib_days %>%
  group_by(case_id) %>%
  summarise(
    Deliberation_minutes = if (any(is.na(day_mins))) NA_real_ else sum(day_mins),
    any_na = any(is.na(day_mins)),
    .groups = "drop"
  ) %>%
  left_join(
    final_day_contributions %>% select(case_id),
    by = "case_id"
  ) %>%
  mutate(
    Deliberation_minutes_flag = if_else(
      any_na,
      "one or more days had unresolvable times — verify manually",
      NA_character_
    )
  ) %>%
  select(case_id,
         Deliberation_minutes, Deliberation_minutes_flag)

#write_csv(deliberation_totals, "output_deliberation_totals.csv")
#message("Saved output_deliberation_totals.csv — ", nrow(deliberation_totals), " cases")

# Merge all into one CSV
dfs <- list(
  output_verdicts,
  output_judgement,
  output_minutes_day1,
  output_minutes_final,
  deliberation_totals
) %>%
  map(~ select(.x, -any_of("filepath")))

final_df <- reduce(dfs, full_join, by = "case_id")
readr::write_excel_csv(final_df, "merged_output.csv")

# ── MANUAL REVIEW LIST ────────────────────────────────────────────────────────
# A focused list of only the damages fields where Google DAI was uncertain.
# Open output_manual_review.csv, check each value against the original PDF,
# and correct any errors before using the data in your analysis.

review_list <- output_verdicts %>%
  filter(isTRUE(flag_for_review)) %>%
  select(case_id, filepath, dai_field_name, dai_field_value,
         dai_amount, value_confidence) %>%
  arrange(value_confidence)  # lowest confidence first

message("  Fields flagged for manual review: ",
        sum(output_verdicts$flag_for_review, na.rm = TRUE))

message("  Cases needing manual review for deliberation: ",
        sum(!is.na(deliberation_totals$Deliberation_minutes_flag)))

if (nrow(review_list) > 0) {
  write_csv(review_list, "output_manual_review.csv")
  message("Saved output_manual_review.csv — ",
          nrow(review_list), " fields need manual verification")
} else {
  message("No fields flagged — all DAI confidence scores above threshold")
}


# ── ERROR LOG ─────────────────────────────────────────────────────────────────
errors <- bind_rows(
  results %>%
    filter(!is.na(api_error)) %>%
    mutate(source = "Claude") %>%
    select(case_id, doc_type, filepath, source, error = api_error),
  dai_raw %>%
    filter(!is.na(dai_error)) %>%
    mutate(source = "Google DAI", doc_type = "verdict") %>%
    select(case_id, doc_type, filepath, source, error = dai_error)
)

if (nrow(errors) > 0) {
  write_csv(errors, "output_errors.csv")
  message("Saved output_errors.csv — ", nrow(errors), " failed calls to investigate")
} else {
  message("No errors — all API calls succeeded")
}
```
