# Court Document Analysis Pipeline (Two-Step Hybrid)
#
# VERDICT forms (handwritten):
#   Step 1 — Google Document AI Form Parser extracts handwritten field values
#             with per-field confidence scores
#   Step 2 — Claude reads the same PDF for Yes/No findings and overall context
#             The two outputs are merged: Google DAI numbers + Claude decisions
#
# JUDGMENT and MINUTE documents (typed PDFs):
#   Claude only — no OCR step needed
#
# Output: three CSVs, one per document type


## ── SETUP ────────────────────────────────────────────────────────────────────
# Before running:
#   1. Install packages if needed:
#        install.packages(c("tidyverse","httr","jsonlite","purrr","base64enc","gargle"))
#   2. Create a config.R file in the same directory as this script (see template below)
#   3. Add config.R to your .gitignore — NEVER commit it to version control
#
# config.R should define these variables:
#   anthropic_key        <- "sk-ant-..."
#   google_key_path      <- "~/path/to/google-service-account-key.json"
#   google_project_id    <- "your-gcp-project-id"
#   google_location      <- "us"   # "us" or "eu"
#   google_processor_id  <- "your-processor-id"
#   cases_root           <- "~/path/to/your/cases"
#   confidence_threshold <- 0.90
#
# Google Document AI one-time setup:
#   a. Create a Google Cloud project at console.cloud.google.com
#   b. Enable the Document AI API
#   c. Create a Form Parser processor:
#        Document AI > Overview > Explore Processors > Form Parser > Create
#   d. Note your Project ID, Processor ID (hex string), and Location ("us" or "eu")
#   e. Create a Service Account with the "Document AI API User" role
#   f. Download the JSON key file and set its path in config.R

```{r setup}
library(tidyverse)
library(httr)
library(jsonlite)
library(purrr)
library(base64enc)
library(gargle)        # handles Google OAuth — install.packages("gargle")

# Load Google Cloud credentials and API key (DO NOT SHARE THIS FILE)
source("config.R")
```


## ── HELPERS ──────────────────────────────────────────────────────────────────

```{r helpers}
`%||%` <- function(x, y) {
  if (is.null(x) || length(x) == 0) y else x
}

# Encode a local PDF to base64 string
encode_pdf <- function(filepath) {
  base64encode(readBin(filepath, "raw", file.info(filepath)$size))
}

# Detect document type from filename
detect_doc_type <- function(filename) {
  fname <- tolower(basename(filename))
  if (str_detect(fname, "verdict"))  return("verdict")
  if (str_detect(fname, "judgement")) return("judgement")
  if (str_detect(fname, "minute"))   return("minute")
  return("unknown")
}

# Safely extract a named field from a parsed JSON list
safe_field <- function(json_list, field, default = NA_character_) {
  val <- json_list[[field]]
  if (is.null(val) || length(val) == 0) default else as.character(val)
}

# Serialize Google DAI form fields into a compact text block for Claude.
# This is appended to the verdict user prompt so Claude can cross-reference
# the OCR readings rather than reading handwritten dollar amounts cold.
# Only fields with a non-empty value are included to keep the block concise.
format_dai_for_prompt <- function(fields_df) {
  if (is.null(fields_df) || nrow(fields_df) == 0) {
    return("(No OCR reference data available for this document.)")
  }
  rows <- fields_df %>%
    filter(!is.na(field_value), nzchar(field_value)) %>%
    mutate(line = sprintf("  %s: %s (confidence: %.0f%%)",
                          field_name, field_value,
                          value_confidence * 100))
  if (nrow(rows) == 0) return("(No OCR reference data available for this document.)")
  paste0(
    "--- OCR REFERENCE BLOCK (Google Document AI pre-extraction) ---\n",
    paste(rows$line, collapse = "\n"),
    "\n--- END OF OCR REFERENCE BLOCK ---"
  )
}
```


## ── BUILD CASE INVENTORY ─────────────────────────────────────────────────────

```{r inventory}
case_folders <- list.dirs(cases_root, recursive = FALSE)

doc_inventory <- map_dfr(case_folders, function(folder) {
  case_id <- basename(folder)
  pdfs    <- list.files(folder, pattern = "\\.pdf$", full.names = TRUE, ignore.case = TRUE)
  tibble(
    case_id  = case_id,
    filepath = pdfs,
    doc_type = map_chr(pdfs, detect_doc_type)
  )
}) %>%
  filter(doc_type != "unknown") %>%
  arrange(case_id, doc_type)

doc_inventory <- doc_inventory %>% filter(case_id == "1000309")

cat(sprintf("Found %d documents across %d cases:\n",
            nrow(doc_inventory), n_distinct(doc_inventory$case_id)))
print(count(doc_inventory, doc_type))
```


## ── PROMPTS (Claude) ─────────────────────────────────────────────────────────
# Verdict prompts ask only for Yes/No findings and fault percentages.
# Dollar amounts come from Google Document AI — Claude is not asked for them.

```{r prompts}

# ── VERDICT ───────────────────────────────────────────────────────────────────
# All verdict fields are extracted in a single API call.
# Handwritten dollar amounts are read by Google Document AI and passed in as an
# OCR reference block appended to the user prompt at runtime — see
# format_dai_for_prompt() and get_claude_response() below.

verdict_system_prompt <- "You are a legal data analyst extracting structured information
from jury verdict forms in US civil cases. The form may be handwritten. You will be
provided with a reference block of field values pre-extracted by an OCR tool — use
these as your primary source for dollar amounts and percentages, but use the document
itself as the authoritative source for all other fields. Return ONLY valid JSON with
no additional text.  Keep unsure responses as blanks."

verdict_user_prompt <- "Extract the following fields from this jury verdict form and
return them as a single JSON object with exactly these key names.

--- PARTY TYPE (Pl_type, Def_type) ---
Record the type of each plaintiff and defendant. Use: individual, corporation, or the
specific government entity type such as city, county, or school. If all parties on one
side are the same type do not repeat — list each distinct type once. If an individual
is represented by their estate, record as individual. If multiple types exist, separate
with a comma.

--- GENDER (Pl_gender, Def_gender) ---
For individual plaintiffs/defendants only, infer gender from the name (Male / Female /
Unknown). If there are both male and female parties on one side, write mixed. Leave
null if all parties on that side are not individuals.

--- COUNTS (Number_pl, Number_def) ---
Count the total number of plaintiffs and defendants. If an individual is represented
by their estate, count as one. Include consolidated parties in the total. Exclude
counter-plaintiffs, counter-defendants, and third parties. Exclude terminated parties.
Do not count separately an individual who appears only as a guardian/representative
for a minor unless they also appear individually.

--- OUTCOME (Outcome, Verdict_note) ---
Determine whether the verdict favors the plaintiff or defendant. Use the verdict
document as the primary source; if outcome cannot be determined from the verdict alone,
note that the judgment document should be consulted. If the jury is deciding only
liability (damages already determined), record Verdict_note as liability only. If only
deciding damages (liability already determined), record as damages only. If a
successful counterclaim means the defense wins more money than the plaintiff, record
Outcome as defendant. If the plaintiff is found 50% or more liable, record Outcome as
defendant. Otherwise record as plaintiff.

--- NON-ECONOMIC DAMAGES REQUESTED (Non_economic_damages_requested) ---
If the verdict form contains a line or space for a dollar value for non-economic
damages — including pain and suffering, loss of consortium, emotional distress,
physical impairment or disfigurement, mental anguish, impairment of quality of life,
loss of enjoyment of life, deprivation of civil rights, or similar — record YES.
Otherwise record NO.

--- PUNITIVE DAMAGES REQUESTED (Punitive_damages_requested) ---
If the verdict form contains a line or space for punitive or exemplary damages,
record YES. Otherwise record NO.

--- MONETARY AWARD (Monetary_award) ---
Total monetary value awarded to the plaintiff including economic, non-economic, and
punitive damages combined. Record 0 if the defendant won. If the defendant is less
than 100% liable, scale the total damages by the defendant liability percentage. If
the verdict indicates the plaintiff award will be reduced by a specific amount (due to
a counterclaim or failure to mitigate), subtract that amount. Use the OCR reference
block below as the primary source for dollar amounts.

--- NON-ECONOMIC DAMAGES AWARDED (Non_economic_damages_awarded) ---
Total non-economic damages awarded. Record 0 if the defendant won. Keywords include:
pain and suffering, loss of consortium, emotional distress, physical impairment,
mental anguish, impairment of quality of life, loss of enjoyment of life, deprivation
of civil rights, and similar. Leave null if the verdict does not specify the nature or
division of damages.

--- PUNITIVE DAMAGES AWARDED (Punitive_damages_awarded) ---
Total punitive or exemplary damages awarded. Record 0 if the defendant won.

--- PLAINTIFF LIABILITY (Percent_plaintiff_liable) ---
If the verdict finds the plaintiff partially liable, record the percentage. Otherwise null.

--- FORMAT RULES ---
Record all dollar amounts as plain numbers with no commas or dollar signs.
Use null for any field that is not present, not applicable, or cannot be determined.
Return ONLY the JSON object below with no additional text.

{
  \"Pl_type\": \"string — comma-separated distinct plaintiff types\",
  \"Def_type\": \"string — comma-separated distinct defendant types\",
  \"Pl_gender\": \"Male / Female / Mixed / null\",
  \"Def_gender\": \"Male / Female / Mixed / null\",
  \"Number_pl\": numeric,
  \"Number_def\": numeric,
  \"Outcome\": \"plaintiff or defendant\",
  \"Verdict_note\": \"string or null — liability only / damages only / or other notable context\",
  \"Non_economic_damages_requested\": \"YES or NO\",
  \"Punitive_damages_requested\": \"YES or NO\",
  \"Monetary_award\": numeric,
  \"Non_economic_damages_awarded\": numeric or null,
  \"Punitive_damages_awarded\": numeric,
  \"Percent_plaintiff_liable\": numeric or null,
  \"verdict_date\": \"YYYY-MM-DD or null\",
  \"notes\": \"string or null — anything unusual about the form or findings\"
}"


# ── JUDGMENT ──────────────────────────────────────────────────────────────────
judgment_system_prompt <- "You are a legal data analyst extracting structured information
from court judgment documents in US civil cases. These are typed official documents.
Extract exact dollar amounts as plain numbers with no commas or dollar signs.
Return ONLY valid JSON with no additional text."

judgment_user_prompt <- "Extract the following fields from this judgment document and
return them as a JSON object:

{
  \"case_number\": \"string\",
  \"judge_name\": \"string\",
  \"judgment_date\": \"YYYY-MM-DD\",
  \"court\": \"string\",
  \"judgment_awards\": [
    {
      \"plaintiff_name\": \"string\",
      \"amount_awarded\": numeric
    }
  ],
  \"post_judgment_interest_rate\": \"string or null — e.g. 0.49%\",
  \"costs_awarded\": \"Yes or No\",
  \"notes\": \"string or null\"
}"


# ── MINUTE ENTRY ──────────────────────────────────────────────────────────────
minute_system_prompt <- "You are a legal data analyst extracting structured information
from court minute entries in US civil cases. These are chronological logs of proceedings.
Return ONLY valid JSON with no additional text."

minute_user_prompt <- "Extract the following fields from this minute entry and return
them as a JSON object:

{
  \"case_number\": \"string\",
  \"hearing_date\": \"YYYY-MM-DD\",
  \"judge_name\": \"string\",
  \"proceeding_type\": \"string — e.g. Trial Day 1, Motions Hearing\",
  \"plaintiffs_present\": \"string — comma separated\",
  \"plaintiff_attorneys\": \"string — comma separated\",
  \"defense_attorneys\": \"string — comma separated\",
  \"key_events\": \"string — brief summary of main events\",
  \"exhibits_admitted\": \"string or null\",
  \"total_time\": \"string or null — e.g. 6 hrs 33 min\",
  \"notes\": \"string or null\"
}"
```


## ── STEP 1: GOOGLE DOCUMENT AI FOR VERDICT HANDWRITING ──────────────────────
#
# Sends each verdict PDF to Google's Form Parser.
# Returns a dataframe of field name / value / confidence per document.
# We use this specifically to extract handwritten dollar amounts accurately.

```{r google_dai_verdicts}

# Get a Google OAuth2 token from the service account key file
get_google_token <- function(key_path) {
  gargle::credentials_service_account(
    path   = key_path,
    scopes = "https://www.googleapis.com/auth/cloud-platform"
  )
}

# Call Google Document AI Form Parser on one PDF.
# Returns a flat tibble of all detected form fields with confidence scores.
get_dai_form_fields <- function(filepath, token) {

  pdf_b64 <- encode_pdf(filepath)

  endpoint <- sprintf(
    "https://%s-documentai.googleapis.com/v1/projects/%s/locations/%s/processors/%s:process",
    google_location, google_project_id, google_location, google_processor_id
  )

  body <- list(
    rawDocument = list(
      content  = pdf_b64,
      mimeType = "application/pdf"
    )
  )

  response <- POST(
    url     = endpoint,
    add_headers(Authorization = paste("Bearer", token$credentials$access_token)),
    content_type_json(),
    body   = toJSON(body, auto_unbox = TRUE),
    encode = "raw"
  )

  if (http_error(response)) {
    stop(paste0("Google DAI error [", status_code(response), "]: ",
                content(response, as = "text", encoding = "UTF-8")))
  }

  parsed    <- content(response, as = "parsed", type = "application/json")
  full_text <- parsed$document$text %||% ""

  # Extract text from a textAnchor using character start/end positions
  extract_text <- function(anchor) {
    segs <- anchor$textSegments
    if (is.null(segs) || length(segs) == 0) return(NA_character_)
    start <- as.integer(segs[[1]]$startIndex %||% 0) + 1L
    end   <- as.integer(segs[[1]]$endIndex   %||% 0)
    substr(full_text, start, end) %>% str_trim()
  }

  pages <- parsed$document$pages %||% list()
  map_dfr(pages, function(page) {
    fields <- page$formFields %||% list()
    if (length(fields) == 0) return(tibble())
    map_dfr(fields, function(field) {
      tibble(
        field_name       = extract_text(field$fieldName$textAnchor),
        field_value      = extract_text(field$fieldValue$textAnchor),
        name_confidence  = field$fieldName$confidence  %||% NA_real_,
        value_confidence = field$fieldValue$confidence %||% NA_real_
      )
    })
  })
}

safe_dai <- purrr::safely(get_dai_form_fields, otherwise = NULL)

# Run Google DAI on verdict PDFs
verdict_files <- doc_inventory %>% filter(doc_type == "verdict")
cat(sprintf("Running Google Document AI on %d verdict PDFs...\n", nrow(verdict_files)))

# Fetch token once and reuse
google_token <- get_google_token(google_key_path)

dai_raw <- verdict_files %>%
  mutate(
    dai_fields = map(filepath, function(fp) {
      cat(sprintf("  DAI processing: %s\n", basename(fp)))
      flush.console()
      ans <- safe_dai(fp, google_token)
      if (!is.null(ans$error)) {
        message("  DAI ERROR on ", basename(fp), ": ", conditionMessage(ans$error))
        return(NULL)
      }
      ans$result
    }),
    dai_error = map_chr(filepath, function(fp) {
      ans <- safe_dai(fp, google_token)
      if (!is.null(ans$error)) conditionMessage(ans$error) else NA_character_
    })
  )

# Extract and clean damages fields from the DAI output.
# Filters for field names that suggest dollar amounts, parses values to numeric,
# and flags any value where DAI reported low confidence.
parse_damages_from_dai <- function(fields_df) {
  if (is.null(fields_df) || nrow(fields_df) == 0) return(tibble())
  fields_df %>%
    filter(str_detect(
      tolower(field_name),
      "damage|loss|award|economic|noneconomic|punitive|amount"
    )) %>%
    mutate(
      amount_numeric  = suppressWarnings(
        as.numeric(str_replace_all(field_value, "[$,\\s]", ""))
      ),
      flag_for_review = value_confidence < confidence_threshold
    )
}

dai_damages <- dai_raw %>%
  mutate(damages_fields = map(dai_fields, parse_damages_from_dai)) %>%
  select(case_id, filepath, damages_fields, dai_error) %>%
  unnest(damages_fields)

cat(sprintf("\nGoogle DAI extracted %d damages field entries from %d verdict forms\n",
            nrow(dai_damages), nrow(verdict_files)))
cat(sprintf("Fields flagged for manual review (confidence < %.0f%%): %d\n",
            confidence_threshold * 100,
            sum(dai_damages$flag_for_review, na.rm = TRUE)))
```


## ── STEP 2: CLAUDE API FUNCTION ─────────────────────────────────────────────

```{r claude_function}
# dai_fields_df: for verdict documents, pass the DAI fields tibble for this file
# so the OCR reference block is appended to the user prompt.
# For judgment and minute documents pass NULL (default).
get_claude_response <- function(filepath, doc_type, dai_fields_df = NULL) {

  sys_prompt  <- switch(doc_type,
    verdict  = verdict_system_prompt,
    judgment = judgment_system_prompt,
    minute   = minute_system_prompt
  )
  user_prompt <- switch(doc_type,
    verdict  = verdict_user_prompt,
    judgment = judgment_user_prompt,
    minute   = minute_user_prompt
  )

  # For verdict documents, append the DAI OCR reference block to the user prompt
  if (doc_type == "verdict") {
    dai_block   <- format_dai_for_prompt(dai_fields_df)
    user_prompt <- paste0(user_prompt, "\n\n", dai_block)
  }

  pdf_b64 <- encode_pdf(filepath)

  body <- list(
    model       = "claude-sonnet-4-6",
    max_tokens  = 1500,    # increased to accommodate expanded verdict JSON output
    temperature = 0,       # deterministic — always pick the single most likely answer
    system      = sys_prompt,
    messages    = list(
      list(
        role    = "user",
        content = list(
          list(
            type   = "document",
            source = list(
              type       = "base64",
              media_type = "application/pdf",
              data       = pdf_b64
            )
          ),
          list(type = "text", text = user_prompt)
        )
      )
    )
  )

  request_start <- Sys.time()

  response <- POST(
    url     = "https://api.anthropic.com/v1/messages",
    add_headers(
      `x-api-key`         = anthropic_key,
      `anthropic-version` = "2023-06-01",
      `content-type`      = "application/json"
    ),
    body   = toJSON(body, auto_unbox = TRUE),
    encode = "raw"
  )

  elapsed         <- as.numeric(difftime(Sys.time(), request_start, units = "secs"))
  parsed_response <- content(response, as = "parsed", type = "application/json")

  if (http_error(response)) {
    stop(paste0("Claude API error [", status_code(response), "]: ",
                parsed_response$error$message %||% "Unknown error"))
  }

  raw_text     <- parsed_response$content[[1]]$text %||% NA_character_
  total_tokens <- (parsed_response$usage$input_tokens  %||% 0) +
                  (parsed_response$usage$output_tokens %||% 0)
  clean_text   <- str_replace_all(raw_text, "```json|```", "") %>% str_trim()

  list(
    raw_text     = raw_text,
    parsed_json  = tryCatch(fromJSON(clean_text, simplifyVector = FALSE),
                            error = function(e) NULL),
    total_tokens = total_tokens,
    elapsed_sec  = elapsed
  )
}

safe_claude <- purrr::safely(get_claude_response, otherwise = NULL)
```


## ── TOKEN PRE-CHECK (optional — run before main pipeline to estimate cost) ───

```{r token_precheck, eval=FALSE}
# Calls the free token-counting endpoint on one sample doc of each type.
# Does not run inference. Use this to verify cost before running the full pipeline.

count_tokens_claude <- function(filepath, doc_type) {
  sys_prompt  <- switch(doc_type,
    verdict  = verdict_system_prompt,
    judgment = judgment_system_prompt,
    minute   = minute_system_prompt)
  user_prompt <- switch(doc_type,
    verdict  = verdict_user_prompt,
    judgment = judgment_user_prompt,
    minute   = minute_user_prompt)
  pdf_b64 <- encode_pdf(filepath)
  body <- list(
    model    = "claude-sonnet-4-6",
    system   = sys_prompt,
    messages = list(list(
      role    = "user",
      content = list(
        list(type = "document",
             source = list(type = "base64", media_type = "application/pdf", data = pdf_b64)),
        list(type = "text", text = user_prompt)
      )
    ))
  )
  response <- POST(
    url     = "https://api.anthropic.com/v1/messages/count_tokens",
    add_headers(`x-api-key` = anthropic_key,
                `anthropic-version` = "2023-06-01",
                `content-type` = "application/json"),
    body   = toJSON(body, auto_unbox = TRUE),
    encode = "raw"
  )
  parsed <- content(response, as = "parsed", type = "application/json")
  parsed$input_tokens %||% NA_real_
}

sample_docs <- doc_inventory %>% group_by(doc_type) %>% slice(1) %>% ungroup()
token_ests  <- sample_docs %>%
  mutate(input_tokens = map2_dbl(filepath, doc_type, count_tokens_claude))

avg_input       <- mean(token_ests$input_tokens, na.rm = TRUE)
n_docs          <- nrow(doc_inventory)
n_verdict_pages <- nrow(doc_inventory %>% filter(doc_type == "verdict")) * 5
est_input_cost  <- (avg_input * n_docs / 1e6) * 3
est_output_cost <- (300 * n_docs / 1e6) * 15
est_dai_cost    <- (n_verdict_pages / 1000) * 1.50

cat(sprintf(
  "\n=== COST ESTIMATE ===
Claude -- %d documents:
  Avg input tokens/doc: %.0f
  Est. input cost:      $%.4f
  Est. output cost:     $%.4f
  Claude subtotal:      $%.4f

Google Document AI -- %d verdict pages:
  Est. DAI cost:        $%.4f

TOTAL ESTIMATE:         $%.4f\n",
  n_docs, avg_input,
  est_input_cost, est_output_cost, est_input_cost + est_output_cost,
  n_verdict_pages, est_dai_cost,
  est_input_cost + est_output_cost + est_dai_cost
))
```


## ── MAIN PIPELINE: CLAUDE ON ALL DOCUMENTS ───────────────────────────────────
#
# Processes one document at a time, saves a checkpoint after every document,
# and writes a CSV every batch_size rows. If the run is interrupted, simply
# re-run this chunk — already-processed rows are skipped automatically.

```{r main_pipeline}
checkpoint_file <- "court_pipeline_checkpoint.rds"
batch_size      <- 20   # save a CSV snapshot every this many documents

if (file.exists(checkpoint_file)) {
  results <- readRDS(checkpoint_file)
  message("Resumed from checkpoint: ", sum(results$processed), " docs already done")
} else {
  results <- doc_inventory %>%
    mutate(
      raw_reply    = NA_character_,
      total_tokens = NA_real_,
      elapsed_sec  = NA_real_,
      api_error    = NA_character_,
      processed    = FALSE
    )
}

n_total       <- nrow(results)
pb            <- txtProgressBar(min = 0, max = n_total, style = 3)
overall_start <- Sys.time()

for (j in seq_len(n_total)) {

  # Skip rows already completed (enables safe resumption after interruption)
  if (isTRUE(results$processed[j])) {
    setTxtProgressBar(pb, j)
    next
  }

  elapsed_mins <- as.numeric(difftime(Sys.time(), overall_start, units = "mins"))
  cat(sprintf("
[%d/%d] Case: %s | Type: %s | Elapsed: %.1f min
",
              j, n_total, results$case_id[j], results$doc_type[j], elapsed_mins))
  flush.console()

  # For verdict documents, look up this file's DAI fields and pass them in
  dai_fields_for_this_doc <- NULL
  if (results$doc_type[j] == "verdict") {
    matched <- dai_raw %>% filter(filepath == results$filepath[j])
    if (nrow(matched) > 0 && !is.null(matched$dai_fields[[1]])) {
      dai_fields_for_this_doc <- matched$dai_fields[[1]]
    }
  }

  ans <- safe_claude(results$filepath[j], results$doc_type[j], dai_fields_for_this_doc)

  if (is.null(ans$result)) {
    results$api_error[j] <- conditionMessage(ans$error) %||% "Unknown error"
  } else {
    results$raw_reply[j]    <- ans$result$raw_text
    results$total_tokens[j] <- ans$result$total_tokens
    results$elapsed_sec[j]  <- ans$result$elapsed_sec
  }

  results$processed[j] <- TRUE
  saveRDS(results, checkpoint_file)   # checkpoint after every document
  setTxtProgressBar(pb, j)

  if (j %% batch_size == 0 || j == n_total) {
    write_csv(results, sprintf("court_pipeline_batch_row%04d.csv", j))
    message(sprintf("
Batch checkpoint saved at row %d", j))
  }
}

close(pb)
message("All Claude calls complete.")
```


## ── PARSE AND MERGE OUTPUTS INTO CSVs ────────────────────────────────────────

```{r parse_outputs}

# ── VERDICT CSV — merge Claude findings + Google DAI damages ──────────────────
#
# Claude provides:     Yes/No liability findings, fault percentages, verdict date
# Google DAI provides: dollar amounts with per-field confidence scores
# Merge key:           case_id + filepath

verdict_claude <- results %>%
  filter(doc_type == "verdict", !is.na(raw_reply)) %>%
  mutate(parsed = map(raw_reply, ~{
    clean <- str_replace_all(.x, "```json|```", "") %>% str_trim()
    tryCatch(fromJSON(clean, simplifyVector = FALSE), error = function(e) NULL)
  })) %>%
  filter(!map_lgl(parsed, is.null)) %>%
  mutate(
    Pl_type                      = map_chr(parsed, ~safe_field(.x, "Pl_type")),
    Def_type                     = map_chr(parsed, ~safe_field(.x, "Def_type")),
    Pl_gender                    = map_chr(parsed, ~safe_field(.x, "Pl_gender")),
    Def_gender                   = map_chr(parsed, ~safe_field(.x, "Def_gender")),
    Number_pl                    = map_chr(parsed, ~safe_field(.x, "Number_pl")),
    Number_def                   = map_chr(parsed, ~safe_field(.x, "Number_def")),
    Outcome                      = map_chr(parsed, ~safe_field(.x, "Outcome")),
    Verdict_note                 = map_chr(parsed, ~safe_field(.x, "Verdict_note")),
    Non_economic_damages_requested = map_chr(parsed, ~safe_field(.x, "Non_economic_damages_requested")),
    Punitive_damages_requested   = map_chr(parsed, ~safe_field(.x, "Punitive_damages_requested")),
    Monetary_award               = map_chr(parsed, ~safe_field(.x, "Monetary_award")),
    Non_economic_damages_awarded = map_chr(parsed, ~safe_field(.x, "Non_economic_damages_awarded")),
    Punitive_damages_awarded     = map_chr(parsed, ~safe_field(.x, "Punitive_damages_awarded")),
    Percent_plaintiff_liable     = map_chr(parsed, ~safe_field(.x, "Percent_plaintiff_liable")),
    verdict_date                 = map_chr(parsed, ~safe_field(.x, "verdict_date")),
    claude_notes                 = map_chr(parsed, ~safe_field(.x, "notes"))
  ) %>%
  select(case_id, filepath,
         Pl_type, Def_type, Pl_gender, Def_gender, Number_pl, Number_def,
         Outcome, Verdict_note,
         Non_economic_damages_requested, Punitive_damages_requested,
         Monetary_award, Non_economic_damages_awarded, Punitive_damages_awarded,
         Percent_plaintiff_liable, verdict_date, claude_notes)

# Google DAI damages — one row per extracted field per verdict PDF
dai_damages_clean <- dai_damages %>%
  select(case_id, filepath,
         dai_field_name   = field_name,
         dai_field_value  = field_value,
         dai_amount       = amount_numeric,
         value_confidence,
         flag_for_review)

# Left join: every Claude verdict row gets matched DAI damages rows
output_verdicts <- verdict_claude %>%
  left_join(dai_damages_clean, by = c("case_id", "filepath"))

write_csv(output_verdicts, "output_verdicts.csv")
message("Saved output_verdicts.csv — ", nrow(output_verdicts), " rows")
message("  Fields flagged for manual review: ",
        sum(output_verdicts$flag_for_review, na.rm = TRUE))


# ── JUDGMENT CSV ──────────────────────────────────────────────────────────────
judgment_rows <- results %>%
  filter(doc_type == "judgment", !is.na(raw_reply)) %>%
  mutate(parsed = map(raw_reply, ~{
    clean <- str_replace_all(.x, "```json|```", "") %>% str_trim()
    tryCatch(fromJSON(clean, simplifyVector = FALSE), error = function(e) NULL)
  })) %>%
  filter(!map_lgl(parsed, is.null))

output_judgments <- judgment_rows %>%
  mutate(awards_list = map(parsed, ~.x$judgment_awards %||% list())) %>%
  select(case_id, filepath, parsed, awards_list) %>%
  unnest(awards_list) %>%
  mutate(
    case_number            = map_chr(parsed, ~safe_field(.x, "case_number")),
    judge_name             = map_chr(parsed, ~safe_field(.x, "judge_name")),
    judgment_date          = map_chr(parsed, ~safe_field(.x, "judgment_date")),
    court                  = map_chr(parsed, ~safe_field(.x, "court")),
    post_judgment_interest = map_chr(parsed, ~safe_field(.x, "post_judgment_interest_rate")),
    costs_awarded          = map_chr(parsed, ~safe_field(.x, "costs_awarded")),
    notes                  = map_chr(parsed, ~safe_field(.x, "notes")),
    plaintiff_name         = map_chr(awards_list, ~safe_field(.x, "plaintiff_name")),
    amount_awarded         = map_chr(awards_list, ~safe_field(.x, "amount_awarded"))
  ) %>%
  select(-parsed, -awards_list)

write_csv(output_judgments, "output_judgments.csv")
message("Saved output_judgments.csv — ", nrow(output_judgments), " rows")


# ── MINUTE ENTRIES CSV ────────────────────────────────────────────────────────
minute_rows <- results %>%
  filter(doc_type == "minute", !is.na(raw_reply)) %>%
  mutate(parsed = map(raw_reply, ~{
    clean <- str_replace_all(.x, "```json|```", "") %>% str_trim()
    tryCatch(fromJSON(clean, simplifyVector = FALSE), error = function(e) NULL)
  })) %>%
  filter(!map_lgl(parsed, is.null)) %>%
  mutate(
    case_number         = map_chr(parsed, ~safe_field(.x, "case_number")),
    hearing_date        = map_chr(parsed, ~safe_field(.x, "hearing_date")),
    judge_name          = map_chr(parsed, ~safe_field(.x, "judge_name")),
    proceeding_type     = map_chr(parsed, ~safe_field(.x, "proceeding_type")),
    plaintiffs_present  = map_chr(parsed, ~safe_field(.x, "plaintiffs_present")),
    plaintiff_attorneys = map_chr(parsed, ~safe_field(.x, "plaintiff_attorneys")),
    defense_attorneys   = map_chr(parsed, ~safe_field(.x, "defense_attorneys")),
    key_events          = map_chr(parsed, ~safe_field(.x, "key_events")),
    exhibits_admitted   = map_chr(parsed, ~safe_field(.x, "exhibits_admitted")),
    total_time          = map_chr(parsed, ~safe_field(.x, "total_time")),
    notes               = map_chr(parsed, ~safe_field(.x, "notes"))
  ) %>%
  select(case_id, filepath, case_number, hearing_date, judge_name,
         proceeding_type, plaintiffs_present, plaintiff_attorneys,
         defense_attorneys, key_events, exhibits_admitted, total_time, notes)

write_csv(minute_rows, "output_minutes.csv")
message("Saved output_minutes.csv — ", nrow(minute_rows), " rows")


# ── MANUAL REVIEW LIST ────────────────────────────────────────────────────────
# A focused list of only the damages fields where Google DAI was uncertain.
# Open output_manual_review.csv, check each value against the original PDF,
# and correct any errors before using the data in your analysis.

review_list <- output_verdicts %>%
  filter(isTRUE(flag_for_review)) %>%
  select(case_id, filepath, dai_field_name, dai_field_value,
         dai_amount, value_confidence) %>%
  arrange(value_confidence)  # lowest confidence first

if (nrow(review_list) > 0) {
  write_csv(review_list, "output_manual_review.csv")
  message("Saved output_manual_review.csv — ",
          nrow(review_list), " fields need manual verification")
} else {
  message("No fields flagged — all DAI confidence scores above threshold")
}


# ── ERROR LOG ─────────────────────────────────────────────────────────────────
errors <- bind_rows(
  results %>%
    filter(!is.na(api_error)) %>%
    mutate(source = "Claude") %>%
    select(case_id, doc_type, filepath, source, error = api_error),
  dai_raw %>%
    filter(!is.na(dai_error)) %>%
    mutate(source = "Google DAI", doc_type = "verdict") %>%
    select(case_id, doc_type, filepath, source, error = dai_error)
)

if (nrow(errors) > 0) {
  write_csv(errors, "output_errors.csv")
  message("Saved output_errors.csv — ", nrow(errors), " failed calls to investigate")
} else {
  message("No errors — all API calls succeeded")
}
```
